---
title: "HBN fit GAMs"
author: "Audrey Luo"
output: html_document
---

```{r setup, include=FALSE}

library(dplyr)
source("/cbica/projects/network_replication/adapted_Rscripts/GAM_functions.R")
source("/cbica/projects/network_replication/adapted_Rscripts/fitGAMs.R")
 
dataset = "HBN"
knitr::opts_chunk$set(include = FALSE, eval = TRUE, echo = FALSE, warning = FALSE, message = FALSE) 
  
  
```

# make connectivityMetric-demographics .csv's
```{r connMetric_demographics, include=FALSE}

demographics <- read.csv(sprintf("/cbica/projects/network_replication/input/%1$s/sample_selection/%1$s_demographics_finalsample_202230226.csv", dataset))
participants_noAge_index <- c(which(is.na(demographics$age))) 
demographics <- demographics[-c(which(is.na(demographics$age))),] 
names(demographics)[c(which(names(demographics) == "sub"))] <- "subject"
demographics <- demographics[,c(which(names(demographics) == "subject"), which(names(demographics) == "sex"), which(names(demographics)=="age"), which(names(demographics) =="meanFD_avgSes"))] 
 
 
# GBC
## GBC.glasser.HBN, GBC.gordon.HBN, GBC.schaefer200.HBN, GBC.schaefer400.HBN
atlases <- c("glasser", "gordon", "schaefer200", "schaefer400")
metric = "GBC"

for(i in c(1:length(atlases))){
  df_name <- paste0(metric, ".", atlases[i], ".", dataset)
  assign(df_name, make_connMetricsDemog_covbat(atlases[i], metric, demographics, "subject", dataset))
}

 
 
# BNC
## BNC.gordon.HBN, BNC.schaefer200x7.HBN, BNC.schaefer200x17.HBN, BNC.schaefer400x7.HBN, BNC.schaefer400x17.HBN
atlases <- c("gordon", "schaefer200x7", "schaefer200x17", "schaefer400x7", "schaefer400x17")
metric = "BNC"
for(i in c(1:length(atlases))){
  df_name <- paste0(metric, ".", atlases[i], ".", dataset)
  assign(df_name, make_connMetricsDemog_covbat(atlases[i], metric, demographics, "subject", dataset))
}

# WNC
## WNC.gordon.HBN, WNC.schaefer200x7.HBN, WNC.schaefer200x17.HBN, WNC.schaefer400x7.HBN, WNC.schaefer400x17.HBN
atlases <- c("gordon", "schaefer200x7", "schaefer200x17", "schaefer400x7", "schaefer400x17")
metric = "WNC"

for(i in c(1:length(atlases))){
  df_name <- paste0(metric, ".", atlases[i], ".", dataset)
  assign(df_name, make_connMetricsDemog_covbat(atlases[i], metric, demographics, "subject", dataset))
} 

 
# pending docker container
# edge 
## edge.glasser.HBN, edge.gordon.HBN, edge.schaefer200x7.HBN, edge.schaefer200x17.HBN, edge.schaefer400x7.HBN, edge.schaefer400x17.HBN
atlases <- c("glasser","gordon", "schaefer200x7", "schaefer200x17", "schaefer400x7", "schaefer400x17")
#make_connMetricsDemog_covbat("gordon", demographics, "subject", dataset)
for(i in c(1:length(atlases))){
  df_name <- paste0("edge.", atlases[i], ".", dataset)
  assign(df_name, make_EdgeDemog_covbat(atlases[i],  demographics, "subject", dataset))
} 
 

 
```


 

# load connectivityMetric-demographics .csv's
```{r load_connectivity, include=TRUE}

GBC.glasser.HBN <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/GBC/GBCglasser_demographics_finalsample_covbat.csv", dataset)) 
GBC.gordon.HBN <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/GBC/GBCgordon_demographics_finalsample_covbat.csv", dataset)) 
 
GBC.schaefer200.HBN <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/GBC/GBCschaefer200_demographics_finalsample_covbat.csv", dataset)) 
names(GBC.schaefer200.HBN) <- gsub('X17Networks', "Networks", names(GBC.schaefer200.HBN))


GBC.schaefer400.HBN <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/GBC/GBCschaefer400_demographics_finalsample_covbat.csv", dataset)) 
names(GBC.schaefer400.HBN) <- gsub('X17Networks', "Networks", names(GBC.schaefer400.HBN)) 
  

# BNC
BNC.gordon.HBN <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/BNC/BNCgordon_demographics_finalsample_covbat.csv", dataset))   
BNC.schaefer200x7.HBN <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/BNC/BNCschaefer200x7_demographics_finalsample_covbat.csv", dataset)) 
names(BNC.schaefer200x7.HBN) <- gsub("X7", "", names(BNC.schaefer200x7.HBN))

BNC.schaefer200x17.HBN <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/BNC/BNCschaefer200x17_demographics_finalsample_covbat.csv", dataset))    
names(BNC.schaefer200x17.HBN) <- gsub("X17", "", names(BNC.schaefer200x17.HBN))

BNC.schaefer400x7.HBN <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/BNC/BNCschaefer400x7_demographics_finalsample_covbat.csv", dataset))
names(BNC.schaefer400x7.HBN) <- gsub("X7", "", names(BNC.schaefer400x7.HBN))

BNC.schaefer400x17.HBN <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/BNC/BNCschaefer400x17_demographics_finalsample_covbat.csv", dataset))   
names(BNC.schaefer400x17.HBN) <- gsub("X17", "", names(BNC.schaefer400x17.HBN))

# WNC
WNC.gordon.HBN <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/WNC/WNCgordon_demographics_finalsample_covbat.csv", dataset))    
WNC.schaefer200x7.HBN <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/WNC/WNCschaefer200x7_demographics_finalsample_covbat.csv", dataset))
names(WNC.schaefer200x7.HBN) <- gsub("X7", "", names(WNC.schaefer200x7.HBN))

WNC.schaefer200x17.HBN <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/WNC/WNCschaefer200x17_demographics_finalsample_covbat.csv", dataset)) 
names(WNC.schaefer200x17.HBN) <- gsub("X17", "", names(WNC.schaefer200x17.HBN))

WNC.schaefer400x7.HBN <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/WNC/WNCschaefer400x7_demographics_finalsample_covbat.csv", dataset)) 
names(WNC.schaefer400x7.HBN) <- gsub("X7", "", names(WNC.schaefer400x7.HBN))

WNC.schaefer400x17.HBN <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/WNC/WNCschaefer400x17_demographics_finalsample_covbat.csv", dataset))  
names(WNC.schaefer400x17.HBN) <- gsub("X17", "", names(WNC.schaefer400x17.HBN))
 


edge.gordon.HBN <- readRDS("/cbica/projects/network_replication/output/HBN/edge/gordon_demographics_finalsample_covbat.RData")
edge.glasser.HBN <- readRDS("/cbica/projects/network_replication/output/HBN/edge/glasser_demographics_finalsample_covbat.RData")
edge.schaefer200x7.HBN <- readRDS("/cbica/projects/network_replication/output/HBN/edge/schaefer200x7_demographics_finalsample_covbat.RData")
edge.schaefer200x17.HBN <- readRDS("/cbica/projects/network_replication/output/HBN/edge/schaefer200x17_demographics_finalsample_covbat.RData")
edge.schaefer400x7.HBN <- readRDS("/cbica/projects/network_replication/output/HBN/edge/schaefer400x7_demographics_finalsample_covbat.RData")
edge.schaefer400x17.HBN <- readRDS("/cbica/projects/network_replication/output/HBN/edge/schaefer400x17_demographics_finalsample_covbat.RData")

# make sex a factor
class(GBC.glasser.HBN$sex)
GBC.glasser.HBN$sex <- as.factor(GBC.glasser.HBN$sex)
GBC.gordon.HBN$sex <- as.factor(GBC.gordon.HBN$sex)
GBC.schaefer200.HBN$sex <- as.factor(GBC.schaefer200.HBN$sex)
GBC.schaefer400.HBN$sex <- as.factor(GBC.schaefer400.HBN$sex)

 
BNC.gordon.HBN$sex <- as.factor(BNC.gordon.HBN$sex)
BNC.schaefer200x7.HBN$sex <- as.factor(BNC.schaefer200x7.HBN$sex)
BNC.schaefer200x17.HBN$sex <- as.factor(BNC.schaefer200x17.HBN$sex)
BNC.schaefer400x7.HBN$sex <- as.factor(BNC.schaefer400x7.HBN$sex)
BNC.schaefer400x17.HBN$sex <- as.factor(BNC.schaefer400x17.HBN$sex)

WNC.gordon.HBN$sex <- as.factor(WNC.gordon.HBN$sex)   
WNC.schaefer200x17.HBN$sex <- as.factor(WNC.schaefer200x17.HBN$sex) 
WNC.schaefer400x17.HBN$sex <- as.factor(WNC.schaefer400x17.HBN$sex) 
WNC.schaefer200x7.HBN$sex <- as.factor(WNC.schaefer200x7.HBN$sex) 
WNC.schaefer400x7.HBN$sex <- as.factor(WNC.schaefer400x7.HBN$sex) 


edge.gordon.HBN$sex <- as.factor(edge.gordon.HBN$sex)
edge.glasser.HBN$sex <- as.factor(edge.glasser.HBN$sex)
edge.schaefer200x7.HBN$sex <- as.factor(edge.schaefer200x7.HBN$sex)
edge.schaefer200x17.HBN$sex <- as.factor(edge.schaefer200x17.HBN$sex)
edge.schaefer400x7.HBN$sex <- as.factor(edge.schaefer400x7.HBN$sex)
edge.schaefer400x17.HBN$sex <- as.factor(edge.schaefer400x17.HBN$sex)

 
```



# load parcel labels and g atedges 
```{r}
# load parcel labels
glasser.parcel.labels <- read.csv("/cbica/projects/network_replication/atlases/parcellations/glasser360_regionlist_final.csv")

gordon.parcel.labels <- read.csv("/cbica/projects/network_replication/atlases/parcellations/gordon_regionlist_final.csv")

schaefer200x7.parcel.labels <- read.csv("/cbica/projects/network_replication/atlases/parcellations/schaefer200x7_regionlist_final.csv")

schaefer200x17.parcel.labels <- read.csv("/cbica/projects/network_replication/atlases/parcellations/schaefer200x17_regionlist_final.csv")
schaefer200.parcel.labels <- schaefer200x17.parcel.labels #gbc

schaefer400x7.parcel.labels <- read.csv("/cbica/projects/network_replication/atlases/parcellations/schaefer400x7_regionlist_final.csv")

schaefer400x17.parcel.labels <- read.csv("/cbica/projects/network_replication/atlases/parcellations/schaefer400x17_regionlist_final.csv")
schaefer400.parcel.labels <- schaefer400x17.parcel.labels #gbc




# edges
gordon_edge <- read.csv("/cbica/projects/network_replication/atlases/edge/gordon_edge.csv")
gordon_edge <- gordon_edge[,2]

glasser_edge <- read.csv("/cbica/projects/network_replication/atlases/edge/glasser_edge.csv")
glasser_edge <- glasser_edge[,2]
schaefer200x7_edge <- read.csv("/cbica/projects/network_replication/atlases/edge/schaefer200x7_edge.csv")
schaefer200x7_edge <- schaefer200x7_edge[,2]
schaefer200x17_edge <- read.csv("/cbica/projects/network_replication/atlases/edge/schaefer200x17_edge.csv")
schaefer200x17_edge <- schaefer200x17_edge[,2]

schaefer400x7_edge <- read.csv("/cbica/projects/network_replication/atlases/edge/schaefer400x7_edge.csv")
schaefer400x7_edge <- schaefer400x7_edge[,2]
schaefer400x17_edge <- read.csv("/cbica/projects/network_replication/atlases/edge/schaefer400x17_edge.csv")
schaefer400x17_edge <- schaefer400x17_edge[,2]
```  



# Check AIC for k=3-6
```{r}
library(stats)

 
dataset_name="HBN"
covariates ="sex + meanFD_avgSes"
smooth_var="age"


check_aic <- function(parcel.labels, atlas_name, network_parcellation, dataset_name, covariates, smooth_var, k_number){
    parcel.labels <- parcel.labels$label
    list_plots <- list()
    list_AIC <- c()
    list_region <- c()
    for(row in c(1:length(parcel.labels))){ #for each region
      region <- parcel.labels[row] 
      dataname <- sprintf("%s.%s%s.%s", metric, atlas_name, network_parcellation, dataset_name) 
      gam.data <- get(dataname) # Return the Value of a Named Object
      parcel <- region
      region <- str_replace(region, "-", ".")
      modelformula <- as.formula(sprintf("%s ~ s(%s, k=%s, fx=T) + %s", region, smooth_var, k_number, covariates)) # 3 knots, fx = should term be unpenalized (so here, it is unpenalized)
      gam.model <- gam(modelformula, data=gam.data)
      gam.results <- summary(gam.model) 
      
      #list_plots <- append(draw(gam.model, residuals = TRUE), list_plots)
      list_AIC <- append(AIC(gam.model), list_AIC)
      list_region <- append(region, list_region)
      k_dataframe <- data.frame(bind_cols(list_AIC, list_region))
      names(k_dataframe) <- c("AIC", "region")
      print(row)
    }
      return(k_dataframe)
}
 
metric="GBC"
k_3 <- check_aic(schaefer200.parcel.labels, "schaefer200", "", "PNC", "sex + meanFD_avgSes", "age", 3)
mean(k_3$AIC) #-4650.164
median(k_3$AIC) #-4650.231

k_4 <- check_aic(schaefer200.parcel.labels, "schaefer200", "", "PNC", "sex + meanFD_avgSes", "age", 4)
mean(k_4$AIC) #-4649.335
median(k_4$AIC) #-4650.828

k_5 <- check_aic(schaefer200.parcel.labels, "schaefer200", "", "PNC", "sex + meanFD_avgSes", "age", 5)
mean(k_5$AIC) #-4648.405
median(k_5$AIC) #-4649.481

k_6 <- check_aic(schaefer200.parcel.labels, "schaefer200", "", "PNC", "sex + meanFD_avgSes", "age", 6)
mean(k_6$AIC) #-4647.478
median(k_6$AIC) #-4647.8
 
 
# BNC
metric="BNC"
k_3.BNC <- check_aic(schaefer200x7.parcel.labels, "schaefer200", "x7", "PNC", "sex + meanFD_avgSes", "age", 3)
mean(k_3.BNC$AIC) # -4351.929
median(k_3.BNC$AIC) # -4464.881

k_4.BNC <- check_aic(schaefer200x7.parcel.labels, "schaefer200", "x7", "PNC", "sex + meanFD_avgSes", "age", 4)
mean(k_4.BNC$AIC) # -4351.238
median(k_4.BNC$AIC) #-4463.059

k_5.BNC <- check_aic(schaefer200x7.parcel.labels, "schaefer200", "x7", "PNC", "sex + meanFD_avgSes", "age", 5)
mean(k_5.BNC$AIC) # -4350.256
median(k_5.BNC$AIC) #-4461.29

k_6.BNC <- check_aic(schaefer200x7.parcel.labels, "schaefer200", "x7", "PNC", "sex + meanFD_avgSes", "age", 6)
mean(k_6.BNC$AIC) # -4349.364
median(k_6.BNC$AIC) #-4461.45


# WNC
metric="WNC"
k_3.WNC <- check_aic(schaefer200x7.parcel.labels, "schaefer200", "x7", "PNC", "sex + meanFD_avgSes", "age", 3)
mean(k_3.WNC$AIC) # -2493.504
median(k_3.WNC$AIC) #-2527.435

k_4.WNC <- check_aic(schaefer200x7.parcel.labels, "schaefer200", "x7", "PNC", "sex + meanFD_avgSes", "age", 4)
mean(k_4.WNC$AIC) # -2492.42
median(k_4.WNC$AIC) #-2526.052

k_5.WNC <- check_aic(schaefer200x7.parcel.labels, "schaefer200", "x7", "PNC", "sex + meanFD_avgSes", "age", 5)
mean(k_5.WNC$AIC) # -2491.383
median(k_5.WNC$AIC) #-2524.531

k_6.WNC <- check_aic(schaefer200x7.parcel.labels, "schaefer200", "x7", "PNC", "sex + meanFD_avgSes", "age", 6)
mean(k_6.WNC$AIC) # -2490.116
median(k_6.WNC$AIC) #-2522.614
 
```





# Fit GAMs
```{r}
 
# GBC GAMs
gam.GBC.age.glasser <- fitGAMs_covbat(glasser.parcel.labels, "GBC", "glasser", "",dataset)
gam.GBC.age.gordon <- fitGAMs_covbat(gordon.parcel.labels, "GBC", "gordon", "", dataset)
gam.GBC.age.schaefer200 <- fitGAMs_covbat(schaefer200x17.parcel.labels, "GBC", "schaefer200", "", dataset)
gam.GBC.age.schaefer400 <- fitGAMs_covbat(schaefer400x17.parcel.labels, "GBC", "schaefer400", "", dataset)
 

# BNC GAMs
gam.BNC.age.gordon <- fitGAMs_covbat(gordon.parcel.labels, "BNC", "gordon", "", dataset)
gam.BNC.age.schaefer200x7 <- fitGAMs_covbat(schaefer200x7.parcel.labels, "BNC", "schaefer200", "x7", dataset)
gam.BNC.age.schaefer200x17 <- fitGAMs_covbat(schaefer200x17.parcel.labels, "BNC", "schaefer200", "x17",dataset)  
gam.BNC.age.schaefer400x7 <- fitGAMs_covbat(schaefer400x7.parcel.labels, "BNC", "schaefer400", "x7", dataset)   
gam.BNC.age.schaefer400x17 <- fitGAMs_covbat(schaefer400x17.parcel.labels, "BNC", "schaefer400", "x17",dataset)  
 


# WNC GAMs
gam.WNC.age.gordon <- fitGAMs_covbat(gordon.parcel.labels, "WNC", "gordon", "", dataset)
gam.WNC.age.schaefer200x7 <- fitGAMs_covbat(schaefer200x7.parcel.labels, "WNC", "schaefer200", "x7", dataset)   
gam.WNC.age.schaefer200x17 <- fitGAMs_covbat(schaefer200x17.parcel.labels, "WNC", "schaefer200", "x17",dataset)  
gam.WNC.age.schaefer400x7 <- fitGAMs_covbat(schaefer400x7.parcel.labels, "WNC", "schaefer400", "x7",dataset)  
gam.WNC.age.schaefer400x17 <- fitGAMs_covbat(schaefer400x17.parcel.labels, "WNC", "schaefer400", "x17",dataset)  


 
# Edge GAMs   -- start here, do this overnight
glasser_edge <- gsub("-", ".", glasser_edge)
names(edge.glasser.HBN) <- gsub("-", ".",names(edge.glasser.HBN))
schaefer200x7_edge <- gsub("7Networks", "Networks", schaefer200x7_edge)
names(edge.schaefer200x7.HBN) <- gsub("7Networks", "Networks", names(edge.schaefer200x7.HBN))
schaefer200x17_edge <- gsub("17Networks", "Networks", schaefer200x17_edge)
names(edge.schaefer200x17.HBN) <- gsub("17Networks", "Networks", names(edge.schaefer200x17.HBN))
schaefer400x7_edge <- gsub("7Networks", "Networks", schaefer400x7_edge)
names(edge.schaefer400x7.HBN) <- gsub("7Networks", "Networks", names(edge.schaefer400x7.HBN))
schaefer400x17_edge <- gsub("17Networks", "Networks", schaefer400x17_edge)
names(edge.schaefer400x17.HBN) <- gsub("17Networks", "Networks", names(edge.schaefer400x17.HBN))
 
gam.edge.age.glasser <- fitGAMs_covbat_edge(glasser_edge,"edge","glasser", dataset)  
gam.edge.age.gordon <- fitGAMs_covbat_edge(gordon_edge,"edge","gordon", dataset)
gam.edge.age.schaefer200x7 <- fitGAMs_covbat_edge(schaefer200x7_edge,"edge","schaefer200x7", dataset)
gam.edge.age.schaefer200x17 <- fitGAMs_covbat_edge(schaefer200x17_edge,"edge","schaefer200x17", dataset)
gam.edge.age.schaefer400x7 <- fitGAMs_covbat_edge(schaefer400x7_edge,"edge","schaefer400x7", dataset)
gam.edge.age.schaefer400x17 <- fitGAMs_covbat_edge(schaefer400x17_edge,"edge","schaefer400x17", dataset)
  
```




# Estimate GAM smooths based on model-predicted data and save out predicted y data** 
```{r}
 
# GBC GAMs 
gam.GBC.smooths.glasser <- estimate_GAMsmooths_covbat(glasser.parcel.labels, "GBC", "glasser", "",dataset)
gam.GBC.smooths.gordon <- estimate_GAMsmooths_covbat(gordon.parcel.labels, "GBC", "gordon", "", dataset)
gam.GBC.smooths.schaefer200 <- estimate_GAMsmooths_covbat(schaefer200x17.parcel.labels, "GBC", "schaefer200", "", dataset)
gam.GBC.smooths.schaefer400 <- estimate_GAMsmooths_covbat(schaefer400x17.parcel.labels, "GBC", "schaefer400", "", dataset)


# BNC GAMs
gam.BNC.smooths.gordon <- estimate_GAMsmooths_covbat(gordon.parcel.labels, "BNC", "gordon", "", dataset)
gam.BNC.smooths.schaefer200x7 <- estimate_GAMsmooths_covbat(schaefer200x7.parcel.labels, "BNC", "schaefer200", "x7", dataset)
gam.BNC.smooths.schaefer200x17 <- estimate_GAMsmooths_covbat(schaefer200x17.parcel.labels, "BNC", "schaefer200", "x17",dataset)
gam.BNC.smooths.schaefer400x7 <- estimate_GAMsmooths_covbat(schaefer400x7.parcel.labels, "BNC", "schaefer400", "x7",dataset)
gam.BNC.smooths.schaefer400x17 <- estimate_GAMsmooths_covbat(schaefer400x17.parcel.labels, "BNC", "schaefer400", "x17",dataset)

# WNC GAMs
gam.WNC.smooths.gordon <- estimate_GAMsmooths_covbat(gordon.parcel.labels, "WNC", "gordon", "", dataset)
gam.WNC.smooths.schaefer200x7 <- estimate_GAMsmooths_covbat(schaefer200x7.parcel.labels, "WNC", "schaefer200", "x7", dataset)
gam.WNC.smooths.schaefer200x17 <- estimate_GAMsmooths_covbat(schaefer200x17.parcel.labels, "WNC", "schaefer200", "x17",dataset)
gam.WNC.smooths.schaefer400x7 <- estimate_GAMsmooths_covbat(schaefer400x7.parcel.labels, "WNC", "schaefer400", "x7",dataset)
gam.WNC.smooths.schaefer400x17 <- estimate_GAMsmooths_covbat(schaefer400x17.parcel.labels, "WNC", "schaefer400", "x17",dataset)
```


# Calculate Region-wise Predicted Fitted GBC values  

```{r}

# GBC GAMs age fitted
gam.GBC.fitted.glasser <- dev_fitted_covbat(glasser.parcel.labels, "GBC", "glasser", dataset)
gam.GBC.fitted.gordon <- dev_fitted_covbat(gordon.parcel.labels, "GBC", "gordon", dataset)
gam.GBC.fitted.schaefer200 <- dev_fitted_covbat(schaefer200x17.parcel.labels, "GBC", "schaefer200", dataset)
gam.GBC.fitted.schaefer400 <- dev_fitted_covbat(schaefer400x17.parcel.labels, "GBC", "schaefer400", dataset)

 
# BNC GAMs age fitted
gam.BNC.fitted.gordon <- dev_fitted_covbat(gordon.parcel.labels, "BNC", "gordon", dataset)
gam.BNC.fitted.schaefer200x7 <- dev_fitted_covbat(schaefer200x7.parcel.labels, "BNC", "schaefer200x7", dataset)
gam.BNC.fitted.schaefer200x17 <- dev_fitted_covbat(schaefer200x17.parcel.labels, "BNC", "schaefer200x17", dataset)
gam.BNC.fitted.schaefer400x7 <- dev_fitted_covbat(schaefer400x7.parcel.labels, "BNC", "schaefer400x7", dataset)
gam.BNC.fitted.schaefer400x17 <- dev_fitted_covbat(schaefer400x17.parcel.labels, "BNC", "schaefer400x17", dataset)

# WNC GAMs age fitted
gam.WNC.fitted.gordon <- dev_fitted_covbat(gordon.parcel.labels, "WNC", "gordon", dataset)
gam.WNC.fitted.schaefer200x7 <- dev_fitted_covbat(schaefer200x7.parcel.labels, "WNC", "schaefer200x7", dataset)
gam.WNC.fitted.schaefer200x17 <- dev_fitted_covbat(schaefer200x17.parcel.labels, "WNC", "schaefer200x17",dataset)
gam.WNC.fitted.schaefer400x7 <- dev_fitted_covbat(schaefer400x7.parcel.labels, "WNC", "schaefer400x7", dataset)
gam.WNC.fitted.schaefer400x17 <- dev_fitted_covbat(schaefer400x17.parcel.labels, "WNC", "schaefer400x17", dataset)

```


 
# Calculate Region-wise Predicted Fitted GBC values Correlation with SA Axis for Schaefer200 only 

```{r}

fits.SAaxis.posteriorcor_schaefer200.GBC <- make_fits.SAaxis.posteriorcor_covbat("GBC", "schaefer200", dataset)

```


# Calculate Region-wise Developmental Derivatives
```{r}

# GBC GAMs age derivatives
gam.GBC.derivatives.glasser <- dev_derivatives_covbat(glasser.parcel.labels, "GBC", "glasser", dataset)
gam.GBC.derivatives.gordon <- dev_derivatives_covbat(gordon.parcel.labels, "GBC", "gordon", dataset)
gam.GBC.derivatives.schaefer200 <- dev_derivatives_covbat(schaefer200x17.parcel.labels, "GBC", "schaefer200", dataset)
gam.GBC.derivatives.schaefer400 <- dev_derivatives_covbat(schaefer400x17.parcel.labels, "GBC", "schaefer400", dataset)

 
# BNC GAMs age derivatives
gam.BNC.derivatives.gordon <- dev_derivatives_covbat(gordon.parcel.labels, "BNC", "gordon", dataset)
gam.BNC.derivatives.schaefer200x7 <- dev_derivatives_covbat(schaefer200x7.parcel.labels, "BNC", "schaefer200x7", dataset)
gam.BNC.derivatives.schaefer200x17 <- dev_derivatives_covbat(schaefer200x17.parcel.labels, "BNC", "schaefer200x17", dataset)
gam.BNC.derivatives.schaefer400x7 <- dev_derivatives_covbat(schaefer400x7.parcel.labels, "BNC", "schaefer400x7", dataset)
gam.BNC.derivatives.schaefer400x17 <- dev_derivatives_covbat(schaefer400x17.parcel.labels, "BNC", "schaefer400x17", dataset)

# WNC GAMs age derivatives
gam.WNC.derivatives.gordon <- dev_derivatives_covbat(gordon.parcel.labels, "WNC", "gordon", dataset)
gam.WNC.derivatives.schaefer200x7 <- dev_derivatives_covbat(schaefer200x7.parcel.labels, "WNC", "schaefer200x7", dataset)
gam.WNC.derivatives.schaefer200x17 <- dev_derivatives_covbat(schaefer200x17.parcel.labels, "WNC", "schaefer200x17",dataset)
gam.WNC.derivatives.schaefer400x7 <- dev_derivatives_covbat(schaefer400x7.parcel.labels, "WNC", "schaefer400x7", dataset)
gam.WNC.derivatives.schaefer400x17 <- dev_derivatives_covbat(schaefer400x17.parcel.labels, "WNC", "schaefer400x17", dataset)
  
```



# Calculate Region-wise Posterior Smooth Derivatives Correlation with SA Axis (computationally heavy - can compute on cluster)

```{r}
# GBC - Region-wise Posterior Smooth Derivatives Correlation with SA Axis
deriv.SAaxis.posteriorcor_glasser.GBC <- make_deriv.SAaxis.posteriorcor_covbat("GBC", "glasser", dataset)
deriv.SAaxis.posteriorcor_gordon.GBC <- make_deriv.SAaxis.posteriorcor_covbat("GBC", "gordon", dataset)
deriv.SAaxis.posteriorcor_schaefer200.GBC <- make_deriv.SAaxis.posteriorcor_covbat("GBC", "schaefer200", dataset)
deriv.SAaxis.posteriorcor_schaefer400.GBC <- make_deriv.SAaxis.posteriorcor_covbat("GBC", "schaefer400", dataset)

# BNC - Region-wise Posterior Smooth Derivatives Correlation with SA Axis
deriv.SAaxis.posteriorcor_gordon.BNC <- make_deriv.SAaxis.posteriorcor_covbat("BNC", "gordon", dataset)
deriv.SAaxis.posteriorcor_schaefer200x7.BNC <- make_deriv.SAaxis.posteriorcor_covbat("BNC", "schaefer200x7", dataset)
deriv.SAaxis.posteriorcor_schaefer400x7.BNC <- make_deriv.SAaxis.posteriorcor_covbat("BNC", "schaefer400x7", dataset)
deriv.SAaxis.posteriorcor_schaefer200x17.BNC <- make_deriv.SAaxis.posteriorcor_covbat("BNC", "schaefer200x17", dataset)
deriv.SAaxis.posteriorcor_schaefer400x17.BNC <- make_deriv.SAaxis.posteriorcor_covbat("BNC", "schaefer400x17", dataset)


# WNC - Region-wise Posterior Smooth Derivatives Correlation with SA Axis
deriv.SAaxis.posteriorcor_gordon.WNC <- make_deriv.SAaxis.posteriorcor_covbat("WNC", "gordon", dataset)
deriv.SAaxis.posteriorcor_schaefer200x7.WNC <- make_deriv.SAaxis.posteriorcor_covbat("WNC", "schaefer200x7", dataset)
deriv.SAaxis.posteriorcor_schaefer400x7.WNC <- make_deriv.SAaxis.posteriorcor_covbat("WNC", "schaefer400x7", dataset)
deriv.SAaxis.posteriorcor_schaefer200x17.WNC <- make_deriv.SAaxis.posteriorcor_covbat("WNC", "schaefer200x17", dataset)
deriv.SAaxis.posteriorcor_schaefer400x17.WNC <- make_deriv.SAaxis.posteriorcor_covbat("WNC", "schaefer400x17", dataset)
 
```
