---
title: "HCP-D Sample Selection"
author: "Audrey Luo"
output: html_document
---
# Sample Selection process
1) original sample: N=652, ages 5-21, 5716 scans total
2) exclude participants with medical conditions affecting brain function, gross neurological abnormalities: N=631, 5527 scans
3) include passing T1 QC: all scans in dataset have survived T1 QC already 
4) include meanFD < 0.3: N=629, 5165 scans 
5) include scans with at least 7 minutes of scan time: N=625, 5159 scans (final sample), 337 females
range before: 2.24000 to 42.66667 min
median before: 42.66667 min

range after: 7.466667 to 42.66667 min
median after: 42.666667 min


Age: mean=14.5, SD=4.1

Race:
- white = 395 - 63.2%
- asian = 48 - 7.7%%
- black = 69 - 11%
- other (native american, hawaiin or pacific islander) = 3 - 0.48%
- missing = 16 - 2.6%
- mixed = 94 - 15%

# Sample Selection for sensitivity analysis (rest only)
5) include scans with at least 6 minutes of rest-only scan time (lowered threshold due to fewer total scans available after selecting for rest-only): N=611, 2324 scans, 328 females 
Notes:
- mean FD is averaged across the scans in a given session
  

```{r setup, include=FALSE}
library(dplyr)
library(tidyverse)
library(magrittr)
library(reshape)
library(reshape2)
library(MASS)
library(stargazer)
library(ggplot2)
library(ggpubr)
library(reticulate) 
# reticulate::py_install("pandas") # install pandas for python code
# reticulate::py_install("glob2")  # install glob2 for python code
  
```


## Concatenate xcp qc files
```{python}
import pandas as pd
import glob2 as glob
import sys
import os
  
path = "/cbica/projects/network_replication/input/HCPD/hcpd_xcp/qc_files"  
all_files = glob.glob(os.path.join(path, "*.csv")) # load all qc csv filenames 

df_from_each_file = (pd.read_csv(f, header=0, converters={'sub': str}) for f in all_files) # read csv's
concatenated_df = pd.concat(df_from_each_file, ignore_index=True) # concatenate csv's

concatenated_df['sub'] = 'sub-' + concatenated_df['sub'].astype(str) # add "sub-" to subject ID's
  
path=r'/cbica/projects/network_replication/input/HCPD/hcpd_xcp/qc_files/'
concatenated_df.to_csv(os.path.join(path,r'HCPD_xcp_qc_concat_20230628.csv'),index=False) # save out concatenated qc files
```
 

 
## 1) original sample: N=652, ages 5-22 
```{r qc_setup}
demographics <- read.csv("/cbica/projects/network_replication/input/HCPD/sample_selection/hcpd_demographics.csv")

# load and concatenate xcp QC information for all subjects
participants <- gsub("HCD", "sub-", demographics$src_subject_id)
collated_HCPD.xcp <- read.csv("/cbica/projects/network_replication/input/HCPD/hcpd_xcp/qc_files/HCPD_xcp_qc_concat_20230628.csv")
 
length(unique(collated_HCPD.xcp$sub)) # 652 participants before head motion QC  
    
```


## 2) exclude participants with medical conditions affecting brain function, gross neurological abnormalities
```{r medical_exclusion}


# cancer/leukemia
cancer <- demographics$src_subject_id[c(which(demographics$medhis_2e == 1))] # HCD0641341

# lead poisoning
lead<- demographics$src_subject_id[c(which(demographics$medhis_2k==1))] # "HCD0392144" "HCD0641341"
 
# sickle cell anemia
sickle <- demographics$src_subject_id[c(which(demographics$medhis_2p==1))] # HCD0641341
 
# accidental poisoning
poisoning <- demographics$src_subject_id[c(which(demographics$medhis_6q ==1))] # "HCD0529751" "HCD2855875"
 
# multiple sclerosis
multiple_sclerosis <- demographics$src_subject_id[c(which(demographics$ms ==1))]  # "HCD0641341" "HCD1617450"

# seizure
seizure_ph9 <- demographics$src_subject_id[c(which(demographics$ph_9 ==1))]  # "HCD0360838" "HCD0478356" - each participant had one seizure
epilepsy_cfmh <- demographics$src_subject_id[c(which(demographics$cfmh_chd_seizure ==1))] # "HCD0641341" "HCD1277149" (not sure why these participants didn't endorse ph_9 -- 'ever went to doctor/ER for seizure')
  
# brain injury
brain_injury <- demographics$src_subject_id[c(which(demographics$seq1c_2 ==1))] # 14 participants 
 
 
medical_exclusion <- unique(c(cancer, lead, sickle, poisoning, multiple_sclerosis, seizure_ph9, epilepsy_cfmh, brain_injury))
 
  
demographics_medExclusion <- demographics[-c(which(demographics$src_subject_id %in% medical_exclusion)),]
 
collated_HCPD.xcp_medExclusion <- collated_HCPD.xcp[-c(which(paste0("HCD", gsub("sub-", "", collated_HCPD.xcp$sub)) %in% medical_exclusion)),]

length(unique(collated_HCPD.xcp_medExclusion$sub)) # N=631
```

## 3) include passing T1 QC (HCP-D dataset only includes scans that passed T1 QC)
## 4) include meanFD < 0.3
```{r meanFD, cache=TRUE}

meanFD_exclude <- collated_HCPD.xcp_medExclusion[c(which(collated_HCPD.xcp_medExclusion$meanFD > 0.3)),] # 362 runs with meanFD > 0.3
 

collated_HCPD.xcp_headMotion <- collated_HCPD.xcp_medExclusion %>% filter(meanFD < 0.3) 

length(unique(collated_HCPD.xcp_headMotion$sub)) # 2 additional participants excluded by meanFD > 0.3, N=629 after excluding meanFD >= 0.3
nrow(collated_HCPD.xcp_headMotion) #5165 scans

write.csv(collated_HCPD.xcp_headMotion, "/cbica/projects/network_replication/input/HCPD/sample_selection/collated_HCPD.xcp_headMotion_20221224.csv")
```


## 5) include scans with at least 7 minutes of scan time
```{r scan_time}
collated_HCPD.xcp_headMotion <- read.csv("/cbica/projects/network_replication/input/HCPD/sample_selection/collated_HCPD.xcp_headMotion_20221224.csv")

# Calculate scan time for each subject 

# load cubids summary and files csv
CUBIDS_summary <- read.csv("/cbica/projects/network_replication/input/HCPD/CUBIDS_csvs/HCPD_summary_20221201.csv")
CUBIDS_summary <- CUBIDS_summary[,-c(1:4)]

fMRIinclude <- collated_HCPD.xcp_headMotion %>% mutate(KeyGroup = paste0("datatype-func_direction-", dir, "_run-0", run, "_suffix-bold_task-", task))

# edit KeyGroup for variants
fMRIinclude$KeyGroup[c(which(str_detect(fMRIinclude$sub, "0577358")))] <- paste0("acquisition-VARIANTNumVolumes_",fMRIinclude$KeyGroup[c(which(str_detect(fMRIinclude$sub, "0577358")))])
fMRIinclude$KeyGroup[c(which(str_detect(fMRIinclude$sub, "1529756")))] <- paste0("acquisition-VARIANTNumVolumes_",fMRIinclude$KeyGroup[c(which(str_detect(fMRIinclude$sub, "1529756")))])
  
fMRIinclude_CUBIDS <- merge(fMRIinclude, CUBIDS_summary[,c(2, 17, 22)], by ="KeyGroup")
  


fMRIinclude_CUBIDS <- fMRIinclude_CUBIDS %>% arrange(sub) %>% mutate(ScanTimeMinutes = NumVolumes*RepetitionTime/60) # sort dataframe by subject
fMRIinclude_CUBIDS_ScanTime <- fMRIinclude_CUBIDS %>% group_by(sub) %>% summarise(ScanTime_Total = sum(ScanTimeMinutes))

# variants can be included (total scan time > 7 min)
fMRIinclude_CUBIDS_ScanTime[c(which(str_detect(fMRIinclude_CUBIDS_ScanTime$sub, "0577358"))),]
fMRIinclude_CUBIDS_ScanTime[c(which(str_detect(fMRIinclude_CUBIDS_ScanTime$sub, "1529756"))),]
 
range(fMRIinclude_CUBIDS_ScanTime$ScanTime_Total) # 2.24000 42.66667
median(fMRIinclude_CUBIDS_ScanTime$ScanTime_Total) # 42.66667
  

subject_scanTime_exclude <- fMRIinclude_CUBIDS_ScanTime$sub[c(which(fMRIinclude_CUBIDS_ScanTime$ScanTime_Total < 7))] # exclude participants with less than 7 min of scan time
  
fMRIinclude_CUBIDS_scanTime <- fMRIinclude_CUBIDS[-c(which(fMRIinclude_CUBIDS$sub %in% subject_scanTime_exclude)),]  
fMRIinclude_CUBIDS <- fMRIinclude_CUBIDS_scanTime
length(unique(fMRIinclude_CUBIDS$sub)) # N=625 (excluded 4 participants)
nrow(fMRIinclude_CUBIDS) # 5159 scans

saveRDS(fMRIinclude_CUBIDS, "/cbica/projects/network_replication/input/HCPD/sample_selection/fMRIinclude_CUBIDS_20221226.RData")
 

fMRIinclude_CUBIDS_ScanTime <- fMRIinclude_CUBIDS %>% group_by(sub) %>% summarise(ScanTime_Total = sum(ScanTimeMinutes))
 
max(fMRIinclude_CUBIDS_ScanTime$ScanTime_Total) # 42 minutes and 40 seconds
range(fMRIinclude_CUBIDS_ScanTime$ScanTime_Total) # 7.466667 42.666667
median(fMRIinclude_CUBIDS_ScanTime$ScanTime_Total)  # 42.666667

fMRIinclude_CUBIDS_NumVols <- fMRIinclude_CUBIDS %>% group_by(sub) %>% summarise(NumVols_Total = sum(NumVolumes))
max(fMRIinclude_CUBIDS_NumVols$NumVols_Total) # 3200 volumes

# sensitivity analysis: rest only
fMRIinclude_CUBIDS_restOnly <- fMRIinclude_CUBIDS[c(which(fMRIinclude_CUBIDS$task=="rest")),] 
dim(fMRIinclude_CUBIDS_restOnly) #2324 scans
length(unique(fMRIinclude_CUBIDS_restOnly$sub)) # N=611
```
 

# Final Demographics Dataframe
```{r final_participant_list}

HCPD_FinalSample_CUBIDS <- readRDS("/cbica/projects/network_replication/input/HCPD/sample_selection/fMRIinclude_CUBIDS_20221226.RData")
 
final_participants <- data.frame(unique(HCPD_FinalSample_CUBIDS$sub))
names(final_participants) <- "sub" 
demographics <- demographics %>% mutate(sub = gsub("HCD", "sub-", src_subject_id))
final_demographics <- merge(demographics, final_participants, by = "sub")
 

## include average of relMeansRMSMotion and meanFD across the acquisitions included in calculating connectivity matrix 
# for each subject, take average relMeansRMSMotion and meanFD
subject <- c()
ses <- c()
avg_relMeansRMSMotion_vec <- c()
avg_meanFD_vec <- c()
for(i in c(1:length(unique(HCPD_FinalSample_CUBIDS$sub)))){
  indices <- which(HCPD_FinalSample_CUBIDS$sub == unique(HCPD_FinalSample_CUBIDS$sub)[i])
  avg_RMS <- mean(as.numeric(HCPD_FinalSample_CUBIDS$relMeansRMSMotion[indices]))
  avg_meanFD <- mean(as.numeric(HCPD_FinalSample_CUBIDS$meanFD[indices]))
  subject <- append(subject, unique(HCPD_FinalSample_CUBIDS$sub)[i])
  ses <- append(ses,HCPD_FinalSample_CUBIDS$ses[indices[1]])
  avg_relMeansRMSMotion_vec <- append(avg_relMeansRMSMotion_vec, avg_RMS)
  avg_meanFD_vec <- append(avg_meanFD_vec, avg_meanFD)
}  

HCPD_avgMotion <- data.frame(cbind(subject, ses, avg_meanFD_vec, avg_relMeansRMSMotion_vec))
names(HCPD_avgMotion) <- c("sub", "ses", "meanFD_avgSes", "relMeansRMSMotion_avgSes")
HCPD_avgMotion$meanFD_avgSes <- as.numeric(HCPD_avgMotion$meanFD_avgSes)
HCPD_avgMotion$relMeansRMSMotion_avgSes <- as.numeric(HCPD_avgMotion$relMeansRMSMotion_avgSes)
final_dem_df <- merge(final_demographics, HCPD_avgMotion, by="sub")
   
unique(final_dem_df$race)
 
length(which(final_dem_df$race=="White"))/nrow(final_dem_df)
# white = 395 - 63.2%
# asian = 48 - 7.7%%
# black = 69 - 11%
# other (native american, hawaiin or pacific islander) = 3 - 0.48%
# missing = 16 - 2.6%
# mixed = 94 - 15%

sd(final_dem_df$interview_age/12) # mean=14.5, SD=4.1
length(which(final_dem_df$sex=="F")) # 337 females

write.csv(final_dem_df, "/cbica/projects/network_replication/input/HCPD/sample_selection/HCPD_demographics_finalsample_20221226.csv")

```



# Final CIFTI File list (for creating connectivity matrices)
```{r ciftiFile_list, include=FALSE, cache=TRUE}
  
HCPD_FinalSample_CUBIDS <- readRDS("/cbica/projects/network_replication/input/HCPD/sample_selection/fMRIinclude_CUBIDS_20221226.RData")
 
 
atlases <- c("Glasser", "Gordon", "Schaefer217", "Schaefer417")
subject_list <- list()
ptseries_filenames <- list()
task_list <- list()
direction_list <- list()
run_list <- list()
atlas_list <- list()
 
for (i in c(1:nrow(HCPD_FinalSample_CUBIDS))) {
  for (j in c(1:length(atlases))){
  atlas <- atlases[j]
  subject <- HCPD_FinalSample_CUBIDS$sub[i]
  task <- HCPD_FinalSample_CUBIDS$task[i]
  direction <- HCPD_FinalSample_CUBIDS$dir[i]
  run <- HCPD_FinalSample_CUBIDS$run[i]
  task_list <- append(task, task_list)
  direction_list <- append(direction, direction_list)
  run_list <- append(run, run_list)
  atlas_list <- append(atlas, atlas_list)
  subject_list <- append(subject, subject_list)
  if (subject == "sub-1529756" | subject == "sub-0577358") {
  file <- paste0(subject, "_ses-V1_task-", task, "_acq-VARIANTNumVolumes_dir-", direction, "_run-", run, "_space-fsLR_atlas-", atlas, "_den-91k_timeseries.ptseries.nii")
  } else {
  file <- paste0(subject, "_ses-V1_task-", task, "_dir-", direction, "_run-", run, "_space-fsLR_atlas-", atlas, "_den-91k_timeseries.ptseries.nii")

  }
  ptseries_filenames <- append(file, ptseries_filenames)
  #print(paste(task, direction, atlas))
  }
  print(paste(subject, "done", i, "/", nrow(HCPD_FinalSample_CUBIDS)))
}

  
filenamesDF <- as.data.frame(do.call(rbind, ptseries_filenames))
subject_namesDF <- as.data.frame(do.call(rbind, subject_list))
task_namesDF <- as.data.frame(do.call(rbind, task_list))
direction_namesDF <- as.data.frame(do.call(rbind, direction_list))
run_namesDF <- as.data.frame(do.call(rbind, run_list))
atlas_namesDF <- as.data.frame(do.call(rbind, atlas_list))
  
file_paths <- as.data.frame(cbind(subject_namesDF, task_namesDF, direction_namesDF, run_namesDF, atlas_namesDF, filenamesDF))
names(file_paths) <- c("subject", "task", "direction", "run", "atlas", "filenames")
 
file_paths <- file_paths %>% mutate(path = paste0("/cbica/projects/network_replication/input/HCPD/hcpd_xcp/", subject, "/", filenames)) %>% mutate(sub_task_direction_run = paste0(subject, "_", task, "_", direction, "_", run))
HCPD_FinalSample_CUBIDS <- HCPD_FinalSample_CUBIDS %>% mutate(sub_task_direction_run = paste0(sub, "_", task, "_", dir, "_", run))
file_paths_restOnly <- file_paths[which(file_paths$task == "rest"),]

file_paths_FINAL <- merge(file_paths, HCPD_FinalSample_CUBIDS[, c(1, ncol(HCPD_FinalSample_CUBIDS))], by = "sub_task_direction_run") 
file_paths_restOnly_FINAL <- merge(file_paths_restOnly, HCPD_FinalSample_CUBIDS[, c(1, ncol(HCPD_FinalSample_CUBIDS))], by = "sub_task_direction_run")
 
length(unique(file_paths_FINAL$sub_task_direction_run)) # 5159 scans 
length(unique(file_paths_FINAL$subject)) #N=625

length(unique(file_paths_restOnly_FINAL$sub_task_direction_run)) # 2324 scans
length(unique(file_paths_restOnly_FINAL$subject)) #N=611
  
HCPD_qc_filenames_atlases <- list(HCPD_FinalSample_CUBIDS, file_paths_FINAL) 
HCPD_qc_filenames_atlases_restOnly <- list(HCPD_FinalSample_CUBIDS[c(which(HCPD_FinalSample_CUBIDS$task=="rest")),], file_paths_restOnly_FINAL) 
  

saveRDS(HCPD_qc_filenames_atlases, "/cbica/projects/network_replication/input/HCPD/sample_selection/HCPD_FinalSample_withCUBIDS_20221227.RData")
saveRDS(HCPD_qc_filenames_atlases_restOnly, "/cbica/projects/network_replication/input/HCPD/sample_selection/HCPD_FinalSample_withCUBIDS_restOnly_20221227.RData")
 
```



# Sensitivity Analysis: Final demographics for rest only
- include participants with at least 6 minutes of rest-only scan time
```{r}

HCPD_qc_filenames_atlases_restOnly <- readRDS("/cbica/projects/network_replication/input/HCPD/sample_selection/HCPD_FinalSample_withCUBIDS_restOnly_20221227.RData")

### Include participants with >= 6 minutes of resting state fMRI
fMRIinclude_CUBIDS_ScanTime_restOnly <- HCPD_qc_filenames_atlases_restOnly[[1]] %>% group_by(sub) %>% summarise(ScanTime_Total = sum(ScanTimeMinutes))
 
range(fMRIinclude_CUBIDS_ScanTime_restOnly$ScanTime_Total)
fMRIinclude_CUBIDS_ScanTime_restOnly$sub[c(which(fMRIinclude_CUBIDS_ScanTime_restOnly$ScanTime_Total < 6))]
length(which(fMRIinclude_CUBIDS_ScanTime_restOnly$ScanTime_Total >= 6)) # 611


final_participants_restOnly <- data.frame(fMRIinclude_CUBIDS_ScanTime_restOnly$sub[c(which(fMRIinclude_CUBIDS_ScanTime_restOnly$ScanTime_Total >= 6))])
names(final_participants_restOnly) <- "sub" 
 

max(fMRIinclude_CUBIDS_ScanTime_restOnly$ScanTime_Total) #25.5 minutes

fMRIinclude_CUBIDS_NumVols_restOnly <- HCPD_qc_filenames_atlases_restOnly[[1]] %>% group_by(sub) %>% summarise(NumVolsTotal = sum(NumVolumes))
max(fMRIinclude_CUBIDS_NumVols_restOnly$NumVolsTotal) #1912 volumes


HCPD_FinalSample_CUBIDS_restOnly <- HCPD_qc_filenames_atlases_restOnly[[1]] 
HCPD_FinalSample_CUBIDS_restOnly <- merge(HCPD_FinalSample_CUBIDS_restOnly, final_participants_restOnly)

names(HCPD_qc_filenames_atlases_restOnly[[2]])[2] <- "sub"
HCPD_qc_filenames_atlases_restOnly_final <- merge(HCPD_qc_filenames_atlases_restOnly[[2]], final_participants_restOnly)
HCPD_qc_filenames_atlases_restOnly_final <- list(HCPD_FinalSample_CUBIDS_restOnly, HCPD_qc_filenames_atlases_restOnly_final)
dim(HCPD_qc_filenames_atlases_restOnly_final[[1]]) #2324 scans

saveRDS(HCPD_qc_filenames_atlases_restOnly_final,"/cbica/projects/network_replication/input/HCPD/sample_selection/HCPD_FinalSample_withCUBIDS_restOnly_20230203.RData")
 
 
demographics <- demographics %>% mutate(sub = gsub("HCD", "sub-", src_subject_id))
final_demographics_restOnly <- merge(demographics, final_participants_restOnly, by = "sub")
 

## include average of relMeansRMSMotion and meanFD across the acquisitions included in calculating connectivity matrix 
# for each subject, take average relMeansRMSMotion and meanFD
subject <- c()
ses <- c()
avg_relMeansRMSMotion_vec <- c()
avg_meanFD_vec <- c()
for(i in c(1:length(unique(HCPD_FinalSample_CUBIDS_restOnly$sub)))){
  indices <- which(HCPD_FinalSample_CUBIDS_restOnly$sub == unique(HCPD_FinalSample_CUBIDS_restOnly$sub)[i])
  avg_RMS <- mean(as.numeric(HCPD_FinalSample_CUBIDS_restOnly$relMeansRMSMotion[indices]))
  avg_meanFD <- mean(as.numeric(HCPD_FinalSample_CUBIDS_restOnly$meanFD[indices]))
  subject <- append(subject, unique(HCPD_FinalSample_CUBIDS_restOnly$sub)[i])
  ses <- append(ses,HCPD_FinalSample_CUBIDS_restOnly$ses[indices[1]])
  avg_relMeansRMSMotion_vec <- append(avg_relMeansRMSMotion_vec, avg_RMS)
  avg_meanFD_vec <- append(avg_meanFD_vec, avg_meanFD)
}  
 

HCPD_avgMotion <- data.frame(cbind(subject, ses, avg_meanFD_vec, avg_relMeansRMSMotion_vec))
names(HCPD_avgMotion) <- c("sub", "ses", "meanFD_avgSes", "relMeansRMSMotion_avgSes")
HCPD_avgMotion$meanFD_avgSes <- as.numeric(HCPD_avgMotion$meanFD_avgSes)
HCPD_avgMotion$relMeansRMSMotion_avgSes <- as.numeric(HCPD_avgMotion$relMeansRMSMotion_avgSes)
final_dem_restOnly_df <- merge(final_demographics_restOnly, HCPD_avgMotion, by="sub")
  

length(which(final_dem_restOnly_df$sex=="F")) # 329 females

write.csv(final_dem_restOnly_df, "/cbica/projects/network_replication/input/HCPD/sample_selection/HCPD_demographics_finalsample_restOnly_20230103.csv")
``` 
