---
title: "WNC GAMs: PNC (Schaefer200x17)"
author: "Valerie Jill Sydnor adapted by Audrey Luo"
output:
  html_document:
    code_folding: show
    highlight: haddock
    theme: lumen
    toc: yes
    toc_depth: 4
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
source("/cbica/projects/network_replication/adapted_Rscripts/GAM_functions.R")
```


**Prepare WNC + Demographics data frame for GAMs**

```{r}
participants <- read.csv("/cbica/projects/network_replication/adapted_Rscripts/participants_allIDs.csv") #final study sample pnc IDs (bblid/scanid) from Adam Pines's multiscale paper
demographics <- read.csv("/cbica/projects/network_replication/PNC/n1601_demographics_go1_20161212.csv") #PNC demographics information
demographics <- demographics %>% mutate(age = (ageAtScan1/12)) #format age variable
demographics$sex <- as.factor(demographics$sex) #format sex variable

demographics <- merge(participants, demographics, by="scanid") #get demographics for final study sample only via ID matching
relRMS <- read.csv("/cbica/projects/network_replication/PNC/qc_files/RBC_PNC_relMeans.csv") 
demographics <- merge(demographics, relRMS, by="rbcid") #add motion information to demographics df
```

# make WNC-demographics .csv's
```{r} 
WNC_subxparcel_matrix_schaefer200 <- read.csv("/cbica/projects/network_replication/WNC/WNC_subxparcel_matrix_schaefer200x17.csv") #participant x schaefer region WNC spreadsheet
WNC_subxparcel_matrix_schaefer200 <- WNC_subxparcel_matrix_schaefer200[-c(1:7, 24, 690, 691),] # the subjects that should've been removed earlier 
names(WNC_subxparcel_matrix_schaefer200)
col_rm <- as.numeric(levels(as.factor(as.data.frame(which(is.na(WNC_subxparcel_matrix_schaefer200), arr.ind=TRUE))$col)))
WNC_subxparcel_matrix_schaefer200 <- WNC_subxparcel_matrix_schaefer200[, -col_rm]
WNC.schaefer200.pnc <- merge(WNC_subxparcel_matrix_schaefer200, demographics, by="rbcid") #get schaefer WNC data and demographics for final study sample via ID matching
names(WNC.schaefer200.pnc) <- gsub('X17Networks_', "", names(WNC.schaefer200.pnc))
#write.csv(WNC.schaefer200.pnc, "/cbica/projects/network_replication/WNC/WNCschaefer200x17_demographics_finalsample.csv")
 
 
```

# load WNC-demographics df's
```{r}
WNC.schaefer200.pnc <- read.csv('/cbica/projects/network_replication/WNC/WNCschaefer200x17_demographics_finalsample.csv')

names(WNC.schaefer200.pnc)
wide_df <- WNC.schaefer200.pnc[, c(3:190, 194, 205, 206)]
```


# edit parcel labels to reflect SNR mask
```{r}
schaefer200.parcel.labels <- read.csv("/cbica/projects/network_replication/atlases/parcellations/schaefer200x17_regionlist.csv", header = T) #schaefer parcel names in order of surface data
names(schaefer200.parcel.labels)[2] <- "orig_parcelname"
# remove parcels using SNR mask
SNR.mask.schaefer200 <- read.csv("/cbica/projects/network_replication/atlases/Masks/SNRmask_schaefer200x17.csv")
rm <- which(SNR.mask.schaefer200$SNR.mask == 0)
# also remove X17Networks_LH_LimbicA_TempPole_4 -- all of its within-network parcels are NA'd out by the mask, so it doesn't have a WNC value
rm <- append(56, rm)
schaefer200.parcel.labels <- schaefer200.parcel.labels[-rm,]
  

##### edited
# load parcellated SA axis
schaefer200_SAaxis_cifti <- read_cifti("/cbica/projects/network_replication/SAaxis/SensorimotorAssociation_Axis_parcellated/SensorimotorAssociation.Axis.Schaefer200.17Networks.pscalar.nii")  

schaefer200_SAaxis <- as.data.frame(cbind(rank(schaefer200_SAaxis_cifti$data), names(schaefer200_SAaxis_cifti$Parcel)))
colnames(schaefer200_SAaxis) <- c("SA.axis_rank","label")

# apply SNR mask
schaefer200_SAaxis[which(SNR.mask.schaefer200 == 0),] <- NA
schaefer200_SAaxis <- schaefer200_SAaxis[-rm,]
schaefer200_SAaxis$SA.axis_rank <- as.numeric(schaefer200_SAaxis$SA.axis_rank)
```


# put data into long format
```{r}
######## edited
long_df<- wide_df %>% pivot_longer(cols = !contains(c("age","sex", "RMSmotion")),names_to = "parcel",values_to = "WNC")
smooth_fits <- long_df %>% group_by(parcel) %>% do(fit = smooth_estimates(gam(WNC ~ s(age,k=4,fx=F),data=.))) %>% unnest(fit)
  
smooth_fits$label <- smooth_fits$parcel
schaefer200_SAaxis$label <- gsub("17Networks_", "", schaefer200_SAaxis$label)
smooth_fits <- left_join(smooth_fits, schaefer200_SAaxis, by = "label")
  
smooth_fits$SA.axis_rank <- as.integer(smooth_fits$SA.axis_rank)
  
smooth_fits <- smooth_fits %>% mutate(SA.axis_percentile_bin = ntile(smooth_fits$SA.axis_rank, 10))
 
ggplot(smooth_fits,aes(age,est,group=SA.axis_rank)) + geom_line(data = smooth_fits, size=.5, alpha = .6, aes(color=SA.axis_rank)) + scale_color_gradient2(low="#6f1282",high = "goldenrod1", mid = "#EBDAFF", midpoint = median(schaefer200_SAaxis$SA.axis_rank)) + theme_classic()

# plot association trajectories only
smooth_fits_assoc <- smooth_fits[which(smooth_fits$SA.axis_rank > 150),]
ggplot(smooth_fits_assoc,aes(age,est,group=SA.axis_rank)) + geom_line(data = smooth_fits_assoc, size=.5, alpha = .6) + theme_classic()
#plot SM trajectories only
smooth_fits_SM <- smooth_fits[which(smooth_fits$SA.axis_rank < 50),]
ggplot(smooth_fits_SM,aes(age,est,group=SA.axis_rank)) + geom_line(data = smooth_fits_SM, size=.5, alpha = .6) + theme_classic()
ggplot(smooth_fits_assoc,aes(age,est,group=SA.axis_rank)) + geom_line(data = smooth_fits_assoc, size=.5, alpha = .6) + theme_classic()


# plot trajectories by SA rank percentile bins
smooth_fits.bins <- smooth_fits %>% group_by(age, SA.axis_percentile_bin) %>% do(est.mean = mean(.$est)) %>% unnest(cols = c(est.mean))
 
smooth_fits.bins <- arrange(smooth_fits.bins, SA.axis_percentile_bin)
 
ggplot(smooth_fits.bins, aes(age,est.mean,group=SA.axis_percentile_bin)) + geom_line(data = smooth_fits.bins, size=1, alpha = .6, aes(color=SA.axis_percentile_bin)) + scale_color_gradient2(low="#6f1282",high = "goldenrod1", mid = "#EBDAFF", midpoint = 5) + theme_classic()
 
 
```


**Fit GAMs**

Fit GAM (WNC ~ s(age) + sex + RMSmotion)) per each region in atlas and save out statistics and derivative-based characteristics

GAMs for Schaefer200
```{r}
gam.WNC.age.schaefer200 <- matrix(data=NA, nrow=dim(schaefer200.parcel.labels)[1], ncol=9) #empty matrix to save gam.fit output to
 
# schaefer200 parcel labels and the labels from WNC.schaefer200.pnc don't currently match. And I don't think parcelnames can begin with a number. following 2 lines fixes this
schaefer200.parcel.labels$orig_parcelname <- gsub('17Networks_', "", schaefer200.parcel.labels$orig_parcelname)
 

# get GAMs for WNC.schaefer200.pnc - which includes schaefer200 WNC data and demographics
for(row in c(1:nrow(schaefer200.parcel.labels))){ #for each schaefer200 region
  region <- schaefer200.parcel.labels$orig_parcelname[row] 
  GAM.RESULTS <- gam.fit(measure = "WNC", atlas = "schaefer200", dataset = "pnc", region = region, smooth_var = "age", covariates = "sex + RMSmotion") #run the gam.fit function
  gam.WNC.age.schaefer200[row,] <- GAM.RESULTS}
 
 
gam.WNC.age.schaefer200 <- as.data.frame(gam.WNC.age.schaefer200)
colnames(gam.WNC.age.schaefer200) <- c("label","GAM.age.Fvalue","GAM.age.pvalue","GAM.age.AdjRsq","Anova.age.pvalue","age.onsetchange","age.peakchange","maxage.WNC.increase","age.maturation")
cols = c(2:9)    
gam.WNC.age.schaefer200[,cols] = apply(gam.WNC.age.schaefer200[,cols], 2, function(x) as.numeric(as.character(x)))
gam.WNC.age.schaefer200 <- gam.WNC.age.schaefer200 %>% mutate(significant = (Anova.age.pvalue < 0.05))
#write.csv(gam.WNC.age.schaefer200, "/cbica/projects/network_replication/WNC/GAM/GAMresults.WNC.age.schaefer200x17.csv", row.names = F, quote = F)
```
 
# load GAMs output
```{r} 
gam.WNC.age.schaefer200 <- read.csv("/cbica/projects/network_replication/WNC/GAM/GAMresults.WNC.age.schaefer200x17.csv")
```



**Estimate GAM smooths based on model-predicted data and save out predicted y data**
Estimate GAM smooths - Schaefer200
```{r}
gam.smooths.schaefer200 <- matrix(data=NA, ncol=7) #empty matrix to save gam.predsmooth fits to
colnames(gam.smooths.schaefer200) <- c("age","fit","se.fit","selo","sehi","index","label")

gam.peaks.schaefer200 <- matrix(data=NA, ncol=2) #empty matrix to save measure peaks to (value of x when y is predicted to be maximal)
colnames(gam.peaks.schaefer200) <- c("label","age.peak")


for(row in c(1:nrow(schaefer200.parcel.labels))){ #for each schaefer200 region
  
  region <- schaefer200.parcel.labels$orig_parcelname[row] #get the region name
  GAM.SMOOTH <- gam.predsmooth(measure = "WNC", atlas = "schaefer200", dataset = "pnc", region = region, smooth_var = "age", covariates = "sex + RMSmotion") #run the gam.predsmooth function
  
  preddata <- as.data.frame(GAM.SMOOTH[3]) #get predicted.smooth df from function output
  preddata$index <- rep(x=row, 1000) #region index
  preddata$label <- rep(x=GAM.SMOOTH[1], 1000) #label
  gam.smooths.schaefer200 <- rbind(gam.smooths.schaefer200, preddata)
  
  datapeak <- as.data.frame(cbind(GAM.SMOOTH[1], GAM.SMOOTH[2]))
  colnames(datapeak) <- c("label","age.peak")
  gam.peaks.schaefer200 <- rbind(gam.peaks.schaefer200, datapeak)
}
gam.smooths.schaefer200 <- gam.smooths.schaefer200[-1,] #remove empty initilization row
gam.smooths.schaefer200$label <- as.character(gam.smooths.schaefer200$label)
gam.peaks.schaefer200 <- gam.peaks.schaefer200[-1,] #remove empty initilization row
gam.peaks.schaefer200$label <- as.character(gam.peaks.schaefer200$label)
gam.peaks.schaefer200$age.peak <- as.numeric(gam.peaks.schaefer200$age.peak)
 
#write.csv(gam.smooths.schaefer200,"/cbica/projects/network_replication/WNC/GAM/GAMsmoothfits.WNC.age.schaefer200x17.csv", row.names = F, quote = F)
#write.csv(gam.peaks.schaefer200, "/cbica/projects/network_replication/WNC/GAM/GAMpeaks.WNC.age.schaefer200x17.csv", row.names = F, quote = F)
 
```
