---
title: "GBC GAMs: PNC"
author: "Valerie Jill Sydnor" adapted by Audrey
output:
  html_document:
    code_folding: show
    highlight: haddock
    theme: lumen
    toc: yes
    toc_depth: 4
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
source("/cbica/projects/network_replication/adapted_Rscripts/GAM_functions.R")
```


**Prepare GBC + Demographics data frame for GAMs**
```{r}
participants <- read.csv("/cbica/projects/network_replication/adapted_Rscripts/participants_allIDs.csv") #final study sample pnc IDs (bblid/scanid) from Adam Pines's multiscale paper
demographics <- read.csv("/cbica/projects/network_replication/PNC/n1601_demographics_go1_20161212.csv") #PNC demographics information
demographics <- demographics %>% mutate(age = (ageAtScan1/12)) #format age variable
demographics$sex <- as.factor(demographics$sex) #format sex variable

demographics <- merge(participants, demographics, by="scanid") #get demographics for final study sample only via ID matching
relRMS <- read.csv("/cbica/projects/network_replication/PNC/qc_files/RBC_PNC_relMeans.csv") 
demographics <- merge(demographics, relRMS, by="rbcid") #add motion information to demographics df
```


# make GBC-demographics .csv's
```{r}
gbc.subxparcel.matrix.glasser <- read.csv("/cbica/projects/network_replication/GBC/GBC_subxparcel_matrix_glasser.csv") #participant x glasser region GBC spreadsheet
#gbc.subxparcel.matrix.glasser has columns (roi's) that are NA's that need to be removed. those NA's correspond to parcels to be removed because of the SNRmask. Also need to remove the rows (corresponding to subjects that are currently missing files)
# need to remove 10 rows and 24 columns
gbc.subxparcel.matrix.glasser <- gbc.subxparcel.matrix.glasser[-c(1:7, 24, 690, 691),] # the subjects that should've been removed earlier 
col_rm <- as.numeric(levels(as.factor(as.data.frame(which(is.na(gbc.subxparcel.matrix.glasser), arr.ind=TRUE))$col)))
gbc.subxparcel.matrix.glasser <- gbc.subxparcel.matrix.glasser[, -col_rm]
gbc.glasser.pnc <- merge(gbc.subxparcel.matrix.glasser, demographics, by="rbcid") #get glasser GBC data and demographics for final study sample via ID matching
#write.csv(gbc.glasser.pnc, "/cbica/projects/network_replication/GBC/GBCglasser_demographics_finalsample.csv", quote = F, row.names = F)
 
```


# load GBC-demographics df's
```{r}
gbc.glasser.pnc <- read.csv('/cbica/projects/network_replication/GBC/GBCglasser_demographics_finalsample.csv')
```


# edit parcel labels to reflect SNR mask
```{r}
glasser.parcel.labels <- read.csv("/cbica/projects/network_replication/atlases/parcellations/glasser360_regionlist.csv", header = T) #glasser parcel names in order of surface data
names(glasser.parcel.labels)[2] <- "orig_parcelname"
# remove parcels using SNR mask
SNR.mask.glasser360 <- read.csv("/cbica/projects/network_replication/atlases/Masks/SNRmask_glasser360.csv")
rm <- which(SNR.mask.glasser360$SNR.mask == 0)
glasser.parcel.labels <- glasser.parcel.labels[-rm,]
 
```

**Fit GAMs**

Fit GAM (GBC ~ s(age) + sex + RMSmotion)) per each region in atlas and save out statistics and derivative-based characteristics

GAMs for Glasser
```{r}
gam.GBC.age.glasser <- matrix(data=NA, nrow=dim(glasser.parcel.labels)[1], ncol=9) #empty matrix to save gam.fit output to
 
# get GAMs for gbc.glasser.pnc - which includes glasser GBC data and demographics
for(row in c(1:nrow(glasser.parcel.labels))){ #for each glasser region
  region <- glasser.parcel.labels$orig_parcelname[row] 
  GAM.RESULTS <- gam.fit(measure = "gbc", atlas = "glasser", dataset = "pnc", region = region, smooth_var = "age", covariates = "sex + RMSmotion") #run the gam.fit function
  gam.GBC.age.glasser[row,] <- GAM.RESULTS}

  
gam.GBC.age.glasser <- as.data.frame(gam.GBC.age.glasser)
colnames(gam.GBC.age.glasser) <- c("label","GAM.age.Fvalue","GAM.age.pvalue","GAM.age.AdjRsq","Anova.age.pvalue","age.onsetchange","age.peakchange","maxage.GBC.increase","age.maturation")
cols = c(2:9)    
gam.GBC.age.glasser[,cols] = apply(gam.GBC.age.glasser[,cols], 2, function(x) as.numeric(as.character(x)))
gam.GBC.age.glasser <- gam.GBC.age.glasser %>% mutate(significant = (Anova.age.pvalue < 0.05))

#write.csv(gam.GBC.age.glasser, "/cbica/projects/network_replication/GBC/GAM/GAMresults.GBC.age.glasser.csv", row.names = F, quote = F)

```

 
# load GAMs output
```{r}

gam.GBC.age.glasser <- read.csv("/cbica/projects/network_replication/GBC/GAM/GAMresults.GBC.age.glasser.csv")

```



**Estimate GAM smooths based on model-predicted data and save out predicted y data**

Estimate GAM smooths - Glasser
```{r}
gam.smooths.glasser <- matrix(data=NA, ncol=7) #empty matrix to save gam.predsmooth fits to
colnames(gam.smooths.glasser) <- c("age","fit","se.fit","selo","sehi","index","label")

gam.peaks.glasser <- matrix(data=NA, ncol=2) #empty matrix to save measure peaks to (value of x when y is predicted to be maximal)
colnames(gam.peaks.glasser) <- c("label","age.peak")

for(row in c(1:nrow(glasser.parcel.labels))){ #for each glasser region
  
  region <- glasser.parcel.labels$orig_parcelname[row] #get the region name
  GAM.SMOOTH <- gam.predsmooth(measure = "gbc", atlas = "glasser", dataset = "pnc", region = region, smooth_var = "age", covariates = "sex + RMSmotion") #run the gam.predsmooth function
  
  preddata <- as.data.frame(GAM.SMOOTH[3]) #get predicted.smooth df from function output
  preddata$index <- rep(x=row, 1000) #region index
  preddata$label <- rep(x=GAM.SMOOTH[1], 1000) #label
  gam.smooths.glasser <- rbind(gam.smooths.glasser, preddata)
  
  datapeak <- as.data.frame(cbind(GAM.SMOOTH[1], GAM.SMOOTH[2]))
  colnames(datapeak) <- c("label","age.peak")
  gam.peaks.glasser <- rbind(gam.peaks.glasser, datapeak)
}
gam.smooths.glasser <- gam.smooths.glasser[-1,] #remove empty initialization row
gam.smooths.glasser$label <- as.character(gam.smooths.glasser$label)
gam.peaks.glasser <- gam.peaks.glasser[-1,] #remove empty initialization row
gam.peaks.glasser$label <- as.character(gam.peaks.glasser$label)
gam.peaks.glasser$age.peak <- as.numeric(gam.peaks.glasser$age.peak)

#write.csv(gam.smooths.glasser,"/cbica/projects/network_replication/GBC/GAM/GAMsmoothfits.GBC.age.glasser.csv", row.names = F, quote = F)
#write.csv(gam.peaks.glasser, "/cbica/projects/network_replication/GBC/GAM/GAMpeaks.GBC.age.glasser.csv", row.names = F, quote = F)
 
```