---
title: "WNC GAMs: PNC (Schaefer200x7)"
author: "Valerie Jill Sydnor" adapted by Audrey
output:
  html_document:
    code_folding: show
    highlight: haddock
    theme: lumen
    toc: yes
    toc_depth: 4
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(magrittr)
library(tidyr)
library(gratia)
library(mgcv)

library(ciftiTools)
ciftiTools.setOption('wb_path', '/Applications/workbench/')
library(gifti)
library(cifti)
source("/cbica/projects/network_replication/adapted_Rscripts/GAM_functions.R")
```


**Prepare WNC + Demographics data frame for GAMs**

```{r}
participants <- read.csv("/cbica/projects/network_replication/adapted_Rscripts/PNC_scripts/participants_allIDs.csv") #final study sample pnc IDs (bblid/scanid) from Adam Pines's multiscale paper
demographics <- read.csv("/cbica/projects/network_replication/PNC/n1601_demographics_go1_20161212.csv") #PNC demographics information
demographics <- demographics %>% mutate(age = (ageAtScan1/12)) #format age variable
demographics$sex <- as.factor(demographics$sex) #format sex variable

demographics <- merge(participants, demographics, by="scanid") #get demographics for final study sample only via ID matching
relRMS <- read.csv("/cbica/projects/network_replication/PNC/qc_files/RBC_PNC_relMeans.csv") 
demographics <- merge(demographics, relRMS, by="rbcid") #add motion information to demographics df
```

# make WNC-demographics .csv's
```{r} 
WNC_subxparcel_matrix_schaefer200 <- read.csv("/cbica/projects/network_replication/WNC/WNC_subxparcel_matrix_schaefer200x7.csv") #participant x schaefer region WNC spreadsheet
WNC_subxparcel_matrix_schaefer200 <- WNC_subxparcel_matrix_schaefer200[-c(1:7, 24, 690, 691),] # the subjects that should've been removed earlier 
col_rm <- as.numeric(levels(as.factor(as.data.frame(which(is.na(WNC_subxparcel_matrix_schaefer200), arr.ind=TRUE))$col)))
WNC_subxparcel_matrix_schaefer200 <- WNC_subxparcel_matrix_schaefer200[, -col_rm]
WNC.schaefer200.pnc <- merge(WNC_subxparcel_matrix_schaefer200, demographics, by="rbcid") #get schaefer WNC data and demographics for final study sample via ID matching
names(WNC.schaefer200.pnc) <- gsub('X7Networks_', "", names(WNC.schaefer200.pnc))
#write.csv(WNC.schaefer200.pnc, "/cbica/projects/network_replication/WNC/WNCschaefer200x7_demographics_finalsample.csv")
 
wide_df <- WNC.schaefer200.pnc[, c(2:190, 194, 205, 206)]
 
#write.csv(wide_df, "/cbica/projects/network_replication/WNC/WNCschaefer200x7_wideDf.csv") 

```

# load WNC-demographics df's
```{r}
WNC.schaefer200.pnc <- read.csv('/cbica/projects/network_replication/WNC/WNCschaefer200x7_demographics_finalsample.csv')

 
```


# edit parcel labels to reflect SNR mask
```{r}
schaefer200.parcel.labels <- read.csv("/cbica/projects/network_replication/atlases/parcellations/schaefer200x7_ggseg_reordered.csv", header = T) #schaefer parcel names in order of surface data
names(schaefer200.parcel.labels)[2] <- "orig_parcelname"
# remove parcels using SNR mask
SNR.mask.schaefer200 <- read.csv('/cbica/projects/network_replication/atlases/Masks/SNRmask_schaefer200x7_reordered.csv') 
rm <- which(SNR.mask.schaefer200$SNR.mask == 0)
schaefer200.parcel.labels <- schaefer200.parcel.labels[-rm,]

# load parcellated SA axis
schaefer200_SAaxis_cifti <- read_cifti("/cbica/projects/network_replication/SAaxis/SensorimotorAssociation_Axis_parcellated/SensorimotorAssociation.Axis.Schaefer200.7Networks.pscalar.nii")  

schaefer200_SAaxis <- as.data.frame(cbind(rank(schaefer200_SAaxis_cifti$data), names(schaefer200_SAaxis_cifti$Parcel)))
colnames(schaefer200_SAaxis) <- c("SA.axis_rank","label")

# reorder SA axis (7 to 17)
index_schaefer200x7to17 <- read.csv("/cbica/projects/network_replication/software/schaefer7to17_reordering/index_schaefer200x7to17.csv", header=F)
 
index_schaefer200x7to17$V1 <- as.numeric(index_schaefer200x7to17$V1)
schaefer200_SAaxis <-schaefer200_SAaxis[index_schaefer200x7to17$V1,]
#as.matrix(cbind(schaefer200_SAaxis, schaefer200.parcel.labels))


# apply SNR mask
schaefer200_SAaxis[which(SNR.mask.schaefer200 == 0),] <- NA
schaefer200_SAaxis <- na.omit(schaefer200_SAaxis) 
schaefer200_SAaxis$SA.axis_rank <- as.numeric(schaefer200_SAaxis$SA.axis_rank)
```


**Fit GAMs**

Fit GAM (WNC ~ s(age) + sex + RMSmotion)) per each region in atlas and save out statistics and derivative-based characteristics

GAMs for Schaefer200
```{r}
gam.WNC.age.schaefer200 <- matrix(data=NA, nrow=dim(schaefer200.parcel.labels)[1], ncol=9) #empty matrix to save gam.fit output to
 
# schaefer200 parcel labels and the labels from WNC.schaefer200.pnc don't currently match. And I don't think parcelnames can begin with a number. following 2 lines fixes this
schaefer200.parcel.labels$orig_parcelname <- gsub('7Networks_', "", schaefer200.parcel.labels$orig_parcelname)


# get GAMs for WNC.schaefer200.pnc - which includes schaefer200 WNC data and demographics
for(row in c(1:nrow(schaefer200.parcel.labels))){ #for each schaefer200 region
  region <- schaefer200.parcel.labels$orig_parcelname[row] 
  GAM.RESULTS <- gam.fit(measure = "WNC", atlas = "schaefer200", dataset = "pnc", region = region, smooth_var = "age", covariates = "sex + RMSmotion") #run the gam.fit function
  gam.WNC.age.schaefer200[row,] <- GAM.RESULTS}


 
gam.WNC.age.schaefer200 <- as.data.frame(gam.WNC.age.schaefer200)
colnames(gam.WNC.age.schaefer200) <- c("label","GAM.age.Fvalue","GAM.age.pvalue","GAM.age.AdjRsq","Anova.age.pvalue","age.onsetchange","age.peakchange","maxage.WNC.increase","age.maturation")
cols = c(2:9)    
gam.WNC.age.schaefer200[,cols] = apply(gam.WNC.age.schaefer200[,cols], 2, function(x) as.numeric(as.character(x)))
gam.WNC.age.schaefer200 <- gam.WNC.age.schaefer200 %>% mutate(significant = (Anova.age.pvalue < 0.05))
#write.csv(gam.WNC.age.schaefer200, "/cbica/projects/network_replication/WNC/GAM/GAMresults.WNC.age.schaefer200x7.csv", row.names = F, quote = F)
```
 
# load GAMs output
```{r} 
gam.WNC.age.schaefer200 <- read.csv("/cbica/projects/network_replication/WNC/GAM/GAMresults.WNC.age.schaefer200x7.csv")
```



**Estimate GAM smooths based on model-predicted data and save out predicted y data**
Estimate GAM smooths - Schaefer200
```{r}
gam.smooths.schaefer200 <- matrix(data=NA, ncol=7) #empty matrix to save gam.predsmooth fits to
colnames(gam.smooths.schaefer200) <- c("age","fit","se.fit","selo","sehi","index","label")

gam.peaks.schaefer200 <- matrix(data=NA, ncol=2) #empty matrix to save measure peaks to (value of x when y is predicted to be maximal)
colnames(gam.peaks.schaefer200) <- c("label","age.peak")


for(row in c(1:nrow(schaefer200.parcel.labels))){ #for each schaefer200 region
  
  region <- schaefer200.parcel.labels$orig_parcelname[row] #get the region name
  GAM.SMOOTH <- gam.predsmooth(measure = "WNC", atlas = "schaefer200", dataset = "pnc", region = region, smooth_var = "age", covariates = "sex + RMSmotion") #run the gam.predsmooth function
  
  preddata <- as.data.frame(GAM.SMOOTH[3]) #get predicted.smooth df from function output
  preddata$index <- rep(x=row, 1000) #region index
  preddata$label <- rep(x=GAM.SMOOTH[1], 1000) #label
  gam.smooths.schaefer200 <- rbind(gam.smooths.schaefer200, preddata)
  
  datapeak <- as.data.frame(cbind(GAM.SMOOTH[1], GAM.SMOOTH[2]))
  colnames(datapeak) <- c("label","age.peak")
  gam.peaks.schaefer200 <- rbind(gam.peaks.schaefer200, datapeak)
}
gam.smooths.schaefer200 <- gam.smooths.schaefer200[-1,] #remove empty initilization row
gam.smooths.schaefer200$label <- as.character(gam.smooths.schaefer200$label)
gam.peaks.schaefer200 <- gam.peaks.schaefer200[-1,] #remove empty initilization row
gam.peaks.schaefer200$label <- as.character(gam.peaks.schaefer200$label)
gam.peaks.schaefer200$age.peak <- as.numeric(gam.peaks.schaefer200$age.peak)
 
#write.csv(gam.smooths.schaefer200,"/cbica/projects/network_replication/WNC/GAM/GAMsmoothfits.WNC.age.schaefer200x7.csv", row.names = F, quote = F)
#write.csv(gam.peaks.schaefer200, "/cbica/projects/network_replication/WNC/GAM/GAMpeaks.WNC.age.schaefer200x7.csv", row.names = F, quote = F)
 
```



# Smooth fits long format
```{r}
long_df<- wide_df %>% pivot_longer(cols = !contains(c("age","sex", "RMSmotion")),names_to = "parcel",values_to = "WNC")
smooth_fits <- long_df %>% group_by(parcel) %>% do(fit = smooth_estimates(gam(WNC ~ s(age,k=3,fx=F),data=.))) %>% unnest(fit)
  
smooth_fits$label <- smooth_fits$parcel
schaefer200_SAaxis$label <- gsub("7Networks_", "", schaefer200_SAaxis$label)
smooth_fits <- left_join(smooth_fits, schaefer200_SAaxis, by = "label")
  
smooth_fits$SA.axis_rank <- as.integer(smooth_fits$SA.axis_rank)
  
smooth_fits <- smooth_fits %>% mutate(SA.axis_percentile_bin = ntile(smooth_fits$SA.axis_rank, 10))

write.csv(smooth_fits, "/cbica/projects/network_replication/WNC/schaefer200x7_smoothfits_longDf.csv")
 
```

