---
title: "WNC Developmental Trajectories: PNC (Schaefer200x7)"
author: "Valerie Jill Sydnor, adapted by Audrey Luo"
output:
  html_document:
    code_folding: show
    highlight: haddock
    theme: lumen
    toc: yes
    toc_depth: 4
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '4'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
require(ggplot2)
library(cowplot)
library(cifti)
library(ggseg)
Sys.setenv(RGL_USE_NULL=TRUE)
library(ggsegExtra)
library(ggsegSchaefer)
library(ggcorrplot)
library(viridis)
library(scales)
library(stringr)
library(tidyr)


```
  
# load schaefer200 parcellated S-A axis
```{r}
# load SNR mask 
SNRmask_schaefer200 <- read.csv('/cbica/projects/network_replication/atlases/Masks/SNRmask_schaefer200x7_reordered.csv')

# load region list
schaefer200.parcel.labels <- read.csv("/cbica/projects/network_replication/atlases/parcellations/schaefer200x7_ggseg_reordered.csv", header = T) #schaefer parcel names in order of surface data
names(schaefer200.parcel.labels)[2] <- "label"
schaefer200.parcel.labels[which(SNRmask_schaefer200 == 0),] <- NA # apply SNR mask to parcel names
schaefer200.parcel.labels <- na.omit(schaefer200.parcel.labels)
 

# load parcellated SA axis
schaefer200_SAaxis_cifti <- read_cifti("/cbica/projects/network_replication/SAaxis/SensorimotorAssociation_Axis_parcellated/SensorimotorAssociation.Axis.Schaefer200.7Networks.pscalar.nii")  

schaefer200_SAaxis <- as.data.frame(cbind(rank(schaefer200_SAaxis_cifti$data), names(schaefer200_SAaxis_cifti$Parcel)))
colnames(schaefer200_SAaxis) <- c("SA.axis_rank","label")

# reorder SA axis (7 to 17)
index_schaefer200x7to17 <- read.csv("/cbica/projects/network_replication/software/schaefer7to17_reordering/index_schaefer200x7to17.csv", header=F)
 
index_schaefer200x7to17$V1 <- as.numeric(index_schaefer200x7to17$V1)
schaefer200_SAaxis <-schaefer200_SAaxis[index_schaefer200x7to17$V1,]
#as.matrix(cbind(schaefer200_SAaxis, schaefer200.parcel.labels))


# apply SNR mask
schaefer200_SAaxis[which(SNRmask_schaefer200 == 0),] <- NA
schaefer200_SAaxis <- na.omit(schaefer200_SAaxis) 

identical(schaefer200_SAaxis$label, schaefer200.parcel.labels$label)
```


```{r include=FALSE}
## GAM Results

gam.WNC.age.schaefer200 <- read.csv("/cbica/projects/network_replication/WNC/GAM/GAMresults.WNC.age.schaefer200x7.csv")

gam.WNC.age.schaefer200 <- gam.WNC.age.schaefer200 %>% select(-label)
gam.WNC.age.schaefer200$label <- schaefer200_SAaxis$label
 

gam.smooths.schaefer200 <- read.csv("/cbica/projects/network_replication/WNC/GAM/GAMsmoothfits.WNC.age.schaefer200x7.csv")
gam.smooths.schaefer200$orig_parcelname <- gam.smooths.schaefer200$label
 

gam.agepeaks.schaefer200 <- read.csv("/cbica/projects/network_replication/WNC/GAM/GAMpeaks.WNC.age.schaefer200x7.csv")
gam.agepeaks.schaefer200 <- gam.agepeaks.schaefer200 %>% select(-label)
gam.agepeaks.schaefer200$label <- schaefer200_SAaxis$label


```

 
# schaefer200 final Dfs
```{r include=FALSE}
# Combine into Final Dfs

df.list <- list(schaefer200_SAaxis,gam.WNC.age.schaefer200)
  
WNC.axis <- Reduce(function(x,y) merge(x,y, all=TRUE, sort=F), df.list) 
WNC.axis$SA.axis_rank <- as.numeric(WNC.axis$SA.axis_rank)
 
```

 
 
```{r include=FALSE}
  
a <- merge(schaefer200.parcel.labels, schaefer200_SAaxis, by="label", sort=F)
a$label <- gsub("7Networks_", "", a$label)
gam.smooths.schaefer200 <- left_join(gam.smooths.schaefer200, a, by = "label")
gam.smooths.schaefer200$SA.axis_rank <-as.numeric(gam.smooths.schaefer200$SA.axis_rank) 

gam.agepeaks.schaefer200 <- left_join(gam.agepeaks.schaefer200, schaefer200_SAaxis, by="label")
gam.agepeaks.schaefer200$SA.axis_rank <-as.numeric(gam.agepeaks.schaefer200$SA.axis_rank) 
```
 
 

#Load Spin Test Parcel Rotation Matrix
```{r}
source("/cbica/projects/network_replication/software/rotate.parcellation.R")
source("/cbica/projects/network_replication/software/perm.sphere.p.R")

schaefer200.coords <- read.csv("/cbica/projects/network_replication/software/rotate_parcellation/Schaefer2018_200Parcels_7Networks_order_FSLMNI152_1mm.Centroid_RAS_reordered.csv") #coordinates of schaefer200.coords parcel centroids on the freesurfer sphere

perm.id.full <- rotate.parcellation(coord.l = as.matrix(schaefer200.coords[1:100,4:6]), coord.r = as.matrix(schaefer200.coords[101:200,4:6]), nrot = 10000) #rotate the schaefer200.coords parcellation 10,000 times on the freesurfer sphere to generate spatial nulls for spin-based permutation significance testing 

 
## saveRDS(perm.id.full, "/cbica/projects/network_replication/software/rotate_parcellation/schaefer200x7.coords_sphericalrotations_N10k.rds")

perm.id.full <- readRDS("/cbica/projects/network_replication/software/rotate_parcellation/schaefer200x7.coords_sphericalrotations_N10k.rds")
```

#create df.dev.spin formatted for spatial permutation testing 
 
```{r}
# need to reintroduced the parcels removed by SNRmask as NA's

schaefer200.parcel.labels_noMask <- read.csv("/cbica/projects/network_replication/atlases/parcellations/schaefer200x7_ggseg_reordered.csv", header = T) 
names(schaefer200.parcel.labels_noMask) <- c("orig_parcel", "label")

WNC.axis$label <- gsub("7Networks_", "", WNC.axis$label)
schaefer200.parcel.labels_noMask$label <- gsub("7Networks_", "", schaefer200.parcel.labels_noMask$label)
setdiff(WNC.axis$label, schaefer200.parcel.labels_noMask$label)

schaefer200.parcel.labels_noMask$label[which(!schaefer200.parcel.labels_noMask$label %in% WNC.axis$label)] # names of removed parcels


# need to go through parcel.labels and see which are in WNC.axis label
# then for the ones that aren't in WNC.axis$label, insert parcel.labels[row_of_missing_label] into WNC.axis, and have the rest of the row be NA
# r = the row index -- indices of SNR removed parcels
# newrow = content of inserted row -- c('name of parcel', NA, NA, NA etc)
# existingDF = WNC.axis
insertRow <- function(r, existingDF, orig.parcel.labels) {
  newrow <- c(paste0(orig.parcel.labels[r]), rep(NA, 10)) # format data for spin tests by assigning NA to low SNR parcels, treating them like the medial wall
  existingDF[seq(r+1,nrow(existingDF)+1),] <- existingDF[seq(r,nrow(existingDF)),]
  existingDF[r,] <- newrow
  existingDF
}

 
r <- which(!schaefer200.parcel.labels_noMask$label %in% WNC.axis$label) # indices of removed parcels
existingDF <- WNC.axis  
 
for(i in c(1:length(r))){
   existingDF <- insertRow(r[i], existingDF, schaefer200.parcel.labels_noMask$label)
}

   
df.dev.spin <- rbind(existingDF[1:100,], existingDF[101:200,]) #format df as left hemisphere -> right hemisphere for spin tests
df.dev.spin <- cbind(df.dev.spin, SNRmask_schaefer200) 
 
identical(df.dev.spin$label, schaefer200.parcel.labels_noMask$label)
 
```


# WNC Developmental Effects

## Number of significant parcels (FDR corrected)

```{r echo=FALSE}
WNC.axis$Anova.age.pvalue.fdr <- p.adjust(WNC.axis$Anova.age.pvalue, method=c("fdr"))
cat(sprintf("There are %s/%s significant parcels", sum(WNC.axis$Anova.age.pvalue.fdr < 0.05), nrow(WNC.axis)))

WNC.axis$significant.fdr <- WNC.axis$Anova.age.pvalue.fdr < 0.05
WNC.axis$significant.fdr[WNC.axis$significant.fdr == TRUE] <- 1
WNC.axis$significant.fdr[WNC.axis$significant.fdr == FALSE] <- 0
 
```
# i can't get  this to work
```{r, echo=F, include=F}
plot(schaefer200, show.legend = FALSE)
ggplot() + geom_brain(data = WNC.axis, atlas = schaefer200, aes(fill=as.factor(significant.fdr)), show.legend = NA) +scale_fill_discrete(name = "significant.fdr", labels = c("Not Sig","Sig")) 

 ggseg(.data = WNC.axis, atlas = "schaefer200", mapping=aes(fill=significant.fdr), position = c("stacked")) + theme_void() + scale_fill_discrete(name = "significant.fdr", labels = c("Not Sig","Sig")) # Error: Must request at least one colour from a hue palette.


 ggseg(WNC.axis, atlas = "schaefer200", mapping=aes(fill=significant.fdr), position = "stacked") + scale_fill_gradientn(colours= c("#053061", "#67001F")) + theme_void()
     
```

## Age Effect by S-A Axis position

```{r}
cor.test(WNC.axis$GAM.age.AdjRsq, as.numeric(WNC.axis$SA.axis_rank), method=c("spearman"), exact=F)

perm.sphere.p(as.numeric(df.dev.spin$GAM.age.AdjRsq), as.numeric(df.dev.spin$SA.axis_rank), perm.id.full, corr.type='spearman')
```

```{r, echo=F}
library(ggpubr)
WNC.axis <- WNC.axis %>% mutate(SA.axis_rank_signif = ifelse(significant.fdr == 1, SA.axis_rank, NA))

WNC.axis
## SA axis average rank vs. age effect
# included all datapoints for this figure
cor.test(WNC.axis$GAM.age.AdjRsq, as.numeric(WNC.axis$SA.axis_rank), method=c("spearman"), exact=F)

r_text <- expression(paste(italic("r"), "= -0.34, ", italic(p[spin]), "< 0.05"))


(schaefer200_SA.AgeEffect <- ggplot(WNC.axis, aes(x=SA.axis_rank, y=GAM.age.AdjRsq, fill = SA.axis_rank_signif)) + geom_point(color = "white", shape = 21, size=2) +
scale_fill_gradient2(low="#6f1282",high = "goldenrod1",, mid = "#EBDAFF", midpoint = median(WNC.axis$SA.axis_rank), na.value="gray") +
labs(fill = "SA Axis Rank", x="\nSensorimotor-Association Axis Rank\n", y=expression(paste("Age Effect (Delta Adj", " R"^2, ")"))) +
geom_smooth(data = WNC.axis, method='lm', se=TRUE, fill=alpha(c("gray70"),.9), col="black") +
theme(
axis.title.x=element_text(size=12, color = "black"),
axis.title.y=element_text(size=12, color = "black"),
axis.line = element_line(color = "black"),
axis.text=element_text(size=12, color = "black"),
panel.background=element_blank(),
legend.position = "right") +
annotate(geom="text", x=140, y=0.055, label=r_text, color="black"))
# ggsave(schaefer200_SA.AgeEffect, file="/cbica/projects/network_replication/adapted_Rscripts/Figures/Schaefer200/WNC/schaefer200x7_SA.AgeEffect.pdf", width = 5, height=4, dpi=300)

```

# exclude outlier
```{r}
 
rm <- which(WNC.axis$GAM.age.AdjRsq==max(WNC.axis$GAM.age.AdjRsq))

WNC.axis_rmOutlier <- WNC.axis[-rm,]
rm <- which(WNC.axis_rmOutlier$GAM.age.AdjRsq == max(WNC.axis_rmOutlier$GAM.age.AdjRsq))
WNC.axis_rmOutlier <- WNC.axis_rmOutlier[-rm,]
## SA axis average rank vs. age effect
# included all datapoints for this figure
cor.test(WNC.axis_rmOutlier$GAM.age.AdjRsq, as.numeric(WNC.axis_rmOutlier$SA.axis_rank), method=c("spearman"), exact=F)

(schaefer200_SA.AgeEffect <- ggplot(WNC.axis_rmOutlier, aes(x=SA.axis_rank, y=GAM.age.AdjRsq, fill = SA.axis_rank_signif)) + geom_point(color = "white", shape = 21, size=2) +
scale_fill_gradient2(low="#6f1282",high = "goldenrod1",, mid = "#EBDAFF", midpoint = median(WNC.axis_rmOutlier$SA.axis_rank), na.value="gray") +
labs(fill = "SA Axis Rank", x="\nSensorimotor-Association Axis Rank\n", y=expression(paste("Age Effect (Delta Adj", " R"^2, ")"))) +
geom_smooth(data = WNC.axis_rmOutlier, method='lm', se=TRUE, fill=alpha(c("gray70"),.9), col="black") +
theme(
axis.title.x=element_text(size=12, color = "black"),
axis.title.y=element_text(size=12, color = "black"),
axis.line = element_line(color = "black"),
axis.text=element_text(size=12, color = "black"),
panel.background=element_blank(),
legend.position = "right") +
annotate(geom="text", x=140, y=0.055, label="R = -0.31, p < 0.00001  ", color="black"))
#  

```




# excluded the non-significant FDR corrected data points to calculate the correlation
```{r}
signif_WNC.axis <- WNC.axis[which(WNC.axis$significant.fdr ==1),] 
 
cor.test(signif_WNC.axis$GAM.age.AdjRsq, as.numeric(signif_WNC.axis$SA.axis_rank), method=c("spearman"), exact=F)

WNC.axis <- WNC.axis %>% mutate(SA.axis_rank_signif = ifelse(significant.fdr == 1, SA.axis_rank, NA))

## SA axis average rank vs. age effect
(schaefer200_SA.AgeEffect <- ggplot(WNC.axis, aes(x=SA.axis_rank, y=GAM.age.AdjRsq, fill = SA.axis_rank_signif)) + geom_point(color = "white", shape = 21, size=2) +
scale_fill_gradient2(low="#6f1282",high = "goldenrod1",, mid = "#EBDAFF", midpoint = median(WNC.axis$SA.axis_rank), na.value="gray") +
labs(fill = "SA Axis Rank", x="\nSensorimotor-Association Axis Rank\n", y=expression(paste("Age Effect (Delta Adj", " R"^2, ")"))) +
geom_smooth(data = signif_WNC.axis, method='lm', se=TRUE, fill=alpha(c("gray70"),.9), col="black") +
theme(
axis.title.x=element_text(size=12, color = "black"),
axis.title.y=element_text(size=12, color = "black"),
axis.line = element_line(color = "black"),
axis.text=element_text(size=12, color = "black"),
panel.background=element_blank(),
legend.position = "right") +
annotate(geom="text", x=120, y=0.05, label="R = -0.41, p = 0.0001  ", color="black"))
  
 
```



## WNC Developmental Trajectories

```{r}
class(gam.smooths.schaefer200$SA.axis_rank)
# seems like transmodal areas have greater WNC and seem to increase with age, while unimodal areas have smaller WNC and increase or stays the same with age
(schaefer200_predWNC <- ggplot(gam.smooths.schaefer200,aes(age,fit,group=index)) + 
  geom_line(data = gam.smooths.schaefer200, size=.8, alpha = .6, aes(color=SA.axis_rank)) + scale_color_gradient2(low="#6f1282",high = "goldenrod1", mid = "#EBDAFF", midpoint = median(WNC.axis$SA.axis_rank)) + 
  labs(color = "SA Axis Rank",
       x="Age", 
       y="Predicted Within-Network Coupling") +
  theme(
axis.title.x=element_text(size=12, color = "black"),
axis.title.y=element_text(size=12, color = "black"),
axis.line = element_line(color = "black"),
axis.text=element_text(size=12, color = "black"),
panel.background=element_blank(),
legend.position = "bottom") + coord_cartesian(expand = FALSE, xlim = c(8, 23)))
 
#ggsave(schaefer200_predWNC, file="/cbica/projects/network_replication/adapted_Rscripts/Figures/Schaefer200/WNC/schaefer200x7_predWNC.pdf", width = 4, height=4, dpi=300)

```

## Age of Maximal WNC 

```{r echo=FALSE}

names(gam.agepeaks.schaefer200)[2] <- "region"

(schaefer200_agepeak <- ggplot() + geom_brain(data=gam.agepeaks.schaefer200, 
                      atlas=schaefer7_200, 
                      mapping=aes(fill=age.peak), 
                      show.legend=TRUE, 
                      position = position_brain(hemi ~ side)) + 
  scale_fill_gradientn(colors = viridis_pal(option="B")(10)) + theme_void())
#ggsave(schaefer200_agepeak, file="/cbica/projects/network_replication/adapted_Rscripts/Figures/Schaefer200/WNC/schaefer200x7_agepeak.pdf", width = 6, height=4, dpi=300)

  
plot(schaefer7_200) +
  theme(legend.position = "bottom",
        legend.text = element_text(size = 9)) +
  guides(fill = guide_legend(ncol = 7))

 
```
