---
title: "NKI fit GAMs"
author: "Audrey Luo"
date: "2022-08-03"
output: html_document
---

```{r setup, include=FALSE}

library(dplyr)
source("/cbica/projects/network_replication/adapted_Rscripts/GAM_functions.R")
source("/cbica/projects/network_replication/adapted_Rscripts/fitGAMs.R")  
dataset = "NKI"
knitr::opts_chunk$set(include = FALSE, eval = TRUE, echo = FALSE, warning = FALSE, message = FALSE) 
```

 
# make connectivityMetric-demographics .csv's
```{r connMetric_demographics, include=FALSE}

demographics <- read.csv(sprintf("/cbica/projects/network_replication/input/%1$s/sample_selection/%1$s_demographics_finalsample_20221219.csv", dataset))

range(demographics$age)
# GBC
## creates GBC.glasser.NKI, GBC.gordon.NKI, GBC.schaefer200.NKI, GBC.schaefer400.NKI csv's
atlases <- c("glasser", "gordon", "schaefer200", "schaefer400")
metric = "GBC"
for(i in c(1:length(atlases))){
  df_name <- paste0(metric, ".", atlases[i], ".", dataset)
  assign(df_name, make_connMetricsDemog(atlases[i], metric, demographics, "subject", dataset))
}


# BNC
## BNC.gordon.NKI, BNC.schaefer200x7.NKI, BNC.schaefer200x17.NKI, BNC.schaefer400x7.NKI, BNC.schaefer400x17.NKI
atlases <- c("gordon", "schaefer200x7", "schaefer200x17", "schaefer400x7", "schaefer400x17")
metric = "BNC"
for(i in c(1:length(atlases))){
  df_name <- paste0(metric, ".", atlases[i], ".", dataset)
  assign(df_name, make_connMetricsDemog(atlases[i], metric, demographics, "subject", dataset))
}

# WNC
## WNC.gordon.NKI, WNC.schaefer200x7.NKI, WNC.schaefer200x17.NKI, WNC.schaefer400x7.NKI, WNC.schaefer400x17.NKI
atlases <- c("gordon", "schaefer200x7", "schaefer200x17", "schaefer400x7", "schaefer400x17")
metric = "WNC"

for(i in c(1:length(atlases))){
  df_name <- paste0(metric, ".", atlases[i], ".", dataset)
  assign(df_name, make_connMetricsDemog(atlases[i], metric, demographics, "subject", dataset))
} 

 
# edge
## edge.glasser.NKI, edge.gordon.NKI, edge.schaefer200x7.NKI, edge.schaefer200x17.NKI, edge.schaefer400x7.NKI, edge.schaefer400x17.NKI
atlases <- c("glasser","gordon", "schaefer200x7", "schaefer200x17", "schaefer400x7", "schaefer400x17")
#make_connMetricsDemog("gordon", demographics, "subject", dataset)
for(i in c(1:length(atlases))){
  df_name <- paste0("edge.", atlases[i], ".", dataset)
  assign(df_name, make_EdgeDemog(atlases[i],  demographics, "subject", dataset))
} 
 
 
```


 

# load connectivityMetric-demographics .csv's
```{r load_connectivity, include=TRUE} 
GBC.glasser.NKI <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/GBC/GBCglasser_demographics_finalsample.csv", dataset))
GBC.gordon.NKI <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/GBC/GBCgordon_demographics_finalsample.csv", dataset)) 
GBC.schaefer200.NKI <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/GBC/GBCschaefer200_demographics_finalsample.csv", dataset)) 
names(GBC.schaefer200.NKI) <- gsub('X17Networks', "Networks", names(GBC.schaefer200.NKI))

GBC.schaefer400.NKI <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/GBC/GBCschaefer400_demographics_finalsample.csv", dataset)) 
names(GBC.schaefer400.NKI) <- gsub('X17Networks', "Networks", names(GBC.schaefer400.NKI)) 
 
 
# BNC
BNC.gordon.NKI <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/BNC/BNCgordon_demographics_finalsample.csv", dataset))   
BNC.schaefer200x7.NKI <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/BNC/BNCschaefer200x7_demographics_finalsample.csv", dataset)) 
names(BNC.schaefer200x7.NKI) <- gsub("X7", "", names(BNC.schaefer200x7.NKI))

BNC.schaefer200x17.NKI <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/BNC/BNCschaefer200x17_demographics_finalsample.csv", dataset))    
names(BNC.schaefer200x17.NKI) <- gsub("X17", "", names(BNC.schaefer200x17.NKI))

BNC.schaefer400x7.NKI <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/BNC/BNCschaefer400x7_demographics_finalsample.csv", dataset))
names(BNC.schaefer400x7.NKI) <- gsub("X7", "", names(BNC.schaefer400x7.NKI))

BNC.schaefer400x17.NKI <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/BNC/BNCschaefer400x17_demographics_finalsample.csv", dataset))   
names(BNC.schaefer400x17.NKI) <- gsub("X17", "", names(BNC.schaefer400x17.NKI))

# WNC
WNC.gordon.NKI <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/WNC/WNCgordon_demographics_finalsample.csv", dataset))    
WNC.schaefer200x7.NKI <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/WNC/WNCschaefer200x7_demographics_finalsample.csv", dataset))
names(WNC.schaefer200x7.NKI) <- gsub("X7", "", names(WNC.schaefer200x7.NKI))

WNC.schaefer200x17.NKI <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/WNC/WNCschaefer200x17_demographics_finalsample.csv", dataset)) 
names(WNC.schaefer200x17.NKI) <- gsub("X17", "", names(WNC.schaefer200x17.NKI))

WNC.schaefer400x7.NKI <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/WNC/WNCschaefer400x7_demographics_finalsample.csv", dataset)) 
names(WNC.schaefer400x7.NKI) <- gsub("X7", "", names(WNC.schaefer400x7.NKI))

WNC.schaefer400x17.NKI <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/WNC/WNCschaefer400x17_demographics_finalsample.csv", dataset))  
names(WNC.schaefer400x17.NKI) <- gsub("X17", "", names(WNC.schaefer400x17.NKI))

edge.gordon.NKI <- readRDS("/cbica/projects/network_replication/output/NKI/edge/gordon_demographics_finalsample.RData")
edge.glasser.NKI <- readRDS("/cbica/projects/network_replication/output/NKI/edge/glasser_demographics_finalsample.RData")
edge.schaefer200x7.NKI <- readRDS("/cbica/projects/network_replication/output/NKI/edge/schaefer200x7_demographics_finalsample.RData")
edge.schaefer200x17.NKI <- readRDS("/cbica/projects/network_replication/output/NKI/edge/schaefer200x17_demographics_finalsample.RData")
edge.schaefer400x7.NKI <- readRDS("/cbica/projects/network_replication/output/NKI/edge/schaefer400x7_demographics_finalsample.RData")
edge.schaefer400x17.NKI <- readRDS("/cbica/projects/network_replication/output/NKI/edge/schaefer400x17_demographics_finalsample.RData")
 
# make sex a factor
GBC.glasser.NKI$sex <- as.factor(GBC.glasser.NKI$gender)
GBC.gordon.NKI$sex <- as.factor(GBC.gordon.NKI$gender)
GBC.schaefer200.NKI$sex <- as.factor(GBC.schaefer200.NKI$gender)
GBC.schaefer400.NKI$sex <- as.factor(GBC.schaefer400.NKI$gender)

 
BNC.gordon.NKI$sex <- as.factor(BNC.gordon.NKI$gender)
BNC.schaefer200x7.NKI$sex <- as.factor(BNC.schaefer200x7.NKI$gender)
BNC.schaefer200x17.NKI$sex <- as.factor(BNC.schaefer200x17.NKI$gender)
BNC.schaefer400x7.NKI$sex <- as.factor(BNC.schaefer400x7.NKI$gender)
BNC.schaefer400x17.NKI$sex <- as.factor(BNC.schaefer400x17.NKI$gender)

 
WNC.gordon.NKI$sex <- as.factor(WNC.gordon.NKI$gender)   
WNC.schaefer200x17.NKI$sex <- as.factor(WNC.schaefer200x17.NKI$gender) 
WNC.schaefer400x17.NKI$sex <- as.factor(WNC.schaefer400x17.NKI$gender) 
WNC.schaefer200x7.NKI$sex <- as.factor(WNC.schaefer200x7.NKI$gender) 
WNC.schaefer400x7.NKI$sex <- as.factor(WNC.schaefer400x7.NKI$gender) 


edge.gordon.NKI$sex <- as.factor(edge.gordon.NKI$gender)
edge.glasser.NKI$sex <- as.factor(edge.glasser.NKI$gender)
edge.schaefer200x7.NKI$sex <- as.factor(edge.schaefer200x7.NKI$gender)
edge.schaefer200x17.NKI$sex <- as.factor(edge.schaefer200x17.NKI$gender)
edge.schaefer400x7.NKI$sex <- as.factor(edge.schaefer400x7.NKI$gender)
edge.schaefer400x17.NKI$sex <- as.factor(edge.schaefer400x17.NKI$gender)
 
```

 

 
# load parcel labels and edges 
```{r}
# load parcel labels 

glasser.parcel.labels <- read.csv("/cbica/projects/network_replication/atlases/parcellations/glasser360_regionlist_final.csv")

gordon.parcel.labels <- read.csv("/cbica/projects/network_replication/atlases/parcellations/gordon_regionlist_final.csv")

schaefer200x7.parcel.labels <- read.csv("/cbica/projects/network_replication/atlases/parcellations/schaefer200x7_regionlist_final.csv")

schaefer200x17.parcel.labels <- read.csv("/cbica/projects/network_replication/atlases/parcellations/schaefer200x17_regionlist_final.csv")
schaefer200.parcel.labels <- schaefer200x17.parcel.labels #gbc

schaefer400x7.parcel.labels <- read.csv("/cbica/projects/network_replication/atlases/parcellations/schaefer400x7_regionlist_final.csv")

schaefer400x17.parcel.labels <- read.csv("/cbica/projects/network_replication/atlases/parcellations/schaefer400x17_regionlist_final.csv")
schaefer400.parcel.labels <- schaefer400x17.parcel.labels #gbc

# edges
gordon_edge <- read.csv("/cbica/projects/network_replication/atlases/edge/gordon_edge.csv")
gordon_edge <- gordon_edge[,2]

glasser_edge <- read.csv("/cbica/projects/network_replication/atlases/edge/glasser_edge.csv")
glasser_edge <- glasser_edge[,2]
schaefer200x7_edge <- read.csv("/cbica/projects/network_replication/atlases/edge/schaefer200x7_edge.csv")
schaefer200x7_edge <- schaefer200x7_edge[,2]
schaefer200x17_edge <- read.csv("/cbica/projects/network_replication/atlases/edge/schaefer200x17_edge.csv")
schaefer200x17_edge <- schaefer200x17_edge[,2]

schaefer400x7_edge <- read.csv("/cbica/projects/network_replication/atlases/edge/schaefer400x7_edge.csv")
schaefer400x7_edge <- schaefer400x7_edge[,2]
schaefer400x17_edge <- read.csv("/cbica/projects/network_replication/atlases/edge/schaefer400x17_edge.csv")
schaefer400x17_edge <- schaefer400x17_edge[,2]
```  




# Check AIC for k=3-6
```{r}
library(stats)

 
dataset_name="NKI"
covariates ="sex + meanFD_avgSes"
smooth_var="age"


check_aic <- function(parcel.labels, atlas_name, network_parcellation, dataset_name, covariates, smooth_var, k_number){
    parcel.labels <- parcel.labels$label
    list_plots <- list()
    list_AIC <- c()
    list_region <- c()
    for(row in c(1:length(parcel.labels))){ #for each region
      region <- parcel.labels[row] 
      dataname <- sprintf("%s.%s%s.%s", metric, atlas_name, network_parcellation, dataset_name) 
      gam.data <- get(dataname) # Return the Value of a Named Object
      parcel <- region
      region <- str_replace(region, "-", ".")
      modelformula <- as.formula(sprintf("%s ~ s(%s, k=%s, fx=T) + %s", region, smooth_var, k_number, covariates)) # 3 knots, fx = should term be unpenalized (so here, it is unpenalized)
      gam.model <- gam(modelformula, data=gam.data)
      gam.results <- summary(gam.model) 
      
      #list_plots <- append(draw(gam.model, residuals = TRUE), list_plots)
      list_AIC <- append(AIC(gam.model), list_AIC)
      list_region <- append(region, list_region)
      k_dataframe <- data.frame(bind_cols(list_AIC, list_region))
      names(k_dataframe) <- c("AIC", "region")
      print(row)
    }
      return(k_dataframe)
}
 
metric="GBC"
k_3 <- check_aic(schaefer200.parcel.labels, "schaefer200", "", "PNC", "sex + meanFD_avgSes", "age", 3)
mean(k_3$AIC) #-4650.1646
median(k_3$AIC) #-4650.231

k_4 <- check_aic(schaefer200.parcel.labels, "schaefer200", "", "PNC", "sex + meanFD_avgSes", "age", 4)
mean(k_4$AIC) #-4649.335
median(k_4$AIC) #-4650.828

k_5 <- check_aic(schaefer200.parcel.labels, "schaefer200", "", "PNC", "sex + meanFD_avgSes", "age", 5)
mean(k_5$AIC) #-4648.405
median(k_5$AIC) #-4649.481

k_6 <- check_aic(schaefer200.parcel.labels, "schaefer200", "", "PNC", "sex + meanFD_avgSes", "age", 6)
mean(k_6$AIC) #-4647.478
median(k_6$AIC) #-4647.478
 
 
# BNC
metric="BNC"
k_3.BNC <- check_aic(schaefer200x7.parcel.labels, "schaefer200", "x7", "PNC", "sex + meanFD_avgSes", "age", 3)
mean(k_3.BNC$AIC) #-4351.929
median(k_3.BNC$AIC) #-4464.881

k_4.BNC <- check_aic(schaefer200x7.parcel.labels, "schaefer200", "x7", "PNC", "sex + meanFD_avgSes", "age", 4)
mean(k_4.BNC$AIC) # -4351.238
median(k_4.BNC$AIC) # -4463.059

k_5.BNC <- check_aic(schaefer200x7.parcel.labels, "schaefer200", "x7", "PNC", "sex + meanFD_avgSes", "age", 5)
mean(k_5.BNC$AIC) # -4350.256
median(k_5.BNC$AIC) #-4461.29

k_6.BNC <- check_aic(schaefer200x7.parcel.labels, "schaefer200", "x7", "PNC", "sex + meanFD_avgSes", "age", 6)
mean(k_6.BNC$AIC) # -4349.364
median(k_6.BNC$AIC) #-4461.45


# WNC
metric="WNC"
k_3.WNC <- check_aic(schaefer200x7.parcel.labels, "schaefer200", "x7", "PNC", "sex + meanFD_avgSes", "age", 3)
mean(k_3.WNC$AIC) # -2493.504
median(k_3.WNC$AIC) #-2527.435

k_4.WNC <- check_aic(schaefer200x7.parcel.labels, "schaefer200", "x7", "PNC", "sex + meanFD_avgSes", "age", 4)
mean(k_4.WNC$AIC) # -2492.42
median(k_4.WNC$AIC) #-2526.052

k_5.WNC <- check_aic(schaefer200x7.parcel.labels, "schaefer200", "x7", "PNC", "sex + meanFD_avgSes", "age", 5)
mean(k_5.WNC$AIC) # -2491.383
median(k_5.WNC$AIC) #-2524.531

k_6.WNC <- check_aic(schaefer200x7.parcel.labels, "schaefer200", "x7", "PNC", "sex + meanFD_avgSes", "age", 6)
mean(k_6.WNC$AIC) # -2490.116
median(k_6.WNC$AIC) #-2522.614
 
```


# Fit GAMs
```{r}
 
# GBC GAMs
gam.GBC.age.glasser <- fitGAMs(glasser.parcel.labels, "GBC", "glasser", "",dataset)
gam.GBC.age.gordon <- fitGAMs(gordon.parcel.labels, "GBC", "gordon", "", dataset)
gam.GBC.age.schaefer200 <- fitGAMs(schaefer200x17.parcel.labels, "GBC", "schaefer200", "", dataset)
gam.GBC.age.schaefer400 <- fitGAMs(schaefer400x17.parcel.labels, "GBC", "schaefer400", "", dataset)
 

# BNC GAMs
gam.BNC.age.gordon <- fitGAMs(gordon.parcel.labels, "BNC", "gordon", "", dataset)
gam.BNC.age.schaefer200x7 <- fitGAMs(schaefer200x7.parcel.labels, "BNC", "schaefer200", "x7", dataset)
gam.BNC.age.schaefer200x17 <- fitGAMs(schaefer200x17.parcel.labels, "BNC", "schaefer200", "x17",dataset)  
gam.BNC.age.schaefer400x7 <- fitGAMs(schaefer400x7.parcel.labels, "BNC", "schaefer400", "x7", dataset)   
gam.BNC.age.schaefer400x17 <- fitGAMs(schaefer400x17.parcel.labels, "BNC", "schaefer400", "x17",dataset)  
 


# WNC GAMs
gam.WNC.age.gordon <- fitGAMs(gordon.parcel.labels, "WNC", "gordon", "", dataset)
gam.WNC.age.schaefer200x7 <- fitGAMs(schaefer200x7.parcel.labels, "WNC", "schaefer200", "x7", dataset)   
gam.WNC.age.schaefer200x17 <- fitGAMs(schaefer200x17.parcel.labels, "WNC", "schaefer200", "x17",dataset)  
gam.WNC.age.schaefer400x7 <- fitGAMs(schaefer400x7.parcel.labels, "WNC", "schaefer400", "x7",dataset)  
gam.WNC.age.schaefer400x17 <- fitGAMs(schaefer400x17.parcel.labels, "WNC", "schaefer400", "x17",dataset)  


 
# Edge GAMs  
glasser_edge <- gsub("-", ".", glasser_edge)
names(edge.glasser.NKI) <- gsub("-", ".",names(edge.glasser.NKI))
schaefer200x7_edge <- gsub("7Networks", "Networks", schaefer200x7_edge)
names(edge.schaefer200x7.NKI) <- gsub("7Networks", "Networks", names(edge.schaefer200x7.NKI))
schaefer200x17_edge <- gsub("17Networks", "Networks", schaefer200x17_edge)
names(edge.schaefer200x17.NKI) <- gsub("17Networks", "Networks", names(edge.schaefer200x17.NKI))
schaefer400x7_edge <- gsub("7Networks", "Networks", schaefer400x7_edge)
names(edge.schaefer400x7.NKI) <- gsub("7Networks", "Networks", names(edge.schaefer400x7.NKI))
schaefer400x17_edge <- gsub("17Networks", "Networks", schaefer400x17_edge)
names(edge.schaefer400x17.NKI) <- gsub("17Networks", "Networks", names(edge.schaefer400x17.NKI))
 
gam.edge.age.glasser <- fitGAMs_edge(glasser_edge,"edge","glasser", dataset)  
gam.edge.age.gordon <- fitGAMs_edge(gordon_edge,"edge","gordon", dataset)
gam.edge.age.schaefer200x7 <- fitGAMs_edge(schaefer200x7_edge,"edge","schaefer200x7", dataset)
gam.edge.age.schaefer200x17 <- fitGAMs_edge(schaefer200x17_edge,"edge","schaefer200x17", dataset)
gam.edge.age.schaefer400x7 <- fitGAMs_edge(schaefer400x7_edge,"edge","schaefer400x7", dataset)
gam.edge.age.schaefer400x17 <- fitGAMs_edge(schaefer400x17_edge,"edge","schaefer400x17", dataset)
  
```




# Estimate GAM smooths based on model-predicted data and save out predicted y data** 
```{r}
 
# GBC GAMs 
gam.GBC.smooths.glasser <- estimate_GAMsmooths(glasser.parcel.labels, "GBC", "glasser", "",dataset)
gam.GBC.smooths.gordon <- estimate_GAMsmooths(gordon.parcel.labels, "GBC", "gordon", "", dataset)
gam.GBC.smooths.schaefer200 <- estimate_GAMsmooths(schaefer200x17.parcel.labels, "GBC", "schaefer200", "", dataset)
gam.GBC.smooths.schaefer400 <- estimate_GAMsmooths(schaefer400x17.parcel.labels, "GBC", "schaefer400", "", dataset)


# BNC GAMs
gam.BNC.smooths.gordon <- estimate_GAMsmooths(gordon.parcel.labels, "BNC", "gordon", "", dataset)
gam.BNC.smooths.schaefer200x7 <- estimate_GAMsmooths(schaefer200x7.parcel.labels, "BNC", "schaefer200", "x7", dataset)
gam.BNC.smooths.schaefer200x17 <- estimate_GAMsmooths(schaefer200x17.parcel.labels, "BNC", "schaefer200", "x17",dataset)
gam.BNC.smooths.schaefer400x7 <- estimate_GAMsmooths(schaefer400x7.parcel.labels, "BNC", "schaefer400", "x7",dataset)
gam.BNC.smooths.schaefer400x17 <- estimate_GAMsmooths(schaefer400x17.parcel.labels, "BNC", "schaefer400", "x17",dataset)

# WNC GAMs
gam.WNC.smooths.gordon <- estimate_GAMsmooths(gordon.parcel.labels, "WNC", "gordon", "", dataset)
gam.WNC.smooths.schaefer200x7 <- estimate_GAMsmooths(schaefer200x7.parcel.labels, "WNC", "schaefer200", "x7", dataset)
gam.WNC.smooths.schaefer200x17 <- estimate_GAMsmooths(schaefer200x17.parcel.labels, "WNC", "schaefer200", "x17",dataset)
gam.WNC.smooths.schaefer400x7 <- estimate_GAMsmooths(schaefer400x7.parcel.labels, "WNC", "schaefer400", "x7",dataset)
gam.WNC.smooths.schaefer400x17 <- estimate_GAMsmooths(schaefer400x17.parcel.labels, "WNC", "schaefer400", "x17",dataset)
```


# Calculate Region-wise Predicted Fitted GBC values  

```{r}

# GBC GAMs age fitted
gam.GBC.fitted.glasser <- dev_fitted(glasser.parcel.labels, "GBC", "glasser", dataset)
gam.GBC.fitted.gordon <- dev_fitted(gordon.parcel.labels, "GBC", "gordon", dataset)
gam.GBC.fitted.schaefer200 <- dev_fitted(schaefer200x17.parcel.labels, "GBC", "schaefer200", dataset)
gam.GBC.fitted.schaefer400 <- dev_fitted(schaefer400x17.parcel.labels, "GBC", "schaefer400", dataset)

 
# BNC GAMs age fitted
gam.BNC.fitted.gordon <- dev_fitted(gordon.parcel.labels, "BNC", "gordon", dataset)
gam.BNC.fitted.schaefer200x7 <- dev_fitted(schaefer200x7.parcel.labels, "BNC", "schaefer200x7", dataset)
gam.BNC.fitted.schaefer200x17 <- dev_fitted(schaefer200x17.parcel.labels, "BNC", "schaefer200x17", dataset)
gam.BNC.fitted.schaefer400x7 <- dev_fitted(schaefer400x7.parcel.labels, "BNC", "schaefer400x7", dataset)
gam.BNC.fitted.schaefer400x17 <- dev_fitted(schaefer400x17.parcel.labels, "BNC", "schaefer400x17", dataset)

# WNC GAMs age fitted
gam.WNC.fitted.gordon <- dev_fitted(gordon.parcel.labels, "WNC", "gordon", dataset)
gam.WNC.fitted.schaefer200x7 <- dev_fitted(schaefer200x7.parcel.labels, "WNC", "schaefer200x7", dataset)
gam.WNC.fitted.schaefer200x17 <- dev_fitted(schaefer200x17.parcel.labels, "WNC", "schaefer200x17",dataset)
gam.WNC.fitted.schaefer400x7 <- dev_fitted(schaefer400x7.parcel.labels, "WNC", "schaefer400x7", dataset)
gam.WNC.fitted.schaefer400x17 <- dev_fitted(schaefer400x17.parcel.labels, "WNC", "schaefer400x17", dataset)

```


 
# Calculate Region-wise Predicted Fitted GBC values Correlation with SA Axis for Schaefer200 only 

```{r}

fits.SAaxis.posteriorcor_schaefer200.GBC <- make_fits.SAaxis.posteriorcor("GBC", "schaefer200", dataset)

```


# Calculate Region-wise Developmental Derivatives
```{r}

# GBC GAMs age derivatives
gam.GBC.derivatives.glasser <- dev_derivatives(glasser.parcel.labels, "GBC", "glasser", dataset)
gam.GBC.derivatives.gordon <- dev_derivatives(gordon.parcel.labels, "GBC", "gordon", dataset)
gam.GBC.derivatives.schaefer200 <- dev_derivatives(schaefer200x17.parcel.labels, "GBC", "schaefer200", dataset)
gam.GBC.derivatives.schaefer400 <- dev_derivatives(schaefer400x17.parcel.labels, "GBC", "schaefer400", dataset)

 
# BNC GAMs age derivatives
gam.BNC.derivatives.gordon <- dev_derivatives(gordon.parcel.labels, "BNC", "gordon", dataset)
gam.BNC.derivatives.schaefer200x7 <- dev_derivatives(schaefer200x7.parcel.labels, "BNC", "schaefer200x7", dataset)
gam.BNC.derivatives.schaefer200x17 <- dev_derivatives(schaefer200x17.parcel.labels, "BNC", "schaefer200x17", dataset)
gam.BNC.derivatives.schaefer400x7 <- dev_derivatives(schaefer400x7.parcel.labels, "BNC", "schaefer400x7", dataset)
gam.BNC.derivatives.schaefer400x17 <- dev_derivatives(schaefer400x17.parcel.labels, "BNC", "schaefer400x17", dataset)

# WNC GAMs age derivatives
gam.WNC.derivatives.gordon <- dev_derivatives(gordon.parcel.labels, "WNC", "gordon", dataset)
gam.WNC.derivatives.schaefer200x7 <- dev_derivatives(schaefer200x7.parcel.labels, "WNC", "schaefer200x7", dataset)
gam.WNC.derivatives.schaefer200x17 <- dev_derivatives(schaefer200x17.parcel.labels, "WNC", "schaefer200x17",dataset)
gam.WNC.derivatives.schaefer400x7 <- dev_derivatives(schaefer400x7.parcel.labels, "WNC", "schaefer400x7", dataset)
gam.WNC.derivatives.schaefer400x17 <- dev_derivatives(schaefer400x17.parcel.labels, "WNC", "schaefer400x17", dataset)
  
```



# Calculate Region-wise Posterior Smooth Derivatives Correlation with SA Axis (computationally heavy - can compute on cluster)

```{r}
# GBC - Region-wise Posterior Smooth Derivatives Correlation with SA Axis
deriv.SAaxis.posteriorcor_glasser.GBC <- make_deriv.SAaxis.posteriorcor("GBC", "glasser", dataset)
deriv.SAaxis.posteriorcor_gordon.GBC <- make_deriv.SAaxis.posteriorcor("GBC", "gordon", dataset)
deriv.SAaxis.posteriorcor_schaefer200.GBC <- make_deriv.SAaxis.posteriorcor("GBC", "schaefer200", dataset)
deriv.SAaxis.posteriorcor_schaefer400.GBC <- make_deriv.SAaxis.posteriorcor("GBC", "schaefer400", dataset)

# BNC - Region-wise Posterior Smooth Derivatives Correlation with SA Axis
deriv.SAaxis.posteriorcor_gordon.BNC <- make_deriv.SAaxis.posteriorcor("BNC", "gordon", dataset)
deriv.SAaxis.posteriorcor_schaefer200x7.BNC <- make_deriv.SAaxis.posteriorcor("BNC", "schaefer200x7", dataset)
deriv.SAaxis.posteriorcor_schaefer400x7.BNC <- make_deriv.SAaxis.posteriorcor("BNC", "schaefer400x7", dataset)
deriv.SAaxis.posteriorcor_schaefer200x17.BNC <- make_deriv.SAaxis.posteriorcor("BNC", "schaefer200x17", dataset)
deriv.SAaxis.posteriorcor_schaefer400x17.BNC <- make_deriv.SAaxis.posteriorcor("BNC", "schaefer400x17", dataset)


# WNC - Region-wise Posterior Smooth Derivatives Correlation with SA Axis
deriv.SAaxis.posteriorcor_gordon.WNC <- make_deriv.SAaxis.posteriorcor("WNC", "gordon", dataset)
deriv.SAaxis.posteriorcor_schaefer200x7.WNC <- make_deriv.SAaxis.posteriorcor("WNC", "schaefer200x7", dataset)
deriv.SAaxis.posteriorcor_schaefer400x7.WNC <- make_deriv.SAaxis.posteriorcor("WNC", "schaefer400x7", dataset)
deriv.SAaxis.posteriorcor_schaefer200x17.WNC <- make_deriv.SAaxis.posteriorcor("WNC", "schaefer200x17", dataset)
deriv.SAaxis.posteriorcor_schaefer400x17.WNC <- make_deriv.SAaxis.posteriorcor("WNC", "schaefer400x17", dataset)
 
```

