---
title: "PNC Sample Selection"
author: "Audrey Luo"
output: html_document
---

# Sample Selection process
1) original sample: N=1559, 4546 scans total, ages 8-23
2) exclude participants with medical conditions affecting brain function and gross neurological abnormalities: N=1413, 4136 scans 
3) include passing T1 QC: N=1374, 4041 scans
4) include meanFD < 0.3: N=1262, 3365 scans
5) include scans with at least 7 minutes of scan time: N= 1207,  3310 scans (final sample), 646 females.

range before: 3.60 to 33.25 min
median before: 28.25 min
mode before: 28.25 min

range after: 8.35 to 33.25 min
median after: 28.25 min

Age: mean = 15.4, SD = 3.5
 
Race
- white = 551 - 45.7%
- black = 513 - 42.5%
- other (native american + hawaiian pi) = 4 + 1 - 0.41%
- asian = 11 - 0.9%
- missing = 0
- mixed = 127 - 10.5%
 
# Sample Selection for sensitivity analysis (rest only)
5) include scans with at least 6 minutes of rest-only scan time (lowered threshold due to fewer total scans available after selecting for rest-only): N= 998, 1060 scans, 549 females 

Notes:
- mean FD is averaged across the scans in a given session
 
 
```{r setup, include=FALSE}
library(dplyr)
library(tidyverse)
library(magrittr)
library(reshape)
library(reshape2)
library(MASS)
library(stargazer)
library(ggplot2)
library(ggpubr)
library(reticulate) 
# reticulate::py_install("pandas") # install pandas for python code
# reticulate::py_install("glob2")  # install glob2 for python code
  
```


## Concatenate xcp qc files
```{python}
import pandas as pd
import glob2 as glob
import sys
import os
  
path = "/cbica/projects/network_replication/input/PNC/pnc_xcp/qc_files"  
all_files = glob.glob(os.path.join(path, "*.csv")) # load all qc csv filenames 

df_from_each_file = (pd.read_csv(f, header=0) for f in all_files) # read csv's
concatenated_df = pd.concat(df_from_each_file, ignore_index=True) # concatenate csv's

path=r'/cbica/projects/network_replication/input/PNC/pnc_xcp/qc_files/'
concatenated_df.to_csv(os.path.join(path,r'PNC_xcp_qc_concat_20230628.csv'),index=False) # save out concatenated qc files

```




## 1) original sample: N=1559, 4546 scans, ages 8-23
```{r qc_setup}
# load concatenated qc files
collated_PNC.xcp <- read.csv("/cbica/projects/network_replication/input/PNC/pnc_xcp/qc_files/PNC_xcp_qc_concat_20230628.csv")
collated_PNC.xcp$sub <- paste0("sub-", collated_PNC.xcp$sub)
length(unique(collated_PNC.xcp$sub)) # 1559 participants before head motion QC  
nrow(collated_PNC.xcp) #4546 scans

# make list of participant ID's to merge with demographics in this chunk  
scanned_participants <- data.frame(unique(collated_PNC.xcp$sub))
names(scanned_participants) <- "sub"

# load T1 QA - T1 ratings used in previous publications 
T1_QA <- read.csv("/cbica/projects/network_replication/input/PNC/sample_selection/n1601_t1QaData_20170306.csv")
bblid_scanid <- read.csv("/cbica/projects/network_replication/input/PNC/sample_selection/bblid_scanid_sub.csv")
T1_QA_PNC <- merge(T1_QA, bblid_scanid, by ="scanid")
T1_QA_PNC <- dplyr::select(T1_QA_PNC, -bblid.y)
T1_QA_PNC <- T1_QA_PNC %>% relocate(rbcid) 
T1_QA_PNC <- T1_QA_PNC %>% dplyr::rename(sub=rbcid)
T1_QA_PNC$sub <- paste0("sub-", T1_QA_PNC$sub)
 
# load demographics (updated file from informatics 6/7/2023)
demographics <- read.csv("/cbica/projects/network_replication/input/PNC/sample_selection/n1601_demographics_go1_20161212.csv")
bblid_scanid <- read.csv("/cbica/projects/network_replication/input/PNC/sample_selection/bblid_scanid_sub.csv")
demographics <- merge(demographics, bblid_scanid, by ="scanid")
demographics <- demographics %>% relocate(bblid, rbcid)
demographics <- dplyr::rename(demographics, sub = rbcid) %>% mutate(age = ageAtScan1/12)
demographics$sub <- paste0("sub-", demographics$sub)

# include only kids who got scanned 
demographics <- merge(scanned_participants, demographics, by = "sub")
nrow(demographics) #1559 total 
range(demographics$age, na.rm=TRUE) # age 8-23
 
```
 
  
## 2) exclude participants with medical conditions affecting brain function and gross neurological abnormalities (healthExcludev2)
```{r medical_exclusion}
PNC_healthExclude <- read.csv("/cbica/projects/network_replication/input/PNC/sample_selection/n1601_health_20170421.csv")
medical_exclusion <- PNC_healthExclude$bblid[c(which(PNC_healthExclude$healthExcludev2==1))] #fyi, bblid in PNC_healthExclude corresponds to rbcid in demographics 

demographics_medExclusion <- demographics[-c(which(demographics$rbcid %in% medical_exclusion)),] 
 
collated_PNC.xcp_medExclusion <- collated_PNC.xcp[-c(which(gsub("sub-", "", collated_PNC.xcp$sub) %in% medical_exclusion)),]

length(unique(collated_PNC.xcp_medExclusion$sub)) # N=1413
nrow(collated_PNC.xcp_medExclusion) # 4136 scans 
```


## 3) include passing T1 QC  
## 4) include meanFD < 0.3
```{r meanFD, cache=TRUE}

# T1 exclusion

collated_PNC.xcp_T1Exclusion <- merge(collated_PNC.xcp_medExclusion, dplyr::select(T1_QA_PNC, sub, t1Exclude), by = "sub")
collated_PNC.xcp_T1Exclusion <- collated_PNC.xcp_T1Exclusion[-c(which(collated_PNC.xcp_T1Exclusion$t1Exclude==1)),]

length(unique(collated_PNC.xcp_T1Exclusion$sub)) # N=1374 after excluding participants with failed T1
nrow(collated_PNC.xcp_T1Exclusion) # 4041 scans


collated_PNC.xcp_headMotion <- collated_PNC.xcp_T1Exclusion[c(which(collated_PNC.xcp_T1Exclusion$meanFD < 0.3)),]
length(unique(collated_PNC.xcp_headMotion$sub)) # N=1262 after excluding meanFD >= 0.3  
nrow(collated_PNC.xcp_headMotion) #3365 scans  
 
write.csv(collated_PNC.xcp_headMotion, "/cbica/projects/network_replication/input/PNC/sample_selection/collated_PNC.xcp_headMotion_20230629.csv", row.names=F)
```



## 5) include scans with at least 7 minutes of scan time
```{r scan_time}
# Calculate scan time for each subject 
collated_PNC.xcp_headMotion <- read.csv("/cbica/projects/network_replication/input/PNC/sample_selection/collated_PNC.xcp_headMotion_20230629.csv")
# load cubids summary and files csv
CUBIDS_summary <- read.csv("/cbica/projects/network_replication/input/PNC/CUBIDS_csvs/PNC_FINAL_summary.csv")
CUBIDS_summary <- CUBIDS_summary[,-c(1:4)]
CUBIDS_files <- read.csv("/cbica/projects/network_replication/input/PNC/CUBIDS_csvs/PNC_FINAL_files.csv")

# filter only for fMRI
CUBIDS_files_func <- CUBIDS_files[-c(which(str_detect(CUBIDS_files$FilePath, "dwi")), which(str_detect(CUBIDS_files$FilePath, "anat")), which(str_detect(CUBIDS_files$FilePath, "fmap"))),]
 
# make columns for subject ID, site, task 
CUBIDS_files_func <- CUBIDS_files_func %>% 
  mutate(sub=str_extract(FilePath, "sub-[0-9]*")) %>% 
  mutate(task =ifelse(str_detect(FilePath, "rest"),  # if the task is a rest scan, the filename looks like task-rest_acq-*
                      gsub("acq-", "", gsub("task-", "", str_extract(FilePath, "task-rest_acq-[a-z0-9]*"))), 
                      gsub("task-", "", str_extract(FilePath, "task-[a-z0-9]*"))))
 
CUBIDS_files_func <- CUBIDS_files_func %>% 
  mutate(sub_task=paste0(sub, "_", task))
collated_PNC.xcp_headMotion <- collated_PNC.xcp_headMotion %>%  
  mutate(sub_task= ifelse(str_detect(task, "rest"), paste0(sub, "_", task, "_", str_extract(acq, "singleband|100")), paste0(sub, "_", task)))
 
  
fMRIinclude_CUBIDS <- merge(collated_PNC.xcp_headMotion, dplyr::select(CUBIDS_files_func, NumVolumes, RepetitionTime, sub_task), by ="sub_task")
  
# sort dataframe by subject and calculate scan time
fMRIinclude_CUBIDS <- fMRIinclude_CUBIDS %>% arrange(sub) %>% mutate(ScanTimeMinutes = NumVolumes*RepetitionTime/60) 
fMRIinclude_CUBIDS_ScanTime <- fMRIinclude_CUBIDS %>% group_by(sub) %>% summarise(ScanTime_Total = sum(ScanTimeMinutes))
 
 
range(fMRIinclude_CUBIDS_ScanTime$ScanTime_Total) # 3.60 to 33.25
median(fMRIinclude_CUBIDS_ScanTime$ScanTime_Total) # 28.25 min
getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}
getmode(fMRIinclude_CUBIDS_ScanTime$ScanTime_Total) #28.25 min
  
# exclude participants with less than 7 min of scan time
subject_scanTime_exclude <- fMRIinclude_CUBIDS_ScanTime$sub[c(which(fMRIinclude_CUBIDS_ScanTime$ScanTime_Total < 7))] 
  
fMRIinclude_CUBIDS<- fMRIinclude_CUBIDS[-c(which(fMRIinclude_CUBIDS$sub %in% subject_scanTime_exclude)),]  

length(unique(fMRIinclude_CUBIDS$sub)) # N=1207
nrow(fMRIinclude_CUBIDS) # 3310 scans


fMRIinclude_CUBIDS_ScanTime <- fMRIinclude_CUBIDS %>% group_by(sub) %>% summarise(ScanTime_Total = sum(ScanTimeMinutes))
 
max(fMRIinclude_CUBIDS_ScanTime$ScanTime_Total) # 33 minutes and 15 seconds
range(fMRIinclude_CUBIDS_ScanTime$ScanTime_Total) # 8.35 33.25
median(fMRIinclude_CUBIDS_ScanTime$ScanTime_Total) # 28.25

fMRIinclude_CUBIDS_NumVols <- fMRIinclude_CUBIDS %>% group_by(sub) %>% summarise(NumVols_Total = sum(NumVolumes))
max(fMRIinclude_CUBIDS_NumVols$NumVols_Total) # 665 volumes

saveRDS(fMRIinclude_CUBIDS, "/cbica/projects/network_replication/input/PNC/sample_selection/fMRIinclude_CUBIDS_20230629.RData")
```
 

# Final Demographics Dataframe
```{r final_participant_list}

fMRIinclude_CUBIDS <- readRDS("/cbica/projects/network_replication/input/PNC/sample_selection/fMRIinclude_CUBIDS_20230629.RData")
final_participants <- data.frame(unique(fMRIinclude_CUBIDS$sub))
names(final_participants) <- "sub"  
final_demographics <- merge(demographics, final_participants, by = "sub")
 
## include average of relMeansRMSMotion and meanFD across the acquisitions included in calculating connectivity matrix 
# for each subject, take average relMeansRMSMotion and meanFD
subject <- c()
ses <- c()
avg_meanFD_vec <- c()
for(i in c(1:length(unique(fMRIinclude_CUBIDS$sub)))){
  indices <- which(fMRIinclude_CUBIDS$sub == unique(fMRIinclude_CUBIDS$sub)[i])
  avg_meanFD <- mean(as.numeric(fMRIinclude_CUBIDS$meanFD[indices]))
  subject <- append(subject, unique(fMRIinclude_CUBIDS$sub)[i])
  ses <- append(ses,fMRIinclude_CUBIDS$ses[indices[1]])
  avg_meanFD_vec <- append(avg_meanFD_vec, avg_meanFD)
}  

PNC_avgMotion <- data.frame(cbind(subject, ses, avg_meanFD_vec))
names(PNC_avgMotion) <- c("sub", "ses", "meanFD_avgSes")
PNC_avgMotion$meanFD_avgSes <- as.numeric(PNC_avgMotion$meanFD_avgSes)
final_dem_df <- merge(final_demographics, PNC_avgMotion, by="sub")
   

length(which(final_dem_df$sex=="2")) # 646 females 

unique(final_dem_df$race)
#"1= White; 
# 2= Black/African American; 
# 3= US_India/Alaska Native;
# 4=Asian; 
# 5=More Than One Race; 
# 6=Hawaiian/Pacific;  
 
length(which(final_dem_df$race==6))/nrow(final_dem_df)
# white = 551 - 45.7%
# black = 513 - 42.5%
# other (native american + hawaiian pi) = 4 + 1 - 0.41%
# asian = 11 - 0.9%
# missing = 0
# mixed = 127 - 10.5%

mean(final_dem_df$age) # mean = 15.4
sd(final_dem_df$age) # SD = 3.5

write.csv(final_dem_df, "/cbica/projects/network_replication/input/PNC/sample_selection/PNC_demographics_finalsample_20230629.csv", row.names=F)
```


# Final CIFTI File list (for creating connectivity matrices)
```{r ciftiFile_list, include=FALSE, cache=TRUE}
  
fMRIinclude_CUBIDS <- readRDS("/cbica/projects/network_replication/input/PNC/sample_selection/fMRIinclude_CUBIDS_20230629.RData")
 
# extract name of .nii.gz file
CUBIDS_files_func <- CUBIDS_files_func %>% mutate(filenames = str_extract(FilePath, "sub-[0-9]*_.*"))

fMRIinclude_CUBIDS <- merge(fMRIinclude_CUBIDS, CUBIDS_files_func[,c(30,31)], by="sub_task")

atlases <- c("Glasser", "Gordon", "Schaefer217", "Schaefer417")
subject_list <- list()
ptseries_filenames <- list()
task_list <- list()
atlas_list <- list()
variant_list <- list()
task_scanInfo_list <- list()
 
for (i in c(1:nrow(fMRIinclude_CUBIDS))) {
  for (j in c(1:length(atlases))){
  atlas <- atlases[j]
  subject <- fMRIinclude_CUBIDS$sub[i]
  task <- fMRIinclude_CUBIDS$task[i]
  task_scanInfo <- gsub("[0-9]_", "", str_extract(fMRIinclude_CUBIDS$sub_task[i], "[0-9]_.*"))
  variant <- fMRIinclude_CUBIDS$acq[i]
  #file <- fMRIinclude_CUBIDS$filenames[i]
  
  atlas_list <- append(atlas, atlas_list)
  subject_list <- append(subject, subject_list)
  task_list <- append(task, task_list)
  variant_list <- append(variant, variant_list)
  task_scanInfo_list <- append(task_scanInfo, task_scanInfo_list)
  if (variant == "") {
    file <- paste0(subject, "_ses-PNC1_task-", task, "_space-fsLR_atlas-", atlas, "_den-91k_bold.ptseries.nii")
  ptseries_filenames <- append(file, ptseries_filenames)
    
  } else {
    file <- paste0(subject, "_ses-PNC1_task-", task, "_acq-", variant, "_space-fsLR_atlas-", atlas, "_den-91k_bold.ptseries.nii")
  ptseries_filenames <- append(file, ptseries_filenames)
  }
  
  }
  print(paste(subject, "done", i, "/", nrow(fMRIinclude_CUBIDS)))
}

 
   
filenamesDF <- as.data.frame(do.call(rbind, ptseries_filenames))
subject_namesDF <- as.data.frame(do.call(rbind, subject_list))
task_namesDF <- as.data.frame(do.call(rbind, task_list))
task_scanInfo_namesDF <- as.data.frame(do.call(rbind, task_scanInfo_list))
variant_namesDF <- as.data.frame(do.call(rbind, variant_list))
atlas_namesDF <- as.data.frame(do.call(rbind, atlas_list))
  
file_paths <- as.data.frame(cbind(subject_namesDF, task_namesDF, task_scanInfo_namesDF, atlas_namesDF, variant_namesDF, filenamesDF))
names(file_paths) <- c("subject", "task", "task_scanInfo","atlas", "acq", "filenames")
 
# make file paths (note that "singleband" and "100" will appear in filenames)
file_paths <- file_paths %>% mutate(path = paste0("/cbica/projects/network_replication/input/PNC/pnc_xcp/", subject, "/", filenames)) %>% mutate(sub_task= ifelse(str_detect(task, "rest"), paste0(subject, "_", task, "_", str_extract(acq, "singleband|100")), paste0(subject, "_", task)))
   
file_paths_restOnly <- file_paths[which(file_paths$task == "rest"),] 

file_paths_FINAL <- merge(file_paths, fMRIinclude_CUBIDS[, c(1, 2)], by = "sub_task") 
file_paths_restOnly_FINAL <- merge(file_paths_restOnly, fMRIinclude_CUBIDS[, c(1, 2)], by = "sub_task") 
 
length(unique(file_paths_FINAL$sub_task)) # 3310 scans 
length(unique(file_paths_FINAL$subject)) #N=1207
length(unique(file_paths_restOnly_FINAL$sub_task)) # 1068 scans
  
PNC_qc_filenames_atlases <- list(fMRIinclude_CUBIDS, file_paths_FINAL) 
# which(!file.exists(PNC_qc_filenames_atlases[[2]]$path)) # to double check if all filepaths exist
 

PNC_qc_filenames_atlases_restOnly <- list(fMRIinclude_CUBIDS[c(which(fMRIinclude_CUBIDS$task=="rest")),], file_paths_restOnly_FINAL) 
 
saveRDS(PNC_qc_filenames_atlases, "/cbica/projects/network_replication/input/PNC/sample_selection/PNC_FinalSample_withCUBIDS_CIFTI_20230629.RData")
saveRDS(PNC_qc_filenames_atlases_restOnly, "/cbica/projects/network_replication/input/PNC/sample_selection/PNC_FinalSample_withCUBIDS_restOnly_20230629.RData")
```
 

# Sensitivity Analysis: Final demographics for rest only
- include participants with at least 6 minutes of rest-only scan time
```{r}

PNC_qc_filenames_atlases_restOnly <- readRDS("/cbica/projects/network_replication/input/PNC/sample_selection/PNC_FinalSample_withCUBIDS_restOnly_20230629.RData")

### Include participants with >= 7 minutes of resting state fMRI
fMRIinclude_CUBIDS_ScanTime_restOnly <- PNC_qc_filenames_atlases_restOnly[[1]] %>% group_by(sub) %>% summarise(ScanTime_Total = sum(ScanTimeMinutes))
 
range(fMRIinclude_CUBIDS_ScanTime_restOnly$ScanTime_Total) 
length(which(fMRIinclude_CUBIDS_ScanTime_restOnly$ScanTime_Total >= 6)) #998

max(fMRIinclude_CUBIDS_ScanTime_restOnly$ScanTime_Total) #11.2 minutes

fMRIinclude_CUBIDS_NumVols_restOnly <- PNC_qc_filenames_atlases_restOnly[[1]] %>% group_by(sub) %>% summarise(NumVolsTotal = sum(NumVolumes))
max(fMRIinclude_CUBIDS_NumVols_restOnly$NumVolsTotal) #224 volumes


final_participants_restOnly <- data.frame(fMRIinclude_CUBIDS_ScanTime_restOnly$sub[c(which(fMRIinclude_CUBIDS_ScanTime_restOnly$ScanTime_Total >= 6))])
names(final_participants_restOnly) <- "sub" 
  
PNC_FinalSample_CUBIDS_restOnly <- PNC_qc_filenames_atlases_restOnly[[1]] 
PNC_FinalSample_CUBIDS_restOnly <- merge(PNC_FinalSample_CUBIDS_restOnly, final_participants_restOnly)
 
PNC_qc_filenames_atlases_restOnly_final <- merge(PNC_qc_filenames_atlases_restOnly[[2]], final_participants_restOnly)
PNC_qc_filenames_atlases_restOnly_final <- list(PNC_FinalSample_CUBIDS_restOnly, PNC_qc_filenames_atlases_restOnly_final)
dim(PNC_qc_filenames_atlases_restOnly_final[[1]]) #1060 scans
 

saveRDS(PNC_qc_filenames_atlases_restOnly_final,"/cbica/projects/network_replication/input/PNC/sample_selection/PNC_FinalSample_withCUBIDS_restOnly_20230629.RData")

#saveRDS(PNC_qc_filenames_atlases_restOnly_final,"/cbica/projects/network_replication/input/PNC/sample_selection/PNC_FinalSample_withCUBIDS_restOnly_20230203.RData")
 
 
final_demographics_restOnly <- merge(demographics, final_participants_restOnly, by = "sub")
 
## include average of relMeansRMSMotion and meanFD across the acquisitions included in calculating connectivity matrix 
# for each subject, take average relMeansRMSMotion and meanFD
subject <- c()
ses <- c()
avg_meanFD_vec <- c()
for(i in c(1:length(unique(PNC_FinalSample_CUBIDS_restOnly$sub)))){
  indices <- which(PNC_FinalSample_CUBIDS_restOnly$sub == unique(PNC_FinalSample_CUBIDS_restOnly$sub)[i])
  avg_meanFD <- mean(as.numeric(PNC_FinalSample_CUBIDS_restOnly$meanFD[indices]))
  subject <- append(subject, unique(PNC_FinalSample_CUBIDS_restOnly$sub)[i])
  ses <- append(ses,PNC_FinalSample_CUBIDS_restOnly$ses[indices[1]])
  avg_meanFD_vec <- append(avg_meanFD_vec, avg_meanFD)
}  
 

PNC_avgMotion <- data.frame(cbind(subject, ses, avg_meanFD_vec))
names(PNC_avgMotion) <- c("sub", "ses", "meanFD_avgSes")
PNC_avgMotion$meanFD_avgSes <- as.numeric(PNC_avgMotion$meanFD_avgSes)
final_dem_restOnly_df <- merge(final_demographics_restOnly, PNC_avgMotion, by="sub")
  
length(unique(final_dem_restOnly_df$sub)) # N=998
length(which(final_dem_restOnly_df$sex==2)) #549

write.csv(final_dem_restOnly_df, "/cbica/projects/network_replication/input/PNC/sample_selection/PNC_demographics_finalsample_restOnly_20230629.csv", row.names=F)

```

