---
title: "BNC GAMs: PNC (Schaefer200x17)"
author: "Valerie Jill Sydnor adapted by Audrey Luo"
output:
  html_document:
    code_folding: show
    highlight: haddock
    theme: lumen
    toc: yes
    toc_depth: 4
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
source("/cbica/projects/network_replication/adapted_Rscripts/GAM_functions.R")
```


**Prepare BNC + Demographics data frame for GAMs**

```{r}
participants <- read.csv("/cbica/projects/network_replication/adapted_Rscripts/participants_allIDs.csv") #final study sample pnc IDs (bblid/scanid) from Adam Pines's multiscale paper
demographics <- read.csv("/cbica/projects/network_replication/PNC/n1601_demographics_go1_20161212.csv") #PNC demographics information
demographics <- demographics %>% mutate(age = (ageAtScan1/12)) #format age variable
demographics$sex <- as.factor(demographics$sex) #format sex variable

demographics <- merge(participants, demographics, by="scanid") #get demographics for final study sample only via ID matching
relRMS <- read.csv("/cbica/projects/network_replication/PNC/qc_files/RBC_PNC_relMeans.csv") 
demographics <- merge(demographics, relRMS, by="rbcid") #add motion information to demographics df
```

# make BNC-demographics .csv's
```{r} 
BNC_subxparcel_matrix_schaefer200 <- read.csv("/cbica/projects/network_replication/BNC/BNC_subxparcel_matrix_schaefer200x17.csv") #participant x schaefer region BNC spreadsheet
BNC_subxparcel_matrix_schaefer200 <- BNC_subxparcel_matrix_schaefer200[-c(1:7, 24, 690, 691),] # the subjects that should've been removed earlier 
names(BNC_subxparcel_matrix_schaefer200)
col_rm <- as.numeric(levels(as.factor(as.data.frame(which(is.na(BNC_subxparcel_matrix_schaefer200), arr.ind=TRUE))$col)))
BNC_subxparcel_matrix_schaefer200 <- BNC_subxparcel_matrix_schaefer200[, -col_rm]
BNC.schaefer200.pnc <- merge(BNC_subxparcel_matrix_schaefer200, demographics, by="rbcid") #get schaefer BNC data and demographics for final study sample via ID matching
names(BNC.schaefer200.pnc) <- gsub('X17Networks_', "", names(BNC.schaefer200.pnc))
#write.csv(BNC.schaefer200.pnc, "/cbica/projects/network_replication/BNC/BNCschaefer200x17_demographics_finalsample.csv")
 
 
```

# load BNC-demographics df's
```{r}
BNC.schaefer200.pnc <- read.csv('/cbica/projects/network_replication/BNC/BNCschaefer200x17_demographics_finalsample.csv')
```


# edit parcel labels to reflect SNR mask
```{r}
schaefer200.parcel.labels <- read.csv("/cbica/projects/network_replication/atlases/parcellations/schaefer200x17_regionlist.csv", header = T) #schaefer parcel names in order of surface data
names(schaefer200.parcel.labels)[2] <- "orig_parcelname"
# remove parcels using SNR mask
SNR.mask.schaefer200 <- read.csv("/cbica/projects/network_replication/atlases/Masks/SNRmask_schaefer200x17.csv")
rm <- which(SNR.mask.schaefer200$SNR.mask == 0)
# also remove X17Networks_LH_LimbicA_TempPole_4 -- all of its between-network parcels are NA'd out by the mask, so it doesn't have a BNC value
schaefer200.parcel.labels <- schaefer200.parcel.labels[-rm,]
  
```

**Fit GAMs**

Fit GAM (BNC ~ s(age) + sex + RMSmotion)) per each region in atlas and save out statistics and derivative-based characteristics

GAMs for Schaefer200
```{r}
gam.BNC.age.schaefer200 <- matrix(data=NA, nrow=dim(schaefer200.parcel.labels)[1], ncol=9) #empty matrix to save gam.fit output to
 
# schaefer200 parcel labels and the labels from BNC.schaefer200.pnc don't currently match. And I don't think parcelnames can begin with a number. following 2 lines fixes this
schaefer200.parcel.labels$orig_parcelname <- gsub('17Networks_', "", schaefer200.parcel.labels$orig_parcelname)
 

# get GAMs for BNC.schaefer200.pnc - which includes schaefer200 BNC data and demographics
for(row in c(1:nrow(schaefer200.parcel.labels))){ #for each schaefer200 region
  region <- schaefer200.parcel.labels$orig_parcelname[row] 
  GAM.RESULTS <- gam.fit(measure = "BNC", atlas = "schaefer200", dataset = "pnc", region = region, smooth_var = "age", covariates = "sex + RMSmotion") #run the gam.fit function
  gam.BNC.age.schaefer200[row,] <- GAM.RESULTS}
 
 
gam.BNC.age.schaefer200 <- as.data.frame(gam.BNC.age.schaefer200)
colnames(gam.BNC.age.schaefer200) <- c("label","GAM.age.Fvalue","GAM.age.pvalue","GAM.age.AdjRsq","Anova.age.pvalue","age.onsetchange","age.peakchange","maxage.BNC.increase","age.maturation")
cols = c(2:9)    
gam.BNC.age.schaefer200[,cols] = apply(gam.BNC.age.schaefer200[,cols], 2, function(x) as.numeric(as.character(x)))
gam.BNC.age.schaefer200 <- gam.BNC.age.schaefer200 %>% mutate(significant = (Anova.age.pvalue < 0.05))
#write.csv(gam.BNC.age.schaefer200, "/cbica/projects/network_replication/BNC/GAM/GAMresults.BNC.age.schaefer200x17.csv", row.names = F, quote = F)
```
 
# load GAMs output
```{r} 
gam.BNC.age.schaefer200 <- read.csv("/cbica/projects/network_replication/BNC/GAM/GAMresults.BNC.age.schaefer200x17.csv")
```



**Estimate GAM smooths based on model-predicted data and save out predicted y data**
Estimate GAM smooths - Schaefer200
```{r}
gam.smooths.schaefer200 <- matrix(data=NA, ncol=7) #empty matrix to save gam.predsmooth fits to
colnames(gam.smooths.schaefer200) <- c("age","fit","se.fit","selo","sehi","index","label")

gam.peaks.schaefer200 <- matrix(data=NA, ncol=2) #empty matrix to save measure peaks to (value of x when y is predicted to be maximal)
colnames(gam.peaks.schaefer200) <- c("label","age.peak")


for(row in c(1:nrow(schaefer200.parcel.labels))){ #for each schaefer200 region
  
  region <- schaefer200.parcel.labels$orig_parcelname[row] #get the region name
  GAM.SMOOTH <- gam.predsmooth(measure = "BNC", atlas = "schaefer200", dataset = "pnc", region = region, smooth_var = "age", covariates = "sex + RMSmotion") #run the gam.predsmooth function
  
  preddata <- as.data.frame(GAM.SMOOTH[3]) #get predicted.smooth df from function output
  preddata$index <- rep(x=row, 1000) #region index
  preddata$label <- rep(x=GAM.SMOOTH[1], 1000) #label
  gam.smooths.schaefer200 <- rbind(gam.smooths.schaefer200, preddata)
  
  datapeak <- as.data.frame(cbind(GAM.SMOOTH[1], GAM.SMOOTH[2]))
  colnames(datapeak) <- c("label","age.peak")
  gam.peaks.schaefer200 <- rbind(gam.peaks.schaefer200, datapeak)
}
gam.smooths.schaefer200 <- gam.smooths.schaefer200[-1,] #remove empty initilization row
gam.smooths.schaefer200$label <- as.character(gam.smooths.schaefer200$label)
gam.peaks.schaefer200 <- gam.peaks.schaefer200[-1,] #remove empty initilization row
gam.peaks.schaefer200$label <- as.character(gam.peaks.schaefer200$label)
gam.peaks.schaefer200$age.peak <- as.numeric(gam.peaks.schaefer200$age.peak)
 
#write.csv(gam.smooths.schaefer200,"/cbica/projects/network_replication/BNC/GAM/GAMsmoothfits.BNC.age.schaefer200x17.csv", row.names = F, quote = F)
#write.csv(gam.peaks.schaefer200, "/cbica/projects/network_replication/BNC/GAM/GAMpeaks.BNC.age.schaefer200x17.csv", row.names = F, quote = F)
 
```
