---
title: "Compute Within-Network connectivty in PNC (Gordon)"
author: "Audrey Luo"
output:
  html_document:
    code_folding: show
    highlight: haddock
    theme: lumen
    toc: yes
    toc_depth: 5
    toc_float: yes
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ciftiTools)
ciftiTools.setOption('wb_path', '/Applications/workbench/')
library(gifti)
library(cifti)
Sys.setenv(RGL_USE_NULL=TRUE)
library(ggseg)
library(ggsegExtra)  
library(ggsegGlasser) 
library(ggsegSchaefer)  
library(viridis)
require(ggplot2)
library(dplyr)
```

 
load region list
```{r}
gordon.parcel.labels <- read.csv("/cbica/projects/network_replication/atlases/parcellations/gordon_regionlist_xcp.csv", header = F)
gordon.communityAffil <- read.csv("/cbica/projects/network_replication/atlases/parcellations/Gordon333_Network/gordon333CommunityAffiliation.1D.csv", header=F)
gordon.parcel.labels <- as.data.frame(cbind(gordon.parcel.labels$V1, gordon.communityAffil$V1))
names(gordon.parcel.labels) <- c("label", "network")
#  make dataframe where rownames are the commAffil number, and then need to transpose V1 to be rows 
gordon_rows <- as.data.frame(t(gordon.parcel.labels$network))
gordon_commAffil_mat <- as.data.frame(gordon_rows[rep(seq_len(nrow(gordon_rows)), each = 333), ])
rownames(gordon_commAffil_mat) <- NULL
```

# Compute Within-Network Connectivty (WNC) function 

```{r}
SNRmask_gordon <- read.csv('/cbica/projects/network_replication/atlases/Masks/SNRmask_gordon.csv')
  
# computeWNC(rbcid, "gordon", gordon_commAffil_mat, gordon.parcel.labels$network)

computeWNC <- function(rbcid, atlas, community_affiliation_mat, network_assignment){
  #read in connectivity matrix
  if(atlas == "gordon"){
    connect.matrix <- read_cifti(sprintf("/cbica/projects/network_replication/pconn/%1$s/%1$s_ses-PNC1_task-rest_acq-singleband_space-fsLR_atlas-Gordon_den-91k_den-91k_bold.pconn.nii",rbcid))
    mask <- SNRmask_gordon} #333 x 333 matrix 
 
  # set rows and columns corresponding to parcel # in mask to NA
  connect.matrix$data[which(mask == 0), ] <- NA 
  connect.matrix$data[,which(mask == 0)] <- NA
  
  #compute average within-network connectivity 
  WNC <- c()
  for (i in 1:nrow(connect.matrix$data)) {  
    within_network_values <- c() 
    WNC_per_node <- c()
    for (j in 1:length(connect.matrix$data[i,])) {  # entire  row
      if(is.na(connect.matrix$data[i,j]) || connect.matrix$data[i,j] == 1) { # add NA if excluded by mask or identity
        within_network_values <- append(within_network_values, NA);
        } else if (gordon.parcel.labels$network[i] == gordon_commAffil_mat[i,j]) { 
          within_network_values <- append(within_network_values, connect.matrix$data[i,j])
          } else if (gordon.parcel.labels$network[i] != gordon_commAffil_mat[i,j]) {  
            within_network_values <- append(within_network_values, NA)
          } 
      }
    #print(within_network_values)  
    WNC_per_node <- append(WNC_per_node, mean(within_network_values, na.rm=TRUE))  
    #print(WNC_per_node) # 1 value
    WNC <- append(WNC, WNC_per_node)  
    } 
  return(WNC)
}
  
  
```


# Compute WNC for each subject  
```{r, echo=T, eval=F, warning=F, message=F}

participants <- read.csv('/cbica/projects/network_replication/adapted_Rscripts/participants_allIDs.csv')
subs_no_files <- read.csv('/cbica/projects/network_replication/adapted_Rscripts/subs_no_files.csv', row.names=NULL)
subs_no_files <- subs_no_files[,2]

WNC.subxparcel.matrix.gordon <- matrix(data = NA, nrow = nrow(participants), ncol = 334)
regionheaders <- as.character(gordon.parcel.labels$label)
demoheaders <- c("rbcid")
colheaders <- as.matrix(c(demoheaders,regionheaders))
colnames(WNC.subxparcel.matrix.gordon) <- colheaders
 
#compute WNC for each subject  
for(sub in c(1:nrow(participants))){
  rbcid=as.character(participants[sub,4])
  if(rbcid %in% subs_no_files){
    next
  }
  else {
  rbcid.data.gordon <- computeWNC(rbcid, "gordon", gordon_commAffil_mat, gordon.parcel.labels$network)
  WNC.subxparcel.matrix.gordon[sub,] <- cbind(rbcid, t(rbcid.data.gordon))
  print(paste(sub, rbcid, "gordon"))
  }
}

as.data.frame(WNC.subxparcel.matrix.gordon)
 
 
#write.csv(WNC.subxparcel.matrix.gordon, "/cbica/projects/network_replication/WNC/WNC_subxparcel_matrix_gordon.csv", row.names=F, quote=F)
 
 
 
