---
title: "WNC Developmental Trajectories: PNC (Gordon)"
author: "Valerie Jill Sydnor, adapted by Audrey Luo"
output:
  html_document:
    code_folding: show
    highlight: haddock
    theme: lumen
    toc: yes
    toc_depth: 4
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '4'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
require(ggplot2)
library(cowplot)
library(cifti)
library(ggseg)
Sys.setenv(RGL_USE_NULL=TRUE)
library(ggsegExtra)
library(ggsegGordon)
library(ggcorrplot)
library(viridis)
library(scales)
library(stringr)
library(tidyr)


```
  
# load gordon parcellated S-A axis
```{r}
# load SNR mask 
SNRmask_gordon <- read.csv('/cbica/projects/network_replication/atlases/Masks/SNRmask_gordon.csv')

# load region list
gordon.parcel.labels <- read.csv("/cbica/projects/network_replication/atlases/parcellations/gordon_regionlist_xcp.csv", header = F) 
names(gordon.parcel.labels) <- "label"
gordon.parcel.labels[which(SNRmask_gordon == 0),] <- NA # apply SNR mask to parcel names
gordon.parcel.labels <- na.omit(gordon.parcel.labels)
 

# load parcellated SA axis
gordon_SAaxis_cifti <- read_cifti("/cbica/projects/network_replication/SAaxis/SensorimotorAssociation_Axis_parcellated/SensorimotorAssociation.Axis.Gordon333.pscalar.nii")  

gordon_SAaxis <- as.data.frame(cbind(rank(gordon_SAaxis_cifti$data), names(gordon_SAaxis_cifti$Parcel)))
colnames(gordon_SAaxis) <- c("SA.axis_rank","label")

# apply SNR mask
gordon_SAaxis[which(SNRmask_gordon == 0),] <- NA
gordon_SAaxis <- na.omit(gordon_SAaxis) 
gordon_SAaxis$label <- gordon.parcel.labels$label
```


```{r include=FALSE}
## GAM Results

gam.WNC.age.gordon <- read.csv("/cbica/projects/network_replication/WNC/GAM/GAMresults.WNC.age.gordon.csv")

gam.WNC.age.gordon <- gam.WNC.age.gordon %>% select(-label)
gam.WNC.age.gordon$label <- gordon_SAaxis$label
 

gam.smooths.gordon <- read.csv("/cbica/projects/network_replication/WNC/GAM/GAMsmoothfits.WNC.age.gordon.csv")
gam.smooths.gordon$orig_parcelname <- gam.smooths.gordon$label
 

gam.agepeaks.gordon <- read.csv("/cbica/projects/network_replication/WNC/GAM/GAMpeaks.WNC.age.gordon.csv")
gam.agepeaks.gordon <- gam.agepeaks.gordon %>% select(-label)
gam.agepeaks.gordon$label <- gordon_SAaxis$label


```

 
# gordon final Dfs
```{r include=FALSE}
# Combine into Final Dfs
df.list <- list(gordon_SAaxis,gam.WNC.age.gordon)
  
WNC.axis <- Reduce(function(x,y) merge(x,y, all=TRUE, sort=F), df.list) 
WNC.axis$SA.axis_rank <- as.numeric(WNC.axis$SA.axis_rank)
 
```

 
 
```{r include=FALSE}
  
a <- merge(gordon.parcel.labels, gordon_SAaxis, by="label", sort=F)
a$label <- gsub("17Networks_", "", a$label)
 
gam.smooths.gordon <- left_join(gam.smooths.gordon, a, by = "label")
#names(gam.smooths.gordon)[11] <- "SA.axis_rank"
gam.smooths.gordon$SA.axis_rank <-as.numeric(gam.smooths.gordon$SA.axis_rank) 

gam.agepeaks.gordon <- left_join(gam.agepeaks.gordon, gordon_SAaxis, by="label")
gam.agepeaks.gordon$SA.axis_rank <-as.numeric(gam.agepeaks.gordon$SA.axis_rank) 
```
 
 
#Load Spin Test Parcel Rotation Matrix
```{r}
source("/cbica/projects/network_replication/software/rotate.parcellation.R")
source("/cbica/projects/network_replication/software/perm.sphere.p.R")
library(fabisearch) # load gordon atlas coordinates
 
gordon.coords <- gordatlas[2:4]  #coordinates of gordon.coords parcel centroids on the freesurfer sphere
 
#perm.id.full <- rotate.parcellation(coord.l = as.matrix(gordon.coords[1:161,]), coord.r = as.matrix(gordon.coords[162:333,]), nrot = 10000) #rotate the gordon.coords parcellation 10,000 times on the freesurfer sphere to generate spatial nulls for spin-based permutation significance testing 


## saveRDS(perm.id.full, "/cbica/projects/network_replication/software/rotate_parcellation/gordon.coords_sphericalrotations_N10k.rds")

perm.id.full <- readRDS("/cbica/projects/network_replication/software/rotate_parcellation/gordon.coords_sphericalrotations_N10k.rds")
```

#create df.dev.spin formatted for spatial permutation testing
```{r}
# need to reintroduced the parcels removed by SNRmask as NA's

gordon.parcel.labels_noMask <- read.csv("/cbica/projects/network_replication/atlases/parcellations/gordon_regionlist_xcp.csv", header = F) 
names(gordon.parcel.labels_noMask) <- "label"
gordon.parcel.labels_noMask
setdiff(WNC.axis$label, gordon.parcel.labels_noMask$label)

gordon.parcel.labels_noMask$label[which(!gordon.parcel.labels_noMask$label %in% WNC.axis$label)] # names of removed parcels


# need to go through parcel.labels and see which are in WNC.axis label
# then for the ones that aren't in WNC.axis$label, insert parcel.labels[row_of_missing_label] into WNC.axis, and have the rest of the row be NA
# r = the row index -- indices of SNR removed parcels
# newrow = content of inserted row -- c('name of parcel', NA, NA, NA etc)
# existingDF = WNC.axis
insertRow <- function(r, existingDF, orig.parcel.labels) {
  newrow <- c(paste0(orig.parcel.labels[r]), rep(NA, 10)) # format data for spin tests by assigning NA to low SNR parcels, treating them like the medial wall
  existingDF[seq(r+1,nrow(existingDF)+1),] <- existingDF[seq(r,nrow(existingDF)),]
  existingDF[r,] <- newrow
  existingDF
}

 
r <- which(!gordon.parcel.labels_noMask$label %in% WNC.axis$label) # indices of removed parcels
existingDF <- WNC.axis  
 
for(i in c(1:length(r))){
   existingDF <- insertRow(r[i], existingDF, gordon.parcel.labels_noMask$label)
}

   
df.dev.spin <- rbind(existingDF[1:161,], existingDF[162:333,]) #format df as left hemisphere -> right hemisphere for spin tests
df.dev.spin <- cbind(df.dev.spin, SNRmask_gordon)
 
```

# WNC Developmental Effects

## Number of significant parcels (FDR corrected)

```{r echo=FALSE}
WNC.axis$Anova.age.pvalue.fdr <- p.adjust(WNC.axis$Anova.age.pvalue, method=c("fdr"))
cat(sprintf("There are %s/%s significant parcels", sum(WNC.axis$Anova.age.pvalue.fdr < 0.05), nrow(WNC.axis)))

WNC.axis$significant.fdr <- WNC.axis$Anova.age.pvalue.fdr < 0.05
WNC.axis$significant.fdr[WNC.axis$significant.fdr == TRUE] <- 1
WNC.axis$significant.fdr[WNC.axis$significant.fdr == FALSE] <- 0
 
```
 
## Age Effect by S-A Axis position

```{r}
cor.test(WNC.axis$GAM.age.AdjRsq, as.numeric(WNC.axis$SA.axis_rank), method=c("spearman"), exact=F)
cor(as.numeric(df.dev.spin$GAM.age.AdjRsq), as.numeric(df.dev.spin$SA.axis_rank),method="spearman", use="complete.obs")

perm.sphere.p(as.numeric(df.dev.spin$GAM.age.AdjRsq), as.numeric(df.dev.spin$SA.axis_rank), perm.id.full, corr.type='spearman')
```


```{r, echo=F}
library(ggpubr)
WNC.axis <- WNC.axis %>% mutate(SA.axis_rank_signif = ifelse(significant.fdr == 1, SA.axis_rank, NA))

 
## SA axis average rank vs. age effect
# included all datapoints for this figure
cor.test(WNC.axis$GAM.age.AdjRsq, as.numeric(WNC.axis$SA.axis_rank), method=c("spearman"), exact=F)

r_text <- expression(paste(italic("r"), "= -0.24, ", italic(p[spin]), "= 0.08"))

(gordon_SA.AgeEffect <- ggplot(WNC.axis, aes(x=SA.axis_rank, y=GAM.age.AdjRsq, fill = SA.axis_rank_signif)) + geom_point(color = "white", shape = 21, size=2) +
scale_fill_gradient2(low="#6f1282",high = "goldenrod1",, mid = "#EBDAFF", midpoint = median(WNC.axis$SA.axis_rank), na.value="gray") +
labs(fill = "SA Axis Rank", x="\nSensorimotor-Association Axis Rank\n", y=expression(paste("Age Effect (Delta Adj", " R"^2, ")"))) +
geom_smooth(data = WNC.axis, method='lm', se=TRUE, fill=alpha(c("gray70"),.9), col="black") +
theme(
axis.title.x=element_text(size=12, color = "black"),
axis.title.y=element_text(size=12, color = "black"),
axis.line = element_line(color = "black"),
axis.text=element_text(size=12, color = "black"),
panel.background=element_blank(),
legend.position = "right") +
annotate(geom="text", x=240, y=0.055, label=r_text, color="black"))
# ggsave(gordon_SA.AgeEffect, file="/cbica/projects/network_replication/adapted_Rscripts/Figures/Gordon333/WNC/gordon_SA.AgeEffect.pdf", width = 5, height=4, dpi=300)

```
 
  
## WNC Developmental Trajectories

```{r}

gam.smooths.gordon$SA.axis_rank <- as.numeric(gam.smooths.gordon$SA.axis_rank)
# seems like transmodal areas have greater WNC and seem to increase with age, while unimodal areas have smaller WNC and increase or stays the same with age
(gordon_predWNC <- ggplot(gam.smooths.gordon,aes(age,fit,group=index)) + 
  geom_line(data = gam.smooths.gordon, size=.8, alpha = .6, aes(color=SA.axis_rank)) + scale_color_gradient2(low="#6f1282",high = "goldenrod1", mid = "#EBDAFF", midpoint = median(WNC.axis$SA.axis_rank)) + 
  labs(color = "SA Axis Rank",
       x="Age", 
       y="Predicted Within-Network Coupling") +
  theme(
axis.title.x=element_text(size=12, color = "black"),
axis.title.y=element_text(size=12, color = "black"),
axis.line = element_line(color = "black"),
axis.text=element_text(size=12, color = "black"),
panel.background=element_blank(),
legend.position = "bottom") + coord_cartesian(expand = FALSE, xlim = c(8, 23)))
 

#ggsave(gordon_predWNC, file="/cbica/projects/network_replication/adapted_Rscripts/Figures/Gordon333/WNC/gordon_predWNC.pdf", width = 4, height=4, dpi=300)

```

## Age of Maximal WNC - can't generate for Gordon due to mismatching ggseg to xcp region names

```{r echo=FALSE}


names(gam.agepeaks.gordon)[2] <- "region"
 
right_gam.agepeaks.gordon <-  gam.agepeaks.gordon
right_gam.agepeaks.gordon$region<- gsub(x = gam.agepeaks.gordon$region, pattern = "R_", replacement = "")
right_gam.agepeaks.gordon <- right_gam.agepeaks.gordon[-which(grepl("L_", right_gam.agepeaks.gordon$region)),]

left_gam.agepeaks.gordon <-  gam.agepeaks.gordon
left_gam.agepeaks.gordon$region<- gsub(x = gam.agepeaks.gordon$region, pattern = "L_", replacement = "")
left_gam.agepeaks.gordon <- left_gam.agepeaks.gordon[-which(grepl("R_", left_gam.agepeaks.gordon$region)),]

(gordon_agepeakR <- ggplot() + geom_brain(data=right_gam.agepeaks.gordon, 
                      atlas=gordon, 
                      mapping=aes(fill=age.peak), 
                      show.legend=TRUE, 
                      hemi = "right") + 
  scale_fill_gradientn(colors = viridis_pal(option="B")(10)) + theme_void())
#ggsave(gordon_agepeakR, file="/cbica/projects/network_replication/adapted_Rscripts/Figures/gordon/GBC/gordon_agepeakR.pdf", width = 6, height=4, dpi=300)

(gordon_agepeakL <- ggplot() + geom_brain(data=left_gam.agepeaks.gordon, 
                      atlas=gordon, 
                      mapping=aes(fill=age.peak), 
                      show.legend=TRUE, 
                      hemi = "left") + 
  scale_fill_gradientn(colors = viridis_pal(option="B")(10)) + theme_void())
#ggsave(gordon_agepeakL, file="/cbica/projects/network_replication/adapted_Rscripts/Figures/gordon/GBC/gordon_agepeakL.pdf", width = 6, height=4, dpi=300)

  
plot(gordon) +
  theme(legend.position = "bottom", 
        legend.text = element_text(size = 9)) +
  guides(fill = guide_legend(ncol = 6))
 
```
