---
title: "HCPD fit GAMs"
author: "Audrey Luo"
output: html_document
---

```{r setup, include=FALSE}

library(dplyr)
source("/cbica/projects/network_replication/Rscripts/functions/main_analyses/GAM_functions.R")
source("/cbica/projects/network_replication/Rscripts/functions/main_analyses/fitGAMs.R")
 
dataset = "HCPD"
knitr::opts_chunk$set(include = FALSE, eval = TRUE, echo = FALSE, warning = FALSE, message = FALSE) 
```

# make connectivityMetric-demographics .csv's
```{r connMetric_demographics, include=FALSE}

demographics <- read.csv(sprintf("/cbica/projects/network_replication/input/%1$s/sample_selection/%1$s_demographics_finalsample_20221226.csv", dataset))
names(demographics)[c(which(names(demographics) == "sub"))] <- "subject"
demographics$age <- demographics$interview_age/12
demographics <- demographics[,c(which(names(demographics) == "subject"), which(names(demographics) == "sex"), which(names(demographics)=="age"), which(names(demographics) =="meanFD_avgSes"))] 
 
# GBC
## create GBC.glasser.HCPD, GBC.gordon.HCPD, GBC.schaefer200.HCPD, GBC.schaefer400.HCPD
atlases <- c("glasser", "gordon", "schaefer200", "schaefer400")
metric = "GBC"

for(i in c(1:length(atlases))){
  df_name <- paste0(metric, ".", atlases[i], ".", dataset)
  assign(df_name, make_connMetricsDemog_covbat(atlases[i], metric, demographics, "subject", dataset))
}

 
# BNC
## BNC.gordon.HCPD, BNC.schaefer200x7.HCPD, BNC.schaefer200x17.HCPD, BNC.schaefer400x7.HCPD, BNC.schaefer400x17.HCPD
atlases <- c("gordon", "schaefer200x7", "schaefer200x17", "schaefer400x7", "schaefer400x17")
metric = "BNC"
for(i in c(1:length(atlases))){
  df_name <- paste0(metric, ".", atlases[i], ".", dataset)
  assign(df_name, make_connMetricsDemog_covbat(atlases[i], metric, demographics, "subject", dataset))
}

# WNC
## WNC.gordon.HCPD, WNC.schaefer200x7.HCPD, WNC.schaefer200x17.HCPD, WNC.schaefer400x7.HCPD, WNC.schaefer400x17.HCPD
atlases <- c("gordon", "schaefer200x7", "schaefer200x17", "schaefer400x7", "schaefer400x17")
metric = "WNC"

for(i in c(1:length(atlases))){
  df_name <- paste0(metric, ".", atlases[i], ".", dataset)
  assign(df_name, make_connMetricsDemog_covbat(atlases[i], metric, demographics, "subject", dataset))
} 

 
# edge 
## edge.schaefer200x7.HCPD
edge.schaefer200x7.HCPD <- make_EdgeDemog_covbat("schaefer200x7", demographics, "subject", dataset)
 
 
```


 

# load connectivityMetric-demographics .csv's
```{r load_connectivity, include=TRUE}

GBC.glasser.HCPD <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/GBC/GBCglasser_demographics_finalsample_covbat.csv", dataset)) 
GBC.gordon.HCPD <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/GBC/GBCgordon_demographics_finalsample_covbat.csv", dataset)) 
 
GBC.schaefer200.HCPD <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/GBC/GBCschaefer200_demographics_finalsample_covbat.csv", dataset)) 
names(GBC.schaefer200.HCPD) <- gsub('X17Networks', "Networks", names(GBC.schaefer200.HCPD))


GBC.schaefer400.HCPD <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/GBC/GBCschaefer400_demographics_finalsample_covbat.csv", dataset)) 
names(GBC.schaefer400.HCPD) <- gsub('X17Networks', "Networks", names(GBC.schaefer400.HCPD)) 
 
 
# BNC
BNC.gordon.HCPD <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/BNC/BNCgordon_demographics_finalsample_covbat.csv", dataset))   
BNC.schaefer200x7.HCPD <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/BNC/BNCschaefer200x7_demographics_finalsample_covbat.csv", dataset)) 
names(BNC.schaefer200x7.HCPD) <- gsub("X7", "", names(BNC.schaefer200x7.HCPD))

BNC.schaefer200x17.HCPD <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/BNC/BNCschaefer200x17_demographics_finalsample_covbat.csv", dataset))    
names(BNC.schaefer200x17.HCPD) <- gsub("X17", "", names(BNC.schaefer200x17.HCPD))

BNC.schaefer400x7.HCPD <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/BNC/BNCschaefer400x7_demographics_finalsample_covbat.csv", dataset))
names(BNC.schaefer400x7.HCPD) <- gsub("X7", "", names(BNC.schaefer400x7.HCPD))

BNC.schaefer400x17.HCPD <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/BNC/BNCschaefer400x17_demographics_finalsample_covbat.csv", dataset))   
names(BNC.schaefer400x17.HCPD) <- gsub("X17", "", names(BNC.schaefer400x17.HCPD))

# WNC
WNC.gordon.HCPD <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/WNC/WNCgordon_demographics_finalsample_covbat.csv", dataset))    
WNC.schaefer200x7.HCPD <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/WNC/WNCschaefer200x7_demographics_finalsample_covbat.csv", dataset))
names(WNC.schaefer200x7.HCPD) <- gsub("X7", "", names(WNC.schaefer200x7.HCPD))

WNC.schaefer200x17.HCPD <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/WNC/WNCschaefer200x17_demographics_finalsample_covbat.csv", dataset)) 
names(WNC.schaefer200x17.HCPD) <- gsub("X17", "", names(WNC.schaefer200x17.HCPD))

WNC.schaefer400x7.HCPD <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/WNC/WNCschaefer400x7_demographics_finalsample_covbat.csv", dataset)) 
names(WNC.schaefer400x7.HCPD) <- gsub("X7", "", names(WNC.schaefer400x7.HCPD))

WNC.schaefer400x17.HCPD <- read.csv(sprintf("/cbica/projects/network_replication/output/%1$s/WNC/WNCschaefer400x17_demographics_finalsample_covbat.csv", dataset))  
names(WNC.schaefer400x17.HCPD) <- gsub("X17", "", names(WNC.schaefer400x17.HCPD))
 
edge.schaefer200x7.HCPD <- readRDS("/cbica/projects/network_replication/output/HCPD/edge/schaefer200x7_demographics_finalsample_covbat.RData") 

# make sex a factor
class(GBC.glasser.HCPD$sex)
GBC.glasser.HCPD$sex <- as.factor(GBC.glasser.HCPD$sex)
GBC.gordon.HCPD$sex <- as.factor(GBC.gordon.HCPD$sex)
GBC.schaefer200.HCPD$sex <- as.factor(GBC.schaefer200.HCPD$sex)
GBC.schaefer400.HCPD$sex <- as.factor(GBC.schaefer400.HCPD$sex)

 
BNC.gordon.HCPD$sex <- as.factor(BNC.gordon.HCPD$sex)
BNC.schaefer200x7.HCPD$sex <- as.factor(BNC.schaefer200x7.HCPD$sex)
BNC.schaefer200x17.HCPD$sex <- as.factor(BNC.schaefer200x17.HCPD$sex)
BNC.schaefer400x7.HCPD$sex <- as.factor(BNC.schaefer400x7.HCPD$sex)
BNC.schaefer400x17.HCPD$sex <- as.factor(BNC.schaefer400x17.HCPD$sex)

WNC.gordon.HCPD$sex <- as.factor(WNC.gordon.HCPD$sex)   
WNC.schaefer200x17.HCPD$sex <- as.factor(WNC.schaefer200x17.HCPD$sex) 
WNC.schaefer400x17.HCPD$sex <- as.factor(WNC.schaefer400x17.HCPD$sex) 
WNC.schaefer200x7.HCPD$sex <- as.factor(WNC.schaefer200x7.HCPD$sex) 
WNC.schaefer400x7.HCPD$sex <- as.factor(WNC.schaefer400x7.HCPD$sex) 

 
edge.schaefer200x7.HCPD$sex <- as.factor(edge.schaefer200x7.HCPD$sex)
  
```



# load parcel labels and edges 
```{r}
# load parcel labels
glasser.parcel.labels <- read.csv("/cbica/projects/network_replication/atlases/parcellations/glasser360_regionlist_final.csv")

gordon.parcel.labels <- read.csv("/cbica/projects/network_replication/atlases/parcellations/gordon_regionlist_final.csv")

schaefer200x7.parcel.labels <- read.csv("/cbica/projects/network_replication/atlases/parcellations/schaefer200x7_regionlist_final.csv")

schaefer200x17.parcel.labels <- read.csv("/cbica/projects/network_replication/atlases/parcellations/schaefer200x17_regionlist_final.csv")
schaefer200.parcel.labels <- schaefer200x17.parcel.labels #gbc

schaefer400x7.parcel.labels <- read.csv("/cbica/projects/network_replication/atlases/parcellations/schaefer400x7_regionlist_final.csv")

schaefer400x17.parcel.labels <- read.csv("/cbica/projects/network_replication/atlases/parcellations/schaefer400x17_regionlist_final.csv")
schaefer400.parcel.labels <- schaefer400x17.parcel.labels #gbc




# edges
schaefer200x7_edge <- read.csv("/cbica/projects/network_replication/atlases/edge/schaefer200x7_edge.csv")
schaefer200x7_edge <- schaefer200x7_edge[,2]
```  


 
# Check AIC for k=3-6
```{r}
library(stats)

 
dataset_name="HCPD"
covariates ="sex + meanFD_avgSes"
smooth_var="age"


check_aic <- function(parcel.labels, atlas_name, network_parcellation, dataset_name, covariates, smooth_var, k_number){
    parcel.labels <- parcel.labels$label
    list_plots <- list()
    list_AIC <- c()
    list_region <- c()
    for(row in c(1:length(parcel.labels))){ #for each region
      region <- parcel.labels[row] 
      dataname <- sprintf("%s.%s%s.%s", metric, atlas_name, network_parcellation, dataset_name) 
      gam.data <- get(dataname) # Return the Value of a Named Object
      parcel <- region
      region <- str_replace(region, "-", ".")
      modelformula <- as.formula(sprintf("%s ~ s(%s, k=%s, fx=T) + %s", region, smooth_var, k_number, covariates)) # 3 knots, fx = should term be unpenalized (so here, it is unpenalized)
      gam.model <- gam(modelformula, data=gam.data)
      gam.results <- summary(gam.model) 
      
      #list_plots <- append(draw(gam.model, residuals = TRUE), list_plots)
      list_AIC <- append(AIC(gam.model), list_AIC)
      list_region <- append(region, list_region)
      k_dataframe <- data.frame(bind_cols(list_AIC, list_region))
      names(k_dataframe) <- c("AIC", "region")
      print(row)
    }
      return(k_dataframe)
}
 
metric="GBC"
k_3 <- check_aic(schaefer200.parcel.labels, "schaefer200", "", "HCPD", "sex + meanFD_avgSes", "age", 3)
mean(k_3$AIC) #-2501.069
median(k_3$AIC) #-2504.715

k_4 <- check_aic(schaefer200.parcel.labels, "schaefer200", "", "HCPD", "sex + meanFD_avgSes", "age", 4)
mean(k_4$AIC) # -2499.712
median(k_4$AIC) # -2503.663

k_5 <- check_aic(schaefer200.parcel.labels, "schaefer200", "", "HCPD", "sex + meanFD_avgSes", "age", 5)
mean(k_5$AIC) #-2500.483
median(k_5$AIC) #-2508.173

k_6 <- check_aic(schaefer200.parcel.labels, "schaefer200", "", "HCPD", "sex + meanFD_avgSes", "age", 6)
mean(k_6$AIC) #-2499.244
median(k_6$AIC) #-2506.327
 
 
# BNC
metric="BNC"
k_3.BNC <- check_aic(schaefer200x7.parcel.labels, "schaefer200", "x7", "HCPD", "sex + meanFD_avgSes", "age", 3)
mean(k_3.BNC$AIC) #-2311.139
median(k_3.BNC$AIC) #-2375.915

k_4.BNC <- check_aic(schaefer200x7.parcel.labels, "schaefer200", "x7", "HCPD", "sex + meanFD_avgSes", "age", 4)
mean(k_4.BNC$AIC) # -2310.105
median(k_4.BNC$AIC) #-2374.434

k_5.BNC <- check_aic(schaefer200x7.parcel.labels, "schaefer200", "x7", "HCPD", "sex + meanFD_avgSes", "age", 5)
mean(k_5.BNC$AIC) # -2309.979
median(k_5.BNC$AIC) #-2374.98

k_6.BNC <- check_aic(schaefer200x7.parcel.labels, "schaefer200", "x7", "HCPD", "sex + meanFD_avgSes", "age", 6)
mean(k_6.BNC$AIC) # -2308.835
median(k_6.BNC$AIC) #-2375.73


# WNC
metric="WNC"
k_3.WNC <- check_aic(schaefer200x7.parcel.labels, "schaefer200", "x7", "HCPD", "sex + meanFD_avgSes", "age", 3)
mean(k_3.WNC$AIC) # -1372.394
median(k_3.WNC$AIC) #-1385.966

k_4.WNC <- check_aic(schaefer200x7.parcel.labels, "schaefer200", "x7", "HCPD", "sex + meanFD_avgSes", "age", 4)
mean(k_4.WNC$AIC) #-1373.165
median(k_4.WNC$AIC) #-1386.701

k_5.WNC <- check_aic(schaefer200x7.parcel.labels, "schaefer200", "x7", "HCPD", "sex + meanFD_avgSes", "age", 5)
mean(k_5.WNC$AIC) # -1374.075
median(k_5.WNC$AIC) # -1387.161

k_6.WNC <- check_aic(schaefer200x7.parcel.labels, "schaefer200", "x7", "HCPD", "sex + meanFD_avgSes", "age", 6)
mean(k_6.WNC$AIC) #-1373.088
median(k_6.WNC$AIC) #-1385.896
 
```




# Fit GAMs
```{r}
 
# GBC GAMs
gam.GBC.age.glasser <- fitGAMs_covbat(glasser.parcel.labels, "GBC", "glasser", "",dataset)
gam.GBC.age.gordon <- fitGAMs_covbat(gordon.parcel.labels, "GBC", "gordon", "", dataset)
gam.GBC.age.schaefer200 <- fitGAMs_covbat(schaefer200x17.parcel.labels, "GBC", "schaefer200", "", dataset)
gam.GBC.age.schaefer400 <- fitGAMs_covbat(schaefer400x17.parcel.labels, "GBC", "schaefer400", "", dataset)
 

# BNC GAMs
gam.BNC.age.gordon <- fitGAMs_covbat(gordon.parcel.labels, "BNC", "gordon", "", dataset)
gam.BNC.age.schaefer200x7 <- fitGAMs_covbat(schaefer200x7.parcel.labels, "BNC", "schaefer200", "x7", dataset)
gam.BNC.age.schaefer200x17 <- fitGAMs_covbat(schaefer200x17.parcel.labels, "BNC", "schaefer200", "x17",dataset)  
gam.BNC.age.schaefer400x7 <- fitGAMs_covbat(schaefer400x7.parcel.labels, "BNC", "schaefer400", "x7", dataset)   
gam.BNC.age.schaefer400x17 <- fitGAMs_covbat(schaefer400x17.parcel.labels, "BNC", "schaefer400", "x17",dataset)  
 


# WNC GAMs
gam.WNC.age.gordon <- fitGAMs_covbat(gordon.parcel.labels, "WNC", "gordon", "", dataset)
gam.WNC.age.schaefer200x7 <- fitGAMs_covbat(schaefer200x7.parcel.labels, "WNC", "schaefer200", "x7", dataset)   
gam.WNC.age.schaefer200x17 <- fitGAMs_covbat(schaefer200x17.parcel.labels, "WNC", "schaefer200", "x17",dataset)  
gam.WNC.age.schaefer400x7 <- fitGAMs_covbat(schaefer400x7.parcel.labels, "WNC", "schaefer400", "x7",dataset)  
gam.WNC.age.schaefer400x17 <- fitGAMs_covbat(schaefer400x17.parcel.labels, "WNC", "schaefer400", "x17",dataset)  

```



# Fit GAMs for Edges 
- Fitting edge-wise GAMs was very computationally heavy, and was thus submitted as job on cubic.
See /cbica/projects/network_replication/Rscripts/HCPD_scripts/Analysis_scripts/connMetrics_scripts/fitGAMs_edge_HCPD.sh
and
/cbica/projects/network_replication/Rscripts/functions/main_analyses/edge_fitGAMs.R
```{r}
# This code chunk was run on cubic   
schaefer200x7_edge <- gsub("7Networks", "Networks", schaefer200x7_edge)
names(edge.schaefer200x7.HCPD) <- gsub("7Networks", "Networks", names(edge.schaefer200x7.HCPD))
gam.edge.age.schaefer200x7 <- fitGAMs_edge_covbat(schaefer200x7_edge,"edge","schaefer200x7", dataset)

```


# Estimate GAM smooths based on model-predicted data and save out predicted y data** 
```{r}
 
# GBC GAMs 
gam.GBC.smooths.glasser <- estimate_GAMsmooths_covbat(glasser.parcel.labels, "GBC", "glasser", "",dataset)
gam.GBC.smooths.gordon <- estimate_GAMsmooths_covbat(gordon.parcel.labels, "GBC", "gordon", "", dataset)
gam.GBC.smooths.schaefer200 <- estimate_GAMsmooths_covbat(schaefer200x17.parcel.labels, "GBC", "schaefer200", "", dataset)
gam.GBC.smooths.schaefer400 <- estimate_GAMsmooths_covbat(schaefer400x17.parcel.labels, "GBC", "schaefer400", "", dataset)


# BNC GAMs
gam.BNC.smooths.gordon <- estimate_GAMsmooths_covbat(gordon.parcel.labels, "BNC", "gordon", "", dataset)
gam.BNC.smooths.schaefer200x7 <- estimate_GAMsmooths_covbat(schaefer200x7.parcel.labels, "BNC", "schaefer200", "x7", dataset)
gam.BNC.smooths.schaefer200x17 <- estimate_GAMsmooths_covbat(schaefer200x17.parcel.labels, "BNC", "schaefer200", "x17",dataset)
gam.BNC.smooths.schaefer400x7 <- estimate_GAMsmooths_covbat(schaefer400x7.parcel.labels, "BNC", "schaefer400", "x7",dataset)
gam.BNC.smooths.schaefer400x17 <- estimate_GAMsmooths_covbat(schaefer400x17.parcel.labels, "BNC", "schaefer400", "x17",dataset)

# WNC GAMs
gam.WNC.smooths.gordon <- estimate_GAMsmooths_covbat(gordon.parcel.labels, "WNC", "gordon", "", dataset)
gam.WNC.smooths.schaefer200x7 <- estimate_GAMsmooths_covbat(schaefer200x7.parcel.labels, "WNC", "schaefer200", "x7", dataset)
gam.WNC.smooths.schaefer200x17 <- estimate_GAMsmooths_covbat(schaefer200x17.parcel.labels, "WNC", "schaefer200", "x17",dataset)
gam.WNC.smooths.schaefer400x7 <- estimate_GAMsmooths_covbat(schaefer400x7.parcel.labels, "WNC", "schaefer400", "x7",dataset)
gam.WNC.smooths.schaefer400x17 <- estimate_GAMsmooths_covbat(schaefer400x17.parcel.labels, "WNC", "schaefer400", "x17",dataset)
```


# Calculate Region-wise Predicted Fitted GBC values  

```{r}

# GBC GAMs age fitted
gam.GBC.fitted.glasser <- dev_fitted_covbat(glasser.parcel.labels, "GBC", "glasser", dataset)
gam.GBC.fitted.gordon <- dev_fitted_covbat(gordon.parcel.labels, "GBC", "gordon", dataset)
gam.GBC.fitted.schaefer200 <- dev_fitted_covbat(schaefer200x17.parcel.labels, "GBC", "schaefer200", dataset)
gam.GBC.fitted.schaefer400 <- dev_fitted_covbat(schaefer400x17.parcel.labels, "GBC", "schaefer400", dataset)

 
# BNC GAMs age fitted
gam.BNC.fitted.gordon <- dev_fitted_covbat(gordon.parcel.labels, "BNC", "gordon", dataset)
gam.BNC.fitted.schaefer200x7 <- dev_fitted_covbat(schaefer200x7.parcel.labels, "BNC", "schaefer200x7", dataset)
gam.BNC.fitted.schaefer200x17 <- dev_fitted_covbat(schaefer200x17.parcel.labels, "BNC", "schaefer200x17", dataset)
gam.BNC.fitted.schaefer400x7 <- dev_fitted_covbat(schaefer400x7.parcel.labels, "BNC", "schaefer400x7", dataset)
gam.BNC.fitted.schaefer400x17 <- dev_fitted_covbat(schaefer400x17.parcel.labels, "BNC", "schaefer400x17", dataset)

# WNC GAMs age fitted
gam.WNC.fitted.gordon <- dev_fitted_covbat(gordon.parcel.labels, "WNC", "gordon", dataset)
gam.WNC.fitted.schaefer200x7 <- dev_fitted_covbat(schaefer200x7.parcel.labels, "WNC", "schaefer200x7", dataset)
gam.WNC.fitted.schaefer200x17 <- dev_fitted_covbat(schaefer200x17.parcel.labels, "WNC", "schaefer200x17",dataset)
gam.WNC.fitted.schaefer400x7 <- dev_fitted_covbat(schaefer400x7.parcel.labels, "WNC", "schaefer400x7", dataset)
gam.WNC.fitted.schaefer400x17 <- dev_fitted_covbat(schaefer400x17.parcel.labels, "WNC", "schaefer400x17", dataset)

```


 

# Calculate Region-wise Predicted Fitted GBC values Correlation with SA Axis for Schaefer200 only 
- Calculating region-wise predicted fitted GBC was very computationally heavy, and was thus submitted as job on cubic.
See /cbica/projects/network_replication/Rscripts/HCPD_scripts/Analysis_scripts/connMetrics_scripts/fittedGBC_analysis_HCPD.sh
and
/cbica/projects/network_replication/Rscripts/functions/main_analyses/fittedGBC_analysis.R

```{r}
# This code chunk was submitted as a job on cubic

fits.SAaxis.posteriorcor_schaefer200.GBC <- make_fits.SAaxis.posteriorcor_covbat("GBC", "schaefer200", dataset)

```
