---
title: "GBC GAMs: PNC"
author: "Valerie Jill Sydnor" adapted by Audrey
output:
  html_document:
    code_folding: show
    highlight: haddock
    theme: lumen
    toc: yes
    toc_depth: 4
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
source("/cbica/projects/network_replication/adapted_Rscripts/GAM_functions.R")
```


**Prepare GBC + Demographics data frame for GAMs**
```{r}
participants <- read.csv("/cbica/projects/network_replication/adapted_Rscripts/participants_allIDs.csv") #final study sample pnc IDs (bblid/scanid) from Adam Pines's multiscale paper
demographics <- read.csv("/cbica/projects/network_replication/PNC/n1601_demographics_go1_20161212.csv") #PNC demographics information
demographics <- demographics %>% mutate(age = (ageAtScan1/12)) #format age variable
demographics$sex <- as.factor(demographics$sex) #format sex variable

demographics <- merge(participants, demographics, by="scanid") #get demographics for final study sample only via ID matching
relRMS <- read.csv("/cbica/projects/network_replication/PNC/qc_files/RBC_PNC_relMeans.csv") 
demographics <- merge(demographics, relRMS, by="rbcid") #add motion information to demographics df
```

# make GBC-demographics .csv's
```{r}

gbc.subxparcel.matrix.gordon <- read.csv("/cbica/projects/network_replication/GBC/GBC_subxparcel_matrix_gordon.csv") #participant x gordon region GBC spreadsheet
gbc.subxparcel.matrix.gordon <- gbc.subxparcel.matrix.gordon[-c(1:7, 24, 690, 691),] # the subjects that should've been removed earlier 
col_rm <- as.numeric(levels(as.factor(as.data.frame(which(is.na(gbc.subxparcel.matrix.gordon), arr.ind=TRUE))$col)))
gbc.subxparcel.matrix.gordon <- gbc.subxparcel.matrix.gordon[, -col_rm]
gbc.gordon.pnc <- merge(gbc.subxparcel.matrix.gordon, demographics, by="rbcid") #get gordon GBC data and demographics for final study sample via ID matching 


gordon.parcel.labels <- read.csv("/cbica/projects/network_replication/atlases/parcellations/gordon_regionlist_xcp.csv", header = F) 
names(gordon.parcel.labels) <- "label"
gordon.parcel.labels[which(SNRmask_gordon == 0),] <- NA # apply SNR mask to parcel names
gordon.parcel.labels <- na.omit(gordon.parcel.labels)

names(gbc.gordon.pnc)[2:305] <- gordon.parcel.labels$label
 
#write.csv(gbc.gordon.pnc, "/cbica/projects/network_replication/GBC/GBCgordon_demographics_finalsample.csv")
```

# load GBC-demographics df's
```{r}
gbc.gordon.pnc <- read.csv('/cbica/projects/network_replication/GBC/GBCgordon_demographics_finalsample.csv')

```


# edit parcel labels to reflect SNR mask
```{r}

gordon.parcel.labels <- read.csv("/cbica/projects/network_replication/atlases/parcellations/gordon_regionlist_xcp.csv", header = F) #schaefer parcel names in order of surface data
names(gordon.parcel.labels) <- "orig_parcelname"
# remove parcels using SNR mask
SNR.mask.gordon <- read.csv("/cbica/projects/network_replication/atlases/Masks/SNRmask_gordon.csv")
rm <- which(SNR.mask.gordon$SNR.mask == 0)
gordon.parcel.labels <- gordon.parcel.labels[-rm,]

```

**Fit GAMs**
Fit GAM (GBC ~ s(age) + sex + RMSmotion)) per each region in atlas and save out statistics and derivative-based characteristics
```{r}
gam.GBC.age.gordon <- matrix(data=NA, nrow=length(gordon.parcel.labels), ncol=9) #empty matrix to save gam.fit output to
 

# get GAMs for gbc.gordon.pnc - which includes gordon GBC data and demographics
for(row in c(1:length(gordon.parcel.labels))){ #for each gordon region
  region <- gordon.parcel.labels[row] 
  GAM.RESULTS <- gam.fit(measure = "gbc", atlas = "gordon", dataset = "pnc", region = region, smooth_var = "age", covariates = "sex + RMSmotion") #run the gam.fit function
  gam.GBC.age.gordon[row,] <- GAM.RESULTS}

 
gam.GBC.age.gordon <- as.data.frame(gam.GBC.age.gordon)
colnames(gam.GBC.age.gordon) <- c("label","GAM.age.Fvalue","GAM.age.pvalue","GAM.age.AdjRsq","Anova.age.pvalue","age.onsetchange","age.peakchange","maxage.GBC.increase","age.maturation")
cols = c(2:9)    
gam.GBC.age.gordon[,cols] = apply(gam.GBC.age.gordon[,cols], 2, function(x) as.numeric(as.character(x)))
gam.GBC.age.gordon <- gam.GBC.age.gordon %>% mutate(significant = (Anova.age.pvalue < 0.05))

#write.csv(gam.GBC.age.gordon, "/cbica/projects/network_replication/GBC/GAM/GAMresults.GBC.age.gordon.csv", row.names = F, quote = F)
 
```


# load GAMs output
```{r}
gam.GBC.age.gordon <- read.csv("/cbica/projects/network_replication/GBC/GAM/GAMresults.GBC.age.gordon.csv")
```


**Estimate GAM smooths based on model-predicted data and save out predicted y data**
```{r}
gam.smooths.gordon <- matrix(data=NA, ncol=7) #empty matrix to save gam.predsmooth fits to
colnames(gam.smooths.gordon) <- c("age","fit","se.fit","selo","sehi","index","label")

gam.peaks.gordon <- matrix(data=NA, ncol=2) #empty matrix to save measure peaks to (value of x when y is predicted to be maximal)
colnames(gam.peaks.gordon) <- c("label","age.peak")

for(row in c(1:length(gordon.parcel.labels))){ #for each gordon region
  
  region <- gordon.parcel.labels[row] #get the region name
  GAM.SMOOTH <- gam.predsmooth(measure = "gbc", atlas = "gordon", dataset = "pnc", region = region, smooth_var = "age", covariates = "sex + RMSmotion") #run the gam.predsmooth function
  
  preddata <- as.data.frame(GAM.SMOOTH[3]) #get predicted.smooth df from function output
  preddata$index <- rep(x=row, 1000) #region index
  preddata$label <- rep(x=GAM.SMOOTH[1], 1000) #label
  gam.smooths.gordon <- rbind(gam.smooths.gordon, preddata)
  
  datapeak <- as.data.frame(cbind(GAM.SMOOTH[1], GAM.SMOOTH[2]))
  colnames(datapeak) <- c("label","age.peak")
  gam.peaks.gordon <- rbind(gam.peaks.gordon, datapeak)
}
gam.smooths.gordon <- gam.smooths.gordon[-1,] #remove empty initilization row
gam.smooths.gordon$label <- as.character(gam.smooths.gordon$label)
gam.peaks.gordon <- gam.peaks.gordon[-1,] #remove empty initilization row
gam.peaks.gordon$label <- as.character(gam.peaks.gordon$label)
gam.peaks.gordon$age.peak <- as.numeric(gam.peaks.gordon$age.peak)

#write.csv(gam.smooths.gordon,"/cbica/projects/network_replication/GBC/GAM/GAMsmoothfits.GBC.age.gordon.csv", row.names = F, quote = F)
#write.csv(gam.peaks.gordon, "/cbica/projects/network_replication/GBC/GAM/GAMpeaks.GBC.age.gordon.csv", row.names = F, quote = F)
```